### 2017-04-07 Paper01_EnthalpyAndCrystallization.tex
Paper01 - Basic layout, initial figures, and method

\documentclass[a4paper,12pt,oneside]{article}%FinalView
%\documentclass[draft,a4paper,12pt,oneside]{article}%draftView

\input{settings/preamble.tex}%Inputs Preamble for its .tex
\usepackage[color]{showkeys}%Shows cross ref paths

\begin{document}
\thispagestyle{empty} % don't show (roman) page number on titlepage
\begin{titlepage}
\begin{center}
\vspace*{1cm}

%Title
\textbf{\LARGE{An assessment of structural enthalpy and crystallization pathways of \MgZnCa~ bulk metallic glass and amorphous films}}

\vspace{2cm}

\textbf{Scott Gleason, David Miskovic, Kevin Laws, Michael Ferry}

\vspace{2cm}

UNSW Australia\\ School of Material Science and Engineering

\vspace{2cm}

%Month and Year
\today
\end{center}
\end{titlepage}

\clearpage 
\pagenumbering{roman}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{ABSTRACT}
\addcontentsline{toc}{section}{ABSTRACT}

The structural nature and thermal stability of amorphous alloys is highly dependent on the method by which they are produced, i.e. their relaxation rate upon cooling.  Both bulk samples and metallic glass films of \MgZnCa~ were produced by copper mold casting and \gls{dc} magnetron sputtering onto aluminium substrates, respectively. Comparisons between structural enthalpy, crystallization pathways, relaxation and crystallization kinetics of the bulk samples and films were examined by elevated temperature \acrshort{xrd} and \acrshort{dsc}. Compared with equivalent experiments on the bulk alloy, results for the thin films show distinct differences in structural enthalpy and deviations from the expected crystalline phase evolution, displaying minor peak shifts, failure of some phases to evolve, and variations in the evolution rates.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%Table of Contents
%\clearpage
\newpage
\tableofcontents\newpage
\addcontentsline{toc}{section}{TABLE OF CONTENTS}
\clearpage %% start of main matter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{INTRODUCTION}
\pagenumbering{arabic}
\glsresetall

The structural nature and thermal stability of amorphous alloys is highly dependent on the method by which they are produced, i.e. their relaxation rate upon cooling.  Both bulk samples and metallic glass films of \MgZnCa~ were produced by copper mold casting and \gls{dc} magnetron sputtering onto aluminium substrates, respectively. Comparisons between structural enthalpy, crystallization pathways, relaxation and crystallization kinetics of the bulk samples and films were examined by elevated temperature \acrshort{xrd} and \acrshort{dsc}. Compared with equivalent experiments on the bulk alloy, results for the thin films show distinct differences in structural enthalpy and deviations from the expected crystalline phase evolution, displaying minor peak shifts, failure of some phases to evolve, and variations in the evolution rates.

Key sources \cite{Zhang2013, Zhang2012} 
\cite{Zhang2011}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{METHOD}
\glsresetall

The master alloy of \MgZnCa~ was produced using high-purity elements of Mg (99.85 wt\%), Zn (99.995 wt\%), and Ca (99.8 wt\%). The alloy was prepared by induction melting in boron nitride coated graphite crucibles, purged with Ar (99.997 vol.\% purity) five times, and protected with a continuous circulating Ar flow. The alloy was heated and cooled through a cycle 700\degree C, 385\degree C, 650\degree C, 385\degree C, 650\degree C to a casting temperature of 500\degree C to ensure homogeneity. Bulk amorphous \MgZnCa~ plate with a thickness of $XX~ \mu m$ was produced by copper mold injection casting. The $25.4~ mm$ diameter targets were prepared from a cylindrical copper mold gravity casting sectioned to a thickness of $3.25~ mm$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{RESULTS}
\glsresetall

%code to put 2 images side by side in a figure
\begin{figure}[b]
	\centering
	%Image 1
	\begin{subfigure}[htbp]{0.75\textwidth}
		\includegraphics[width=\textwidth]{Bulk_Heated_XRD_StackFull_Smooth2.png}
		\caption{}
		\label{fig:HeatBulkFullStack}
	\end{subfigure}
	%Image 2
	\begin{subfigure}[htbp]{0.75\textwidth}
		\includegraphics[width=\textwidth]{Bulk_Heated_XRD_Waterfall3D_Smooth2.png}
		\caption{}
		\label{fig:HeatBulkWaterFall}
	\end{subfigure}
	\caption{(a) Stacked \gls{xrd} patterns from the incremental heating of bulk \MgZnCa. (b) Cascading \gls{xrd} patterns from the incremental heating of bulk \MgZnCa. }%global caption
	\label{fig:HeatBulk}
\end{figure}

%code to put 2 images side by side in a figure
\begin{figure}[b]
	\centering
	%Image 1
	\begin{subfigure}[htbp]{0.75\textwidth}
		\includegraphics[width=\textwidth]{TF_Facet_HeatXRD_StackFull_Smooth.png}
		\caption{}
		\label{fig:HeatFilmFullStack}
	\end{subfigure}
	%Image 2
	\begin{subfigure}[htbp]{0.75\textwidth}
		\includegraphics[width=\textwidth]{TF_Facet_HeatXRD_Waterfall3D_Smooth.png}
		\caption{}
		\label{fig:HeatFilmWaterFall}
	\end{subfigure}
	\caption{(a) Stacked \gls{xrd} patterns from the incremental heating of film \MgZnCa. (b) Cascading \gls{xrd} patterns from the incremental heating of film \MgZnCa. }%global caption
	\label{fig:HeatFilm}
\end{figure}

%single image
\begin{figure}[b]
	\centering
	\includegraphics[width=0.95\textwidth]{XTalPath_Facet_FullStack_Smooth.png}
	\caption[Table of contents Capition]{\acrshort{xrd} pattern for \MgZnCa~ heated through several crystallization peaks identified from \acrshort{dsc}}
	\label{fig:TF_DSC_XRDHeating}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{DISCUSSION}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{CONCLUSIONS}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{ACKNOWLEDGEMENTS}

%People
Yu Wang for his assistance with \acrshort{xrd} experimentation and Rietveld refinement.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%Bibliography
\bibliography{ThesisBib}
\bibliographystyle{unsrt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

### 2017-04-07 Paper01_EnthalpyAndCrystallization.tex
Method - refined first paragraph

@@
 The master alloy of \MgZnCa~ was produced using high-purity elements of Mg (99.85 wt\%), Zn (99.995 wt\%), and Ca (99.8 wt\%).
-The alloy was prepared by induction melting in boron nitride coated graphite crucibles, purged with Ar (99.997 vol.\% purity) five times, and protected with a continuous circulating Ar flow.
-The alloy was heated and cooled through a cycle 700\degree C, 385\degree C, 650\degree C, 385\degree C, 650\degree C to a casting temperature of 500\degree C to ensure homogeneity.
+The alloy was prepared by induction melting in boron nitride coated graphite crucibles, purged with Ar (99.997 vol.\% purity) five times, and protected with a circulating Ar atmosphere.
+Alloy homogeneity was ensured through heating and cooling through a cycle 700\degree C, 385\degree C, 650\degree C, 385\degree C, 650\degree C to a casting temperature of 500 \degree C and 450\degree C for for injection and gravity casting respectively.
 Bulk amorphous \MgZnCa~ plate with a thickness of $XX~ \mu m$ was produced by copper mold injection casting.
-The $25.4~ mm$ diameter targets were prepared from a cylindrical copper mold gravity casting sectioned to a thickness of $3.25~ mm$.
+The $25.4~ mm$ diameter targets were prepared from a cylindrical copper mold gravity casting sectioned to thicknesses of $3.25~ mm$.
+
+\gls{dc} magnetron sputtering
 

### 2017-04-07 Paper01_EnthalpyAndCrystallization.tex
Method - Draft - Sputter Method

@@
 Alloy homogeneity was ensured through heating and cooling through a cycle 700\degree C, 385\degree C, 650\degree C, 385\degree C, 650\degree C to a casting temperature of 500 \degree C and 450\degree C for for injection and gravity casting respectively.
-Bulk amorphous \MgZnCa~ plate with a thickness of $XX~ \mu m$ was produced by copper mold injection casting.
-The $25.4~ mm$ diameter targets were prepared from a cylindrical copper mold gravity casting sectioned to thicknesses of $3.25~ mm$.
+Bulk amorphous \MgZnCa~ plate with a thickness of $XX \mu m$ was produced by copper mold injection casting.
+The $25.4 mm$ diameter targets were prepared from a cylindrical copper mold gravity casting sectioned to thicknesses of $3.25 mm$.
 
-\gls{dc} magnetron sputtering
+Films were produced from an in-house \acrshort{dc} magnetron sputtering facility with Ar working gas (99.997 vol.\% purity).
+The power was $15W$, typical voltage of $290-350V$, nominal chamber temperature of 25 \degree C, pressure 1 bar, Ar flow 3.01 \gls{sccm}.
+
+DSC
+
+XRD
 
@@
 \glsresetall
+
+deposition were for 35 minutes, and saw an average temperature rise of $3 - 4$ \degree C during the deposition. Nominal film thickness was about $2.5 \mu m$ giving a deposition rate of $1.2 nm/s$.
 

### 2017-04-07 Paper01_EnthalpyAndCrystallization.tex
Method - Added subsections and basic xrd draft

@@
 
+\subsection{Master alloy}
 The master alloy of \MgZnCa~ was produced using high-purity elements of Mg (99.85 wt\%), Zn (99.995 wt\%), and Ca (99.8 wt\%).
@@
 
+\subsection{\acrshort{dc} magnetron sputtering}
 Films were produced from an in-house \acrshort{dc} magnetron sputtering facility with Ar working gas (99.997 vol.\% purity).
@@
 
+\subsection{\acrshort{dsc} characterization}
 DSC
 
-XRD
+\subsection{\acrshort{xrd} characterization}
+XRD heated in 5 degree increments at 20 k/min. scans of xx over a range of 30 - 60 2 theta allows 20 minute scans.
 

### 2017-04-12 Paper01_EnthalpyAndCrystallization.tex
Results - Updated bulk XRD with labled figure
Results - updated with latest labelled figures

@@
 	\begin{subfigure}[htbp]{0.75\textwidth}
-		\includegraphics[width=\textwidth]{Bulk_Heated_XRD_StackFull_Smooth2.png}
+		\includegraphics[width=\textwidth]{Bulk_Heated_XRD_StackFull_Smooth2_Labelled2.png}
 		\caption{}
@@
 	\begin{subfigure}[htbp]{0.75\textwidth}
-		\includegraphics[width=\textwidth]{TF_Facet_HeatXRD_StackFull_Smooth.png}
+		\includegraphics[width=\textwidth]{TF_Facet_HeatXRD_StackFull_Smooth_Labelled.png}
 		\caption{}

### 2017-04-14 Paper01_EnthalpyAndCrystallization.tex
Results - Added m figure, and labelled heated xrd figure. Moved unused figures to own directory

@@
 
+Relaxed \gls{dsc} of bulk material taken at different heating rates was used to establish the fragility of the \MgZnCa system.
+$\beta^{-1} = 1.338E - 16e^{5274 (\frac{1}{T-T_{0}})}$ with Adj. $R^{2}=0.972$
+
+%single image
+\begin{figure}[b]
+	\centering
+	\includegraphics[width=0.95\textwidth]{Bulk_Fitted_mValue.png}
+	\caption[Table of contents Capition]{Fitted fragility for the \MgZnCa system obtained by \acrshort{dsc} at various heating rates}
+	\label{fig:Bulk_Fitted_mValue}
+\end{figure}
+
 %code to put 2 images side by side in a figure
@@
 	\centering
-	\includegraphics[width=0.95\textwidth]{XTalPath_Facet_FullStack_Smooth.png}
+	\includegraphics[width=0.95\textwidth]{XTalPath_Facet_FullStack_Smooth_Labelled_HeavyCull.png}
 	\caption[Table of contents Capition]{\acrshort{xrd} pattern for \MgZnCa~ heated through several crystallization peaks identified from \acrshort{dsc}}

### 2017-04-14 Paper01_EnthalpyAndCrystallization.tex
Discussion - added some DSC notes, Results - added m value calcs.

@@
 \section{METHOD}
-\glsresetall
 
@@
 \section{RESULTS}
-\glsresetall
 
@@
 
-Relaxed \gls{dsc} of bulk material taken at different heating rates was used to establish the fragility of the \MgZnCa system.
-$\beta^{-1} = 1.338E - 16e^{5274 (\frac{1}{T-T_{0}})}$ with Adj. $R^{2}=0.972$
+Relaxed \gls{dsc} of bulk material taken at different heating rates was used to establish the fragility of the \MgZnCa~ system. From the equations ... a fit of
+$\beta^{-1} = 1.338E - 16e^{5274 (\frac{1}{T-T_{0}})}$ with Adj. $R^{2}=0.972$ was established. This give a $D^{*}=20.4$ which using $D^{*}=590/(m-16)$ Shuai2014 [4, 5] gives a fragility $m=44.9$.
 
@@
 
+The use of a 60K \gls{dsc} heating rate compared to the more commonly used 20K rate [sources] shifts peaks for the bulk \MgZnCa~ alloy about 8 - 15 degrees higher.
+This higher heating rates were used because crystallization events for the films were different to differentiation at the lower heating rate.
+Films show little shift to high temperature peaks with increases heating rates, but large shifts with relaxation. 
+Bulk show the opposite behaviour, larger peaks shifts with higher heating rates and little shift with relaxation.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2017-04-16 Paper01_EnthalpyAndCrystallization.tex
Results - added the bulk relaxation images

@@
 
+%code to put 2 images side by side in a figure
+\begin{figure}[b]
+	\centering
+	%Image 1
+	\begin{subfigure}[htbp]{0.495\textwidth}
+		\includegraphics[width=\textwidth]{Bulk_Relaxed_Full.png}
+		\caption{}
+		\label{fig:Bulk_Relaxed}
+	\end{subfigure}
+	%Image 2
+	\begin{subfigure}[htbp]{0.495\textwidth}
+		\includegraphics[width=\textwidth]{Bulk_Onset_Peaks_Relaxed_120C.png}
+		\caption{}
+		\label{fig:Bulk_Onsets}
+	\end{subfigure}
+	\caption{(a) Bulk \MgZnCa~ relaxed at 120 \degree C for 10 minutes and heated at various heating rates.
+The insert stacks the \gls{dsc} curves and labels the \Tg~ and \Tx es of the $100 K/min$ sample.
+(b) The \Tg s and \Tx es of the bulk \MgZnCa~ at all heating rates.
+}%global caption
+	\label{fig:DSC_Bulk}
+\end{figure}
+
 %single image
@@
 	\centering
-	\includegraphics[width=0.95\textwidth]{Bulk_Fitted_mValue.png}
+	\includegraphics[width=0.95\textwidth]{Bulk_Fitted_mValue_Tg.png}
 	\caption[Table of contents Capition]{Fitted fragility for the \MgZnCa system obtained by \acrshort{dsc} at various heating rates}

### 2017-07-25 Paper01_EnthalpyAndCrystallization.tex
Results - added table of bulk onset values
Updated figures from ISMANAM work

@@
 
-\textbf{Scott Gleason, David Miskovic, Kevin Laws, Michael Ferry}
+\textbf{Scott Gleason, David Miskovic, Nicholas Hamilton, Kevin Laws, Michael Ferry}
 
@@
 
+\begin{table}[h]
+	\centering
+	\begin{tabular}{ c c c c c c c }
+		\toprule
+		Heating Rate \acrshort{ht} & \acrshort{Tg} & $T_{x1}$ & $T_{x2}$ & $T_{x3}$ & $T_{x4}$ & $T_{x5}$ \\ 
+		$K/min$ & & & & & & \\
+		\midrule
+		100 & 136.1 & 163.4 & 205.2 & 217.2 & 251.2 & 270.6 \\ 
+		80 & 132.0 & 159.5 & 201.5 & 213.7 & 245.3 & 266.0 \\ 
+		60 & 129.6 & 157.4 & 199.1 & 210.9 & 240.6 & 261.8 \\ 
+		40 & 126.6 & 155.0 & 196.3 & 208.0 & 234.8 & 256.3 \\ 
+		30 & 126.2 & 151.1 & 193.7 & 204.8 & 230.5 & 252.3 \\ 
+		20 & 125.1 & 149.8 & 190.9 & 201.4 & 224.1 & 247.5 \\ 
+		15 & 123.8 & 148.5 & 189.2 & 199.3 & 220.7 & 244.4 \\ 
+		10 & 123.5 & 144.7 & 186.1 & 195.9 & 215.4 & 240.2 \\ 
+		5 & 120.5 & 141.7 & 181.9 & 189.8 & 204.5 & 232.8 \\ 
+		\bottomrule
+	\end{tabular}
+	\caption{Bulk \MgZnCa~ alloy onset temperatures for the various \acrshort{dsc} \acrlongpl{ht} \acrshort{ht}. All temperatures are in \degree C.}
+	\label{tab:BulkOnsets}
+\end{table}
+
 %code to put 2 images side by side in a figure
@@
 	\begin{subfigure}[htbp]{0.495\textwidth}
-		\includegraphics[width=\textwidth]{Bulk_Relaxed_Full.png}
+		\includegraphics[width=\textwidth]{DSC_Fragility_Bulk.png}
 		\caption{}
-		\label{fig:Bulk_Relaxed}
+		\label{fig:DSC_vHeatingRate_Bulk}
 	\end{subfigure}
@@
 		\caption{}
-		\label{fig:Bulk_Onsets}
+		\label{fig:DSC_Onsets_Bulk}
 	\end{subfigure}
@@
 	\centering
-	\includegraphics[width=0.95\textwidth]{Bulk_Fitted_mValue_Tg.png}
+	\includegraphics[width=0.95\textwidth]{Bulk_Film_Fragility.png}
 	\caption[Table of contents Capition]{Fitted fragility for the \MgZnCa system obtained by \acrshort{dsc} at various heating rates}
-	\label{fig:Bulk_Fitted_mValue}
+	\label{fig:Fragility_BulkFilm_mValue}
 \end{figure}
@@
 	\begin{subfigure}[htbp]{0.75\textwidth}
-		\includegraphics[width=\textwidth]{Bulk_Heated_XRD_StackFull_Smooth2_Labelled2.png}
+		\includegraphics[width=\textwidth]{XRD_Dynamic_Bulk.png}
 		\caption{}
-		\label{fig:HeatBulkFullStack}
+		\label{fig:XRD_Dynamic_FullStack_Bulk}
 	\end{subfigure}
@@
 		\caption{}
-		\label{fig:HeatBulkWaterFall}
+		\label{fig:XRD_Dynamic_WaterFall_Bulk}
 	\end{subfigure}
 	\caption{(a) Stacked \gls{xrd} patterns from the incremental heating of bulk \MgZnCa. (b) Cascading \gls{xrd} patterns from the incremental heating of bulk \MgZnCa. }%global caption
-	\label{fig:HeatBulk}
+	\label{fig:XRD_Dynamic_Bulk}
 \end{figure}
@@
 	\begin{subfigure}[htbp]{0.75\textwidth}
-		\includegraphics[width=\textwidth]{TF_Facet_HeatXRD_StackFull_Smooth_Labelled.png}
+		\includegraphics[width=\textwidth]{XRD_Dynamic_Film.png}
 		\caption{}
-		\label{fig:HeatFilmFullStack}
+		\label{fig:XRD_Dynamic_FullStack_Film}
 	\end{subfigure}
@@
 		\caption{}
-		\label{fig:HeatFilmWaterFall}
+		\label{fig:XRD_Dynamic_WaterFall_Film}
 	\end{subfigure}
 	\caption{(a) Stacked \gls{xrd} patterns from the incremental heating of film \MgZnCa. (b) Cascading \gls{xrd} patterns from the incremental heating of film \MgZnCa. }%global caption
-	\label{fig:HeatFilm}
+	\label{fig:XRD_Dynamic_Film}
 \end{figure}
@@
 	\centering
-	\includegraphics[width=0.95\textwidth]{XTalPath_Facet_FullStack_Smooth_Labelled_HeavyCull.png}
-	\caption[Table of contents Capition]{\acrshort{xrd} pattern for \MgZnCa~ heated through several crystallization peaks identified from \acrshort{dsc}}
-	\label{fig:TF_DSC_XRDHeating}
+	\includegraphics[width=0.95\textwidth]{XRD_Annealing_Bulk.png}
+	\caption[Table of contents Capition]{\acrshort{xrd} pattern for Bulk \MgZnCa~ heated through several crystallization peaks identified from \acrshort{dsc}}
+	\label{fig:XRD_Annealing_Bulk}
+\end{figure}
+
+%single image
+\begin{figure}[b]
+	\centering
+	\includegraphics[width=0.95\textwidth]{XRD_Annealing_Film.png}
+	\caption[Table of contents Capition]{\acrshort{xrd} pattern for Film \MgZnCa~ heated through several crystallization peaks identified from \acrshort{dsc}}
+	\label{fig:XRD_Annealing_Film}
 \end{figure}

### 2017-07-26 Paper01_EnthalpyAndCrystallization.tex
DSC Film - added film DSC figures
Method - filed in XRD details

@@
 \subsection{\acrshort{xrd} characterization}
-XRD heated in 5 degree increments at 20 k/min. scans of xx over a range of 30 - 60 2 theta allows 20 minute scans.
+Annealing XRD (PANalytical Empyrean) with a Cu $K_{\alpha}$ X-ray source ($\lambda = 1.541 \angstrom$ ). Generator Voltage 45, Tube Current 40, Scan Step Size 0.0262606, Time per step 397.29.
+
+Dynamic XRD (Bruker D8) with a Cu $K_{\alpha}$ X-ray source ($\lambda = 1.541 \angstrom$ ). Generator Voltage 45, Tube Current 100, Scan Step Size 0.02, Time per step 134.4.
+
+XRD heated in 5 degree increments at 20 k/min. scans of xx over a range of 31 - 60 2 theta allows 20 minute scans.
 
@@
 
+%code to put 2 images side by side in a figure
+\begin{figure}[b]
+	\centering
+	%Image 1
+	\begin{subfigure}[htbp]{0.495\textwidth}
+		\includegraphics[width=\textwidth]{DSC_Fragility_Film.png}
+		\caption{}
+		\label{fig:DSC_vHeatingRate_Film}
+	\end{subfigure}
+	%Image 2
+	\begin{subfigure}[htbp]{0.495\textwidth}
+		\includegraphics[width=\textwidth]{Onsets_BulkandFilm.png}
+		\caption{}
+		\label{fig:DSC_Onsets_Film}
+	\end{subfigure}
+	\caption{(a) Unrelaxed film \MgZnCa~ heated at various heating rates.
+The insert stacks the \gls{dsc} curves and labels the \Tg~ and \Tx es of the $100 K/min$ sample.
+(b) The \Tg s and \Tx es of the bulk and film \MgZnCa~ at all heating rates.
+}%global caption
+	\label{fig:DSC_Film}
+\end{figure}
+
 %single image
@@
 	\centering
-	\includegraphics[width=0.95\textwidth]{XRD_Annealing_Bulk.png}
+	\includegraphics[width=0.9\textwidth]{XRD_Annealing_Bulk.png}
 	\caption[Table of contents Capition]{\acrshort{xrd} pattern for Bulk \MgZnCa~ heated through several crystallization peaks identified from \acrshort{dsc}}
@@
 	\centering
-	\includegraphics[width=0.95\textwidth]{XRD_Annealing_Film.png}
+	\includegraphics[width=0.9\textwidth]{XRD_Annealing_Film.png}
 	\caption[Table of contents Capition]{\acrshort{xrd} pattern for Film \MgZnCa~ heated through several crystallization peaks identified from \acrshort{dsc}}

### 2017-07-26 Paper01_EnthalpyAndCrystallization.tex
Method - work on DSC, casting, and Sputter

@@
 The alloy was prepared by induction melting in boron nitride coated graphite crucibles, purged with Ar (99.997 vol.\% purity) five times, and protected with a circulating Ar atmosphere.
-Alloy homogeneity was ensured through heating and cooling through a cycle 700\degree C, 385\degree C, 650\degree C, 385\degree C, 650\degree C to a casting temperature of 500 \degree C and 450\degree C for for injection and gravity casting respectively.
-Bulk amorphous \MgZnCa~ plate with a thickness of $XX \mu m$ was produced by copper mold injection casting.
+Alloy homogeneity was ensured through heating and cooling through a cycle of 700\degree C, 385\degree C, 650\degree C, 385\degree C, 650\degree C to a casting temperature of 500 \degree C and 450\degree C for for injection and gravity casting respectively.
+Bulk amorphous \MgZnCa~ rod of $2.5 mm$ diameter and plates of thickness of $XX \mu m$ was produced by copper mold injection casting.
 The $25.4 mm$ diameter targets were prepared from a cylindrical copper mold gravity casting sectioned to thicknesses of $3.25 mm$.
@@
 Films were produced from an in-house \acrshort{dc} magnetron sputtering facility with Ar working gas (99.997 vol.\% purity).
-The power was $15W$, typical voltage of $290-350V$, nominal chamber temperature of 25 \degree C, pressure 1 bar, Ar flow 3.01 \gls{sccm}.
+The power was $15W$, typical voltage of $290-350V$, nominal chamber pressure 1 bar, temperature of 25 \degree C, Ar flow 3.01 \gls{sccm}.
+Depositions were onto Al substrates for a period of 35 minutes.
 
 \subsection{\acrshort{dsc} characterization}
-DSC
+Isochronic DSC (204 F1 Phoenix, Netzsch, Selb, Germany) was carried out in aluminium crucibles under protective argon atmosphere. Scans were performed at heating rates of 5 to 100 K/min.
 
@@
 
-XRD heated in 5 degree increments at 20 k/min. scans of xx over a range of 31 - 60 2 theta allows 20 minute scans.
+The temperature was raised in 5 K increments at 20 K/min. scans of xx over a range of 31 - 60 2 theta allows 20 minute scans.
 
@@
 
+%single image
+\begin{figure}[b]
+	\centering
+	\includegraphics[width=0.9\textwidth]{XRD_Annealing_Bulk.png}
+	\caption[Table of contents Capition]{\acrshort{xrd} pattern for Bulk \MgZnCa~ heated through several crystallization peaks identified from \acrshort{dsc}}
+	\label{fig:XRD_Annealing_Bulk}
+\end{figure}
+
+%single image
+\begin{figure}[b]
+	\centering
+	\includegraphics[width=0.9\textwidth]{XRD_Annealing_Film.png}
+	\caption[Table of contents Capition]{\acrshort{xrd} pattern for Film \MgZnCa~ heated through several crystallization peaks identified from \acrshort{dsc}}
+	\label{fig:XRD_Annealing_Film}
+\end{figure}
+
 %code to put 2 images side by side in a figure
@@
 
-%single image
-\begin{figure}[b]
-	\centering
-	\includegraphics[width=0.9\textwidth]{XRD_Annealing_Bulk.png}
-	\caption[Table of contents Capition]{\acrshort{xrd} pattern for Bulk \MgZnCa~ heated through several crystallization peaks identified from \acrshort{dsc}}
-	\label{fig:XRD_Annealing_Bulk}
-\end{figure}
-
-%single image
-\begin{figure}[b]
-	\centering
-	\includegraphics[width=0.9\textwidth]{XRD_Annealing_Film.png}
-	\caption[Table of contents Capition]{\acrshort{xrd} pattern for Film \MgZnCa~ heated through several crystallization peaks identified from \acrshort{dsc}}
-	\label{fig:XRD_Annealing_Film}
-\end{figure}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2017-07-27 Paper01_EnthalpyAndCrystallization.tex
Fixed DSC Bulk table values
DSC Table - added film onsets table
Method - worked on XRD and DSC

@@
 \subsection{\acrshort{dsc} characterization}
-Isochronic DSC (204 F1 Phoenix, Netzsch, Selb, Germany) was carried out in aluminium crucibles under protective argon atmosphere. Scans were performed at heating rates of 5 to 100 K/min.
+Isochronic DSC (204 F1 Phoenix, Netzsch, Selb, Germany) was carried out in aluminium crucibles under protective argon atmosphere.
+Scans were performed at heating rates of 5 to 100 K/min.
+Film samples were deposited directly into the pan.
+For annealing XRD samples DSC samples were heated to desired temperature at 20 K/min and then quenched to room temperature before the XRD measurements.
 
@@
 
-The temperature was raised in 5 K increments at 20 K/min. scans of xx over a range of 31 - 60 2 theta allows 20 minute scans.
+The temperature was raised in 5 K increments at 20 K/min. Scans from 31 - 60 2 theta were completed within 1092 seconds (18min 12sec) to minimise the effects of recrystallisation.
 
@@
 		\midrule
-		100 & 136.1 & 163.4 & 205.2 & 217.2 & 251.2 & 270.6 \\ 
-		80 & 132.0 & 159.5 & 201.5 & 213.7 & 245.3 & 266.0 \\ 
-		60 & 129.6 & 157.4 & 199.1 & 210.9 & 240.6 & 261.8 \\ 
-		40 & 126.6 & 155.0 & 196.3 & 208.0 & 234.8 & 256.3 \\ 
-		30 & 126.2 & 151.1 & 193.7 & 204.8 & 230.5 & 252.3 \\ 
-		20 & 125.1 & 149.8 & 190.9 & 201.4 & 224.1 & 247.5 \\ 
-		15 & 123.8 & 148.5 & 189.2 & 199.3 & 220.7 & 244.4 \\ 
-		10 & 123.5 & 144.7 & 186.1 & 195.9 & 215.4 & 240.2 \\ 
-		5 & 120.5 & 141.7 & 181.9 & 189.8 & 204.5 & 232.8 \\ 
+		100 & 136.1 & 152.4 & 193.4 & 201.8 & 240.2 & 262.4 \\
+		80  & 132.0 & 151.6 & 194.4 & 201.9 & 238.2 & 260.3 \\
+		60  & 129.6 & 151.6 & 190.0 & 197.8 & 232.9 & 259.0 \\
+		40  & 126.6 & 151.0 & 189.0 & 200.0 & 226.4 & 254.7 \\
+		30  & 126.2 & 147.4 & 187.0 & 198.4 & 221.0 & 251.1 \\
+		20  & 125.1 & 147.3 & 188.4 & 197.0 & 216.0 & 246.8 \\
+		15  & 123.8 & 146.0 & 186.2 & 195.6 & 212.2 & 243.9 \\
+		10  & 123.5 & 142.3 & 183.4 & 192.9 & 207.4 & 239.8 \\
+		5   & 120.5 & 139.2 & 179.7 & 187.5 & 199.8 & 232.7 \\ 
 		\bottomrule
@@
 	\label{tab:BulkOnsets}
+\end{table}
+
+\begin{table}[h]
+	\centering
+	\begin{tabular}{ c c c c c c c }
+		\toprule
+		Heating Rate \acrshort{ht} & \acrshort{Tg} & $T_{x1}$ & $T_{x2}$ & $T_{x3}$ & $T_{x4}$ & $T_{x5}$ \\ 
+		$K/min$ & & & & & & \\
+		\midrule
+		100 & 108.5 & 135.1 & 0.0 & 177.3 & 0.0 & 240.3 \\
+		80  & 106.0 & 128.2 & 0.0 & 165.6 & 0.0 & 238.8 \\
+		60  & 107.3 & 129.1 & 0.0 & 176.1 & 0.0 & 237.8 \\
+		40  & 100.2 & 117.6 & 0.0 & 170.7 & 0.0 & 234.2 \\
+		30  & 95.3  & 114.4 & 0.0 & 169.5 & 0.0 & 232.5 \\
+		20  & 95.5  & 110.0 & 0.0 & 170.5 & 0.0 & 229.4 \\
+		15  & 92.5  & 107.4 & 0.0 & 168.8 & 0.0 & 224.0 \\
+		\bottomrule
+	\end{tabular}
+	\caption{Film \MgZnCa~ alloy onset temperatures for the various \acrshort{dsc} \acrlongpl{ht} \acrshort{ht}. All temperatures are in \degree C.}
+	\label{tab:DSCOnsets}
 \end{table}

### 2017-07-27 Paper01_EnthalpyAndCrystallization.tex
Method - turned into sentences

@@
 The alloy was prepared by induction melting in boron nitride coated graphite crucibles, purged with Ar (99.997 vol.\% purity) five times, and protected with a circulating Ar atmosphere.
-Alloy homogeneity was ensured through heating and cooling through a cycle of 700\degree C, 385\degree C, 650\degree C, 385\degree C, 650\degree C to a casting temperature of 500 \degree C and 450\degree C for for injection and gravity casting respectively.
-Bulk amorphous \MgZnCa~ rod of $2.5 mm$ diameter and plates of thickness of $XX \mu m$ was produced by copper mold injection casting.
-The $25.4 mm$ diameter targets were prepared from a cylindrical copper mold gravity casting sectioned to thicknesses of $3.25 mm$.
+Alloy homogeneity was ensured by heating and cooling through a cycle of 700\degree C, 385\degree C, 650\degree C, 385\degree C, 650\degree C to a casting temperature of 500 \degree C and 450\degree C for for injection and gravity casting respectively.
+Bulk amorphous \MgZnCa~ rod of $2.5 mm$ diameter and plates of thickness of $XX \mu m$ were produced by copper mold injection casting.
+The $25.4 mm$ diameter targets were prepared from a cylindrical copper mold gravity castings sectioned to thicknesses of $3.25 mm$.
+All samples and targets were stored under Ar (99.997 vol.\% purity) when not being examined or used.
 
@@
 Films were produced from an in-house \acrshort{dc} magnetron sputtering facility with Ar working gas (99.997 vol.\% purity).
-The power was $15W$, typical voltage of $290-350V$, nominal chamber pressure 1 bar, temperature of 25 \degree C, Ar flow 3.01 \gls{sccm}.
-Depositions were onto Al substrates for a period of 35 minutes.
+The power was $15W$, typical voltage of $290-350V$, nominal chamber pressure of 1 bar, substrate temperature of 25 \degree C, and Ar flow of 3.01 \acrshort{sccm}.
+Films were deposited directly onto to Al \acrshort{dsc} lid substrates.
+Depositions were for a period of 35 minutes.
+Deposition rate was estimated at $1.2 nm/s$.
 
 \subsection{\acrshort{dsc} characterization}
-Isochronic DSC (204 F1 Phoenix, Netzsch, Selb, Germany) was carried out in aluminium crucibles under protective argon atmosphere.
-Scans were performed at heating rates of 5 to 100 K/min.
-Film samples were deposited directly into the pan.
-For annealing XRD samples DSC samples were heated to desired temperature at 20 K/min and then quenched to room temperature before the XRD measurements.
+Isochronic \acrshort{dsc} (204 F1 Phoenix, Netzsch, Selb, Germany) was carried out in aluminium crucibles under a protective Ar (99.997 vol.\% purity) atmosphere.
+Scans were performed at heating rates of $5$ to $100 K/min$.
+
+For annealed \acrshort{xrd} the samples were heat treated in the \acrshort{dsc} by heating to the desired temperature at $20 K/min$ followed by quenching to room temperature.
 
 \subsection{\acrshort{xrd} characterization}
-Annealing XRD (PANalytical Empyrean) with a Cu $K_{\alpha}$ X-ray source ($\lambda = 1.541 \angstrom$ ). Generator Voltage 45, Tube Current 40, Scan Step Size 0.0262606, Time per step 397.29.
+Annealing \acrshort{xrd} (PANalytical, Empyrean, Cu $K_{\alpha}$ X-ray source, $\lambda = 1.541 \angstrom$) was performed at room temperature. 
+(Generator Voltage 45, Tube Current 40, Scan Step Size 0.0262606, Time per Step 397.29).
 
-Dynamic XRD (Bruker D8) with a Cu $K_{\alpha}$ X-ray source ($\lambda = 1.541 \angstrom$ ). Generator Voltage 45, Tube Current 100, Scan Step Size 0.02, Time per step 134.4.
-
-The temperature was raised in 5 K increments at 20 K/min. Scans from 31 - 60 2 theta were completed within 1092 seconds (18min 12sec) to minimise the effects of recrystallisation.
+Dynamic \acrshort{xrd} (Bruker, D8, Cu $K_{\alpha}$ X-ray source, $\lambda = 1.541 \angstrom$) was performed by raising temperature at a rate of $20 K/min$ and performing scans \textit{in situ}.
+The first scan was performed at 35 \degree C, then 75 \degree C, after which temperature was raised in $5K$ increments.
+The $2 \theta$ scans from $31 - 60$\degree~ were completed within $1092 sec$ ($18min,~ 12sec$) to minimise the effects of recrystallisation during the experiment.
+(Generator Voltage 45, Tube Current 100, Scan Step Size 0.02, Time per Step 134.4).
 

### 2017-07-27 Paper01_EnthalpyAndCrystallization.tex
Images - All but Dynmaic XRD split into single images

@@
 
-%code to put 2 images side by side in a figure
+%single image
 \begin{figure}[b]
 	\centering
-	%Image 1
-	\begin{subfigure}[htbp]{0.495\textwidth}
-		\includegraphics[width=\textwidth]{DSC_Fragility_Bulk.png}
-		\caption{}
+	\includegraphics[width=0.55\textwidth]{DSC_Fragility_Bulk.png}
+	\caption[Table of contents Capition]{Bulk \MgZnCa~ relaxed at 120 \degree C for 10 minutes and heated at various heating rates.
+The insert stacks the \gls{dsc} curves and labels the \Tg~ and \Tx es of the $100 K/min$ sample.}%global caption
 	\label{fig:DSC_vHeatingRate_Bulk}
-	\end{subfigure}
-	%Image 2
-	\begin{subfigure}[htbp]{0.495\textwidth}
-		\includegraphics[width=\textwidth]{Bulk_Onset_Peaks_Relaxed_120C.png}
-		\caption{}
-		\label{fig:DSC_Onsets_Bulk}
-	\end{subfigure}
-	\caption{(a) Bulk \MgZnCa~ relaxed at 120 \degree C for 10 minutes and heated at various heating rates.
-The insert stacks the \gls{dsc} curves and labels the \Tg~ and \Tx es of the $100 K/min$ sample.
-(b) The \Tg s and \Tx es of the bulk \MgZnCa~ at all heating rates.
-}%global caption
-	\label{fig:DSC_Bulk}
 \end{figure}
 
-%code to put 2 images side by side in a figure
+%single image
 \begin{figure}[b]
 	\centering
-	%Image 1
-	\begin{subfigure}[htbp]{0.495\textwidth}
-		\includegraphics[width=\textwidth]{DSC_Fragility_Film.png}
-		\caption{}
+	\includegraphics[width=0.55\textwidth]{DSC_Fragility_Bulk.png}
+	\caption[Table of contents Capition]{Unrelaxed film \MgZnCa~ heated at various heating rates.
+The insert stacks the \gls{dsc} curves and labels the \Tg~ and \Tx es of the $100 K/min$ sample.}%global caption
 	\label{fig:DSC_vHeatingRate_Film}
-	\end{subfigure}
-	%Image 2
-	\begin{subfigure}[htbp]{0.495\textwidth}
-		\includegraphics[width=\textwidth]{Onsets_BulkandFilm.png}
-		\caption{}
-		\label{fig:DSC_Onsets_Film}
-	\end{subfigure}
-	\caption{(a) Unrelaxed film \MgZnCa~ heated at various heating rates.
-The insert stacks the \gls{dsc} curves and labels the \Tg~ and \Tx es of the $100 K/min$ sample.
-(b) The \Tg s and \Tx es of the bulk and film \MgZnCa~ at all heating rates.
-}%global caption
-	\label{fig:DSC_Film}
+\end{figure}
+
+%single image
+\begin{figure}[b]
+	\centering
+	\includegraphics[width=0.55\textwidth]{Bulk_Onset_Peaks_Relaxed_120C.png}
+	\caption[Table of contents Capition]{The \Tg s and \Tx es of the bulk \MgZnCa~ at all heating rates. }%global caption
+	\label{fig:DSC_Onsets_Bulk}
+\end{figure}
+
+%single image
+\begin{figure}[b]
+	\centering
+	\includegraphics[width=0.55\textwidth]{Onsets_BulkandFilm.png}
+	\caption[Table of contents Capition]{The \Tg s and \Tx es of the bulk and film \MgZnCa~ at all heating rates. }%global caption
+	\label{fig:DSC_Onsets_BulkFilm}
 \end{figure}

### 2017-07-28 Paper01_EnthalpyAndCrystallization.tex
Method - Added Stylus Profiler

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\twocolumn
 
@@
 The $25.4 mm$ diameter targets were prepared from a cylindrical copper mold gravity castings sectioned to thicknesses of $3.25 mm$.
-All samples and targets were stored under Ar (99.997 vol.\% purity) when not being examined or used.
+All samples and targets were stored under Ar when not being examined or used.
 
@@
 
+\subsection{Stylus Profiler}
+Nominal film thickness was measure by a stylus profiler (Dektak 2A, Bruker, Germany).
+A glass slide was placed under the substrates within the sputtering chamber, allowing the substrates to act as a mask.
+Profile measurements were taken by measuring the height difference between the bare glass and the film covered glass.
+This film thickness was used to estimate the sputter deposition rate.
+
 \subsection{\acrshort{dsc} characterization}
-Isochronic \acrshort{dsc} (204 F1 Phoenix, Netzsch, Selb, Germany) was carried out in aluminium crucibles under a protective Ar (99.997 vol.\% purity) atmosphere.
+Isochronic \acrshort{dsc} (204 F1 Phoenix, Netzsch, Selb, Germany) was carried out in Al crucibles under a protective Ar (99.997 vol.\% purity) atmosphere.
 Scans were performed at heating rates of $5$ to $100 K/min$.
 
-For annealed \acrshort{xrd} the samples were heat treated in the \acrshort{dsc} by heating to the desired temperature at $20 K/min$ followed by quenching to room temperature.
+For annealed \acrshort{xrd} the samples were heat treated in the \acrshort{dsc} by heating to the desired temperature at $20 K/min$ followed by Ar quenching to room temperature.
 
@@
 
-deposition were for 35 minutes, and saw an average temperature rise of $3 - 4$ \degree C during the deposition. Nominal film thickness was about $2.5 \mu m$ giving a deposition rate of $1.2 nm/s$.
+During the 35 minute depositions an average temperature rise of $3 - 4$ \degree C was observed. Nominal film thickness was about $2.5 \mu m$ giving a deposition rate of $1.2 nm/s$.
 

### 2017-07-28 Paper01_EnthalpyAndCrystallization.tex
Results - Added basic deposition results

@@
 
-During the 35 minute depositions an average temperature rise of $3 - 4$ \degree C was observed. Nominal film thickness was about $2.5 \mu m$ giving a deposition rate of $1.2 nm/s$.
+From the 35 minute depositions a nominal film thickness of $2.5 \mu m$ was obtained, giving a deposition rate of approximately $1.2 nm/s$.
+The temperature within the chamber was found to rise of $3 - 4$ \degree C, significantly less than the expected $20K$ suggested by similar set ups \cite{Wang2014}.
+
+\acrshort{eds} anaylsis showed the composition of bulk and film \MgZnCa~ was approximately the same.
 

### 2017-07-28 Paper01_EnthalpyAndCrystallization.tex
Method - added EDS

@@
 
-\subsection{Stylus Profiler}
+\subsection{Stylus profiler analysis}
 Nominal film thickness was measure by a stylus profiler (Dektak 2A, Bruker, Germany).
@@
 This film thickness was used to estimate the sputter deposition rate.
+
+\subsection{\acrshort{eds} analysis}
+Alloy composition and homogeneity were confirmed by \acrshort{sem}-\acrshort{eds} (S3400, Hitachi, ?Japan?).
+Hyper-maps were collected with a accelerating voltage of $15-20kV$, and a probe current of $50units?$.
 
@@
 \subsection{\acrshort{xrd} characterization}
-Annealing \acrshort{xrd} (PANalytical, Empyrean, Cu $K_{\alpha}$ X-ray source, $\lambda = 1.541 \angstrom$) was performed at room temperature. 
+Annealing \acrshort{xrd} (Empyrean, PANalytical, Cu $K_{\alpha}$ X-ray source, $\lambda = 1.541 \angstrom$) was performed at room temperature. 
 (Generator Voltage 45, Tube Current 40, Scan Step Size 0.0262606, Time per Step 397.29).
 
-Dynamic \acrshort{xrd} (Bruker, D8, Cu $K_{\alpha}$ X-ray source, $\lambda = 1.541 \angstrom$) was performed by raising temperature at a rate of $20 K/min$ and performing scans \textit{in situ}.
+Dynamic \acrshort{xrd} (D8, Bruker, Cu $K_{\alpha}$ X-ray source, $\lambda = 1.541 \angstrom$) was performed by raising temperature at a rate of $20 K/min$ and performing scans \textit{in situ}.
 The first scan was performed at 35 \degree C, then 75 \degree C, after which temperature was raised in $5K$ increments.

### 2017-07-28 Paper01_EnthalpyAndCrystallization.tex
Fixed errors in Tg and Tx1 for bulk and film, table and Fig 1, 2
Results - Added EDS table results

@@
 
-\acrshort{eds} anaylsis showed the composition of bulk and film \MgZnCa~ was approximately the same.
+\acrshort{eds} analysis shows the nominal composition of bulk and film \MgZnCa~ is approximately the same.
+
+\begin{table}[h]
+	\centering
+	\begin{tabular}{ c c c }
+		\toprule
+		\acrshort{eds} Analysis & Bulk (at\%)  & Film (at\%)  \\
+		\midrule
+		Mg & $64.85 \pm 3.18$ & $62.92 \pm 3.24$ \\
+		Zn & $29.55 \pm 0.82$ & $31.17 \pm 0.95$ \\
+		Ca & $~~ 5.60 \pm 0.17$ & $~~ 5.91 \pm 0.19$ \\ 
+		\bottomrule
+	\end{tabular}
+	\caption{\acrshort{eds} composition of bulk and film \MgZnCa~ in atomic weight percent.}
+	\label{tab:EDS_Composition}
+\end{table}
 
@@
 		\midrule
-		100 & 136.1 & 152.4 & 193.4 & 201.8 & 240.2 & 262.4 \\
-		80  & 132.0 & 151.6 & 194.4 & 201.9 & 238.2 & 260.3 \\
-		60  & 129.6 & 151.6 & 190.0 & 197.8 & 232.9 & 259.0 \\
-		40  & 126.6 & 151.0 & 189.0 & 200.0 & 226.4 & 254.7 \\
-		30  & 126.2 & 147.4 & 187.0 & 198.4 & 221.0 & 251.1 \\
-		20  & 125.1 & 147.3 & 188.4 & 197.0 & 216.0 & 246.8 \\
-		15  & 123.8 & 146.0 & 186.2 & 195.6 & 212.2 & 243.9 \\
-		10  & 123.5 & 142.3 & 183.4 & 192.9 & 207.4 & 239.8 \\
-		5   & 120.5 & 139.2 & 179.7 & 187.5 & 199.8 & 232.7 \\ 
+		100 & 136.1 & 164.8 & 193.4 & 201.8 & 240.2 & 262.4 \\
+		80  & 132.0 & 160.0 & 194.4 & 201.9 & 238.2 & 260.3 \\
+		60  & 129.6 & 157.7 & 190.0 & 197.8 & 232.9 & 259.0 \\
+		40  & 126.6 & 155.2 & 189.0 & 200.0 & 226.4 & 254.7 \\
+		30  & 126.2 & 151.5 & 187.0 & 198.4 & 221.0 & 251.1 \\
+		20  & 125.1 & 149.8 & 188.4 & 197.0 & 216.0 & 246.8 \\
+		15  & 123.8 & 148.3 & 186.2 & 195.6 & 212.2 & 243.9 \\
+		10  & 123.5 & 144.5 & 183.4 & 192.9 & 207.4 & 239.8 \\
+		5   & 120.5 & 141.1 & 179.7 & 187.5 & 199.8 & 232.7 \\ 
 		\bottomrule
@@
 		\midrule
-		100 & 108.5 & 135.1 & 0.0 & 177.3 & 0.0 & 240.3 \\
-		80  & 106.0 & 128.2 & 0.0 & 165.6 & 0.0 & 238.8 \\
-		60  & 107.3 & 129.1 & 0.0 & 176.1 & 0.0 & 237.8 \\
-		40  & 100.2 & 117.6 & 0.0 & 170.7 & 0.0 & 234.2 \\
-		30  & 95.3  & 114.4 & 0.0 & 169.5 & 0.0 & 232.5 \\
-		20  & 95.5  & 110.0 & 0.0 & 170.5 & 0.0 & 229.4 \\
-		15  & 92.5  & 107.4 & 0.0 & 168.8 & 0.0 & 224.0 \\
+		100 & 108.5 & 128.6 &  & 177.3 &  & 240.3 \\
+		80  & 106.0 & 121.2 &  & 165.6 &  & 238.8 \\
+		60  & 107.3 & 134.0 &  & 176.1 &  & 237.8 \\
+		40  & 100.2 & 119.8 &  & 170.7 &  & 234.2 \\
+		30  & 95.3  & 110.4 &  & 169.5 &  & 232.5 \\
+		20  & 95.5  & 115.2 &  & 170.5 &  & 229.4 \\
+		15  & 92.5  & 113.5 &  & 168.8 &  & 224.0 \\
 		\bottomrule
@@
 	\centering
-	\includegraphics[width=0.55\textwidth]{DSC_Fragility_Bulk.png}
+	\includegraphics[width=0.65\textwidth]{DSC_Fragility_Bulk.png}
 	\caption[Table of contents Capition]{Bulk \MgZnCa~ relaxed at 120 \degree C for 10 minutes and heated at various heating rates.
@@
 	\centering
-	\includegraphics[width=0.55\textwidth]{DSC_Fragility_Bulk.png}
+	\includegraphics[width=0.65\textwidth]{DSC_Fragility_Film.png}
 	\caption[Table of contents Capition]{Unrelaxed film \MgZnCa~ heated at various heating rates.

### 2017-07-28 Paper01_EnthalpyAndCrystallization.tex
Results - Fragility - worked on writting and put in fits for both bulk and film

@@
 From the 35 minute depositions a nominal film thickness of $2.5 \mu m$ was obtained, giving a deposition rate of approximately $1.2 nm/s$.
-The temperature within the chamber was found to rise of $3 - 4$ \degree C, significantly less than the expected $20K$ suggested by similar set ups \cite{Wang2014}.
+The temperature within the chamber was found to rise $3 - 4$\degree C, significantly less than the expected $20K$ suggested by similar setups \cite{Wang2014}.
 
-\acrshort{eds} analysis shows the nominal composition of bulk and film \MgZnCa~ is approximately the same.
+\acrshort{eds} analysis shows good agreement in the nominal composition for both the bulk and film \MgZnCa, see Table \ref{tab:EDS_Composition}.
 
@@
 \end{table}
-
-Relaxed \gls{dsc} of bulk material taken at different heating rates was used to establish the fragility of the \MgZnCa~ system. From the equations ... a fit of
-$\beta^{-1} = 1.338E - 16e^{5274 (\frac{1}{T-T_{0}})}$ with Adj. $R^{2}=0.972$ was established. This give a $D^{*}=20.4$ which using $D^{*}=590/(m-16)$ Shuai2014 [4, 5] gives a fragility $m=44.9$.
 
@@
 \end{figure}
+
+Variable heating rate \acrshort{dsc} for both the bulk and film \MgZnCa~ was used to establish the fragility of the system.
+Numerical solutions where used to fit the equation $\beta^{-1} = \tau_{0}~ e^{(\frac{D^{*}T_{0}}{T-T_{0}})}$ [source] for both the bulk and film.
+The fragility $m$ could then be calcuated from the relationship $D^{*}=590/(m-16)$ Shuai2014 [4, 5].
+
+For the bulk it was found $\beta^{-1} = 1.338E - 16e^{5274 (\frac{1}{T-T_{0}})}$ with Adj.
+$R^{2}=0.972$, giving a $D^{*}=20.4$, and a fragility $m=44.9$.
+For the film $\beta^{-1} = 5.921E - 11e^{2766 (\frac{1}{T-T_{0}})}$ with Adj.
+$R^{2}=0.861$, giving a $D^{*}=10.0$, and fragility $m=75.0$.
+See Figure \ref{fig:Fragility_BulkFilm_mValue}.
 

### 2017-08-01 Paper01_EnthalpyAndCrystallization.tex
Method - minor typos and edits

@@
 The alloy was prepared by induction melting in boron nitride coated graphite crucibles, purged with Ar (99.997 vol.\% purity) five times, and protected with a circulating Ar atmosphere.
-Alloy homogeneity was ensured by heating and cooling through a cycle of 700\degree C, 385\degree C, 650\degree C, 385\degree C, 650\degree C to a casting temperature of 500 \degree C and 450\degree C for for injection and gravity casting respectively.
-Bulk amorphous \MgZnCa~ rod of $2.5 mm$ diameter and plates of thickness of $XX \mu m$ were produced by copper mold injection casting.
+Alloy homogeneity was ensured by heating and cooling through a cycle of 700\degree C, 385\degree C, 650\degree C, 385\degree C, 650\degree C to a casting temperature of 500 \degree C and 450\degree C for injection and gravity casting respectively.
+Bulk amorphous \MgZnCa~ rods of $2.5 mm$ diameter and plates of thickness of $XX \mu m$ were produced by copper mold injection casting.
 The $25.4 mm$ diameter targets were prepared from a cylindrical copper mold gravity castings sectioned to thicknesses of $3.25 mm$.
@@
 Films were produced from an in-house \acrshort{dc} magnetron sputtering facility with Ar working gas (99.997 vol.\% purity).
-The power was $15W$, typical voltage of $290-350V$, nominal chamber pressure of 1 bar, substrate temperature of 25 \degree C, and Ar flow of 3.01 \acrshort{sccm}.
+The power was $15W$, typical voltage of $290-350V$, nominal chamber pressure of 1 bar, substrate temperature of $25$\degree C, and Ar flow of 3.01 \acrshort{sccm}.
 Films were deposited directly onto to Al \acrshort{dsc} lid substrates.
@@
 A glass slide was placed under the substrates within the sputtering chamber, allowing the substrates to act as a mask.
-Profile measurements were taken by measuring the height difference between the bare glass and the film covered glass.
+Profile measurements were taken by measuring the height difference between the bare glass and the film coated glass.
 This film thickness was used to estimate the sputter deposition rate.
@@
 Alloy composition and homogeneity were confirmed by \acrshort{sem}-\acrshort{eds} (S3400, Hitachi, ?Japan?).
-Hyper-maps were collected with a accelerating voltage of $15-20kV$, and a probe current of $50units?$.
+Hyper-maps were collected with a accelerating voltage of $15-20kV$, and a probe current of $50 \mu A$.
+(Conditions; counts were 5000 kps or better, dead time was less than 20 \%, and working distance was 10mm).
 
 \subsection{\acrshort{dsc} characterization}
-Isochronic \acrshort{dsc} (204 F1 Phoenix, Netzsch, Selb, Germany) was carried out in Al crucibles under a protective Ar (99.997 vol.\% purity) atmosphere.
+Isochronic \acrshort{dsc} (204 F1 Phoenix, Netzsch, Selb, Germany) was carried out in Al crucibles under a protective Ar atmosphere (99.997 vol.\% purity).
 Scans were performed at heating rates of $5$ to $100 K/min$.
@@
 Dynamic \acrshort{xrd} (D8, Bruker, Cu $K_{\alpha}$ X-ray source, $\lambda = 1.541 \angstrom$) was performed by raising temperature at a rate of $20 K/min$ and performing scans \textit{in situ}.
-The first scan was performed at 35 \degree C, then 75 \degree C, after which temperature was raised in $5K$ increments.
+The first scan was performed at $35$\degree C, then $75$\degree C, after which temperature was raised in $5K$ increments until reaching the peak temperature at $185$\degree C.
 The $2 \theta$ scans from $31 - 60$\degree~ were completed within $1092 sec$ ($18min,~ 12sec$) to minimise the effects of recrystallisation during the experiment.

### 2017-08-01 Paper01_EnthalpyAndCrystallization.tex
Figures - Added deconvolution figures in a 3x3 grid

@@
 
+Both the bulk and film \MgZnCa~ were examined at various \acrshort{dsc} heating rates to observe changed in the \Tg and \Tx temperatures.
+As expected higher heating rates resulted endothermic peaks shifting to higher temperatures and curve convolution.
+
+Numerical solutions were used to deconvolution the \acrshort{dsc} data so the various \Tx onsets could be determined.
+The results of the deconvolution are presented in Table \ref{tab:BulkOnsets} for the bulk and Table \ref{tab:FilmOnsets} for the film.
+
 \begin{table}[h]
@@
 	\caption{Film \MgZnCa~ alloy onset temperatures for the various \acrshort{dsc} \acrlongpl{ht} \acrshort{ht}. All temperatures are in \degree C.}
-	\label{tab:DSCOnsets}
+	\label{tab:FilmOnsets}
 \end{table}
@@
 Numerical solutions where used to fit the equation $\beta^{-1} = \tau_{0}~ e^{(\frac{D^{*}T_{0}}{T-T_{0}})}$ [source] for both the bulk and film.
-The fragility $m$ could then be calcuated from the relationship $D^{*}=590/(m-16)$ Shuai2014 [4, 5].
+The fragility $m$ could then be calculated from the relationship $D^{*}=590/(m-16)$ Shuai2014 [4, 5].
 
@@
 
+%MultiFigure
+\begin{figure}[b]
+	\centering
+	\includegraphics[width=.3\textwidth]{input_Raw_Bulk_NoLeveling_5Ks_result_A5lsc.png}\quad
+	\includegraphics[width=.3\textwidth]{input_Raw_Bulk_NoLeveling_10Ks_result_A5lsc.png}\quad
+	\includegraphics[width=.3\textwidth]{input_Raw_Bulk_NoLeveling_15Ks_result_A5lsc.png}
+
+	\medskip
+
+	\includegraphics[width=.3\textwidth]{input_Raw_Bulk_NoLeveling_20Ks_result_A5lsc.png}\quad
+	\includegraphics[width=.3\textwidth]{input_Raw_Bulk_NoLeveling_30Ks_result_A5lsc.png}\quad
+	\includegraphics[width=.3\textwidth]{input_Raw_Bulk_NoLeveling_40Ks_result_A5lsc.png}
+
+	\medskip
+
+	\includegraphics[width=.3\textwidth]{input_Raw_Bulk_NoLeveling_60Ks_result_A5lsc.png}\quad
+	\includegraphics[width=.3\textwidth]{input_Raw_Bulk_NoLeveling_80Ks_result_A5lsc.png}\quad
+	\includegraphics[width=.3\textwidth]{input_Raw_Bulk_NoLeveling_100Ks_result_A5lsc.png}
+
+	\caption{\acrshort{dsc} deconvolution for the bulk. From left to right, top to bottom, 5, 10, 15, 20, 30, 40, 60, 80, 100 K/min.}
+	\label{fig:DSC_Bulk_Decon}
+\end{figure}
+
+%MultiFigure
+\begin{figure}[b]
+	\centering
+	\includegraphics[width=.3\textwidth]{input_Raw_Film_NoLeveling_15Ks_result_A5lsc.png}\quad
+	\includegraphics[width=.3\textwidth]{input_Raw_Film_NoLeveling_20Ks_result_A5lsc.png}\quad
+	\includegraphics[width=.3\textwidth]{input_Raw_Film_NoLeveling_30Ks_result_A5lsc.png}
+
+	\medskip
+
+	\includegraphics[width=.3\textwidth]{input_Raw_Film_NoLeveling_40Ks_result_A5lsc.png}\quad
+	\includegraphics[width=.3\textwidth]{input_Raw_Film_NoLeveling_60Ks_result_A5lsc.png}\quad
+	\includegraphics[width=.3\textwidth]{input_Raw_Film_NoLeveling_80Ks_result_A5lsc.png}
+
+	\medskip
+
+	\includegraphics[width=.3\textwidth]{input_Raw_Film_NoLeveling_100Ks_result_A5lsc.png}
+
+	\caption{\acrshort{dsc} deconvolution for the film. From left to right, top to bottom, 15, 20, 30, 40, 60, 80, 100 K/min.}
+	\label{fig:DSC_Film_Decon}
+\end{figure}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 The use of a 60K \gls{dsc} heating rate compared to the more commonly used 20K rate [sources] shifts peaks for the bulk \MgZnCa~ alloy about 8 - 15 degrees higher.
-This higher heating rates were used because crystallization events for the films were different to differentiation at the lower heating rate.
+This higher heating rates were used because crystallization events for the films were difficult to differentiation at the lower heating rate.
 Films show little shift to high temperature peaks with increases heating rates, but large shifts with relaxation. 

### 2017-08-02 Paper01_EnthalpyAndCrystallization.tex
Figures - added decon onsets and enthalpy curve plots
Results - Added subsections to outline, and moved figures to relivent sections
Results - Fraglity - Added sources for the formulas used

@@
-\documentclass[a4paper,12pt,oneside]{article}%FinalView
-%\documentclass[draft,a4paper,12pt,oneside]{article}%draftView
+%\documentclass[a4paper,12pt,oneside]{article}%FinalView
+\documentclass[draft,a4paper,12pt,oneside]{article}%draftView
 
@@
 \section{RESULTS}
+\subsection{Alloy composition}
 
@@
 \end{table}
+
+\subsection{\acrshort{dsc}}
+\subsubsection{Isothermal \acrshort{dsc}}
+
+%single image
+\begin{figure}[b]
+	\centering
+	\includegraphics[width=0.65\textwidth]{DSC_Fragility_Bulk.png}
+	\caption[Table of contents Capition]{Bulk \MgZnCa~ relaxed at 120 \degree C for 10 minutes and heated at various heating rates.
+The insert stacks the \gls{dsc} curves and labels the \Tg~ and \Tx es of the $100 K/min$ sample.}%global caption
+	\label{fig:DSC_vHeatingRate_Bulk}
+\end{figure}
+
+%single image
+\begin{figure}[b]
+	\centering
+	\includegraphics[width=0.65\textwidth]{DSC_Fragility_Film.png}
+	\caption[Table of contents Capition]{Unrelaxed film \MgZnCa~ heated at various heating rates.
+The insert stacks the \gls{dsc} curves and labels the \Tg~ and \Tx es of the $100 K/min$ sample.}%global caption
+	\label{fig:DSC_vHeatingRate_Film}
+\end{figure}
+
+\subsubsection{Fragility}
+
+Variable heating rate \acrshort{dsc} for both the bulk and film \MgZnCa~ was used to establish the fragility of the system.
+Numerical solutions where used to fit the equation $\beta^{-1} = \tau_{0}~ e^{(\frac{D^{*}T_{0}}{T-T_{0}})}$ \cite{Busch1998} for both the bulk and film.
+The fragility $m$ could then be calculated from the relationship $D^{*}=590/(m-16)$ \cite{Angell2002, Wei2014}.
+
+For the bulk it was found $\beta^{-1} = 1.338E - 16e^{5274 (\frac{1}{T-T_{0}})}$ with Adj.
+$R^{2}=0.972$, giving a $D^{*}=20.4$, and a fragility $m=44.9$.
+For the film $\beta^{-1} = 5.921E - 11e^{2766 (\frac{1}{T-T_{0}})}$ with Adj.
+$R^{2}=0.861$, giving a $D^{*}=10.0$, and fragility $m=75.0$.
+See Figure \ref{fig:Fragility_BulkFilm_mValue}.
+
+%single image
+\begin{figure}[b]
+	\centering
+	\includegraphics[width=0.95\textwidth]{Bulk_Film_Fragility.png}
+	\caption[Table of contents Capition]{Fitted fragility for the \MgZnCa system obtained by \acrshort{dsc} at various heating rates}
+	\label{fig:Fragility_BulkFilm_mValue}
+\end{figure}
+
+\subsection{\acrshort{dsc} deconvolution}
+
+%MultiFigure
+\begin{figure}[b]
+	\centering
+	\includegraphics[width=.3\textwidth]{input_Raw_Bulk_NoLeveling_5Ks_result_A5lsc.png}\quad
+	\includegraphics[width=.3\textwidth]{input_Raw_Bulk_NoLeveling_10Ks_result_A5lsc.png}\quad
+	\includegraphics[width=.3\textwidth]{input_Raw_Bulk_NoLeveling_15Ks_result_A5lsc.png}
+	\medskip
+	\includegraphics[width=.3\textwidth]{input_Raw_Bulk_NoLeveling_20Ks_result_A5lsc.png}\quad
+	\includegraphics[width=.3\textwidth]{input_Raw_Bulk_NoLeveling_30Ks_result_A5lsc.png}\quad
+	\includegraphics[width=.3\textwidth]{input_Raw_Bulk_NoLeveling_40Ks_result_A5lsc.png}
+	\medskip
+	\includegraphics[width=.3\textwidth]{input_Raw_Bulk_NoLeveling_60Ks_result_A5lsc.png}\quad
+	\includegraphics[width=.3\textwidth]{input_Raw_Bulk_NoLeveling_80Ks_result_A5lsc.png}\quad
+	\includegraphics[width=.3\textwidth]{input_Raw_Bulk_NoLeveling_100Ks_result_A5lsc.png}
+	\caption{\acrshort{dsc} deconvolution for the bulk. From left to right, top to bottom, 5, 10, 15, 20, 30, 40, 60, 80, 100 K/min.}
+	\label{fig:DSC_Bulk_Decon}
+\end{figure}
+
+%MultiFigure
+\begin{figure}[b]
+	\centering
+	\includegraphics[width=.3\textwidth]{input_Raw_Film_NoLeveling_15Ks_result_A5lsc.png}\quad
+	\includegraphics[width=.3\textwidth]{input_Raw_Film_NoLeveling_20Ks_result_A5lsc.png}\quad
+	\includegraphics[width=.3\textwidth]{input_Raw_Film_NoLeveling_30Ks_result_A5lsc.png}
+	\medskip
+	\includegraphics[width=.3\textwidth]{input_Raw_Film_NoLeveling_40Ks_result_A5lsc.png}\quad
+	\includegraphics[width=.3\textwidth]{input_Raw_Film_NoLeveling_60Ks_result_A5lsc.png}\quad
+	\includegraphics[width=.3\textwidth]{input_Raw_Film_NoLeveling_80Ks_result_A5lsc.png}
+	\medskip
+	\includegraphics[width=.3\textwidth]{input_Raw_Film_NoLeveling_100Ks_result_A5lsc.png}
+	\caption{\acrshort{dsc} deconvolution for the film. From left to right, top to bottom, 15, 20, 30, 40, 60, 80, 100 K/min.}
+	\label{fig:DSC_Film_Decon}
+\end{figure}
+
+\subsubsection{Onset determination}
 
@@
 	\centering
-	\includegraphics[width=0.65\textwidth]{DSC_Fragility_Bulk.png}
-	\caption[Table of contents Capition]{Bulk \MgZnCa~ relaxed at 120 \degree C for 10 minutes and heated at various heating rates.
-The insert stacks the \gls{dsc} curves and labels the \Tg~ and \Tx es of the $100 K/min$ sample.}%global caption
-	\label{fig:DSC_vHeatingRate_Bulk}
-\end{figure}
-
-%single image
-\begin{figure}[b]
-	\centering
-	\includegraphics[width=0.65\textwidth]{DSC_Fragility_Film.png}
-	\caption[Table of contents Capition]{Unrelaxed film \MgZnCa~ heated at various heating rates.
-The insert stacks the \gls{dsc} curves and labels the \Tg~ and \Tx es of the $100 K/min$ sample.}%global caption
-	\label{fig:DSC_vHeatingRate_Film}
-\end{figure}
-
-%single image
-\begin{figure}[b]
-	\centering
 	\includegraphics[width=0.55\textwidth]{Bulk_Onset_Peaks_Relaxed_120C.png}
@@
 
-Variable heating rate \acrshort{dsc} for both the bulk and film \MgZnCa~ was used to establish the fragility of the system.
-Numerical solutions where used to fit the equation $\beta^{-1} = \tau_{0}~ e^{(\frac{D^{*}T_{0}}{T-T_{0}})}$ [source] for both the bulk and film.
-The fragility $m$ could then be calculated from the relationship $D^{*}=590/(m-16)$ Shuai2014 [4, 5].
+\subsubsection{Reaction enthalpy}
 
-For the bulk it was found $\beta^{-1} = 1.338E - 16e^{5274 (\frac{1}{T-T_{0}})}$ with Adj.
-$R^{2}=0.972$, giving a $D^{*}=20.4$, and a fragility $m=44.9$.
-For the film $\beta^{-1} = 5.921E - 11e^{2766 (\frac{1}{T-T_{0}})}$ with Adj.
-$R^{2}=0.861$, giving a $D^{*}=10.0$, and fragility $m=75.0$.
-See Figure \ref{fig:Fragility_BulkFilm_mValue}.
-
-%single image
+%MultiFigure
 \begin{figure}[b]
 	\centering
-	\includegraphics[width=0.95\textwidth]{Bulk_Film_Fragility.png}
-	\caption[Table of contents Capition]{Fitted fragility for the \MgZnCa system obtained by \acrshort{dsc} at various heating rates}
-	\label{fig:Fragility_BulkFilm_mValue}
+	\includegraphics[width=.6\textwidth]{Decon_Onsets_BR.png}
+	\medskip
+	\includegraphics[width=.6\textwidth]{Decon_peak_area_BR.png}
+	\caption{\acrshort{dsc} onset temperatures and enthalpy of formation for the bulk and film.}
+	\label{fig:DSC_Decon}
 \end{figure}
+
+\subsubsection{Relaxation enthalpy}
+
+\subsection{\acrshort{xrd}}
+\subsubsection{Annealing \acrshort{xrd}}
 
@@
 \end{figure}
+
+\subsubsection{Dynamic \acrshort{xrd}}
 
@@
 
-%MultiFigure
-\begin{figure}[b]
-	\centering
-	\includegraphics[width=.3\textwidth]{input_Raw_Bulk_NoLeveling_5Ks_result_A5lsc.png}\quad
-	\includegraphics[width=.3\textwidth]{input_Raw_Bulk_NoLeveling_10Ks_result_A5lsc.png}\quad
-	\includegraphics[width=.3\textwidth]{input_Raw_Bulk_NoLeveling_15Ks_result_A5lsc.png}
-
-	\medskip
-
-	\includegraphics[width=.3\textwidth]{input_Raw_Bulk_NoLeveling_20Ks_result_A5lsc.png}\quad
-	\includegraphics[width=.3\textwidth]{input_Raw_Bulk_NoLeveling_30Ks_result_A5lsc.png}\quad
-	\includegraphics[width=.3\textwidth]{input_Raw_Bulk_NoLeveling_40Ks_result_A5lsc.png}
-
-	\medskip
-
-	\includegraphics[width=.3\textwidth]{input_Raw_Bulk_NoLeveling_60Ks_result_A5lsc.png}\quad
-	\includegraphics[width=.3\textwidth]{input_Raw_Bulk_NoLeveling_80Ks_result_A5lsc.png}\quad
-	\includegraphics[width=.3\textwidth]{input_Raw_Bulk_NoLeveling_100Ks_result_A5lsc.png}
-
-	\caption{\acrshort{dsc} deconvolution for the bulk. From left to right, top to bottom, 5, 10, 15, 20, 30, 40, 60, 80, 100 K/min.}
-	\label{fig:DSC_Bulk_Decon}
-\end{figure}
-
-%MultiFigure
-\begin{figure}[b]
-	\centering
-	\includegraphics[width=.3\textwidth]{input_Raw_Film_NoLeveling_15Ks_result_A5lsc.png}\quad
-	\includegraphics[width=.3\textwidth]{input_Raw_Film_NoLeveling_20Ks_result_A5lsc.png}\quad
-	\includegraphics[width=.3\textwidth]{input_Raw_Film_NoLeveling_30Ks_result_A5lsc.png}
-
-	\medskip
-
-	\includegraphics[width=.3\textwidth]{input_Raw_Film_NoLeveling_40Ks_result_A5lsc.png}\quad
-	\includegraphics[width=.3\textwidth]{input_Raw_Film_NoLeveling_60Ks_result_A5lsc.png}\quad
-	\includegraphics[width=.3\textwidth]{input_Raw_Film_NoLeveling_80Ks_result_A5lsc.png}
-
-	\medskip
-
-	\includegraphics[width=.3\textwidth]{input_Raw_Film_NoLeveling_100Ks_result_A5lsc.png}
-
-	\caption{\acrshort{dsc} deconvolution for the film. From left to right, top to bottom, 15, 20, 30, 40, 60, 80, 100 K/min.}
-	\label{fig:DSC_Film_Decon}
-\end{figure}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2017-08-02 Paper01_EnthalpyAndCrystallization.tex
Results - DSC - Draft for bulk DSC done

@@
-%\documentclass[a4paper,12pt,oneside]{article}%FinalView
-\documentclass[draft,a4paper,12pt,oneside]{article}%draftView
+\documentclass[a4paper,12pt,oneside]{article}%FinalView
+%\documentclass[draft,a4paper,12pt,oneside]{article}%draftView
 
@@
 
+Isothermal relaxation \acrshort{dsc} was preformed by heating samples at $20 K/min$ to the desired annealing temperature, holding for desired time, and Ar quenching to room temperature.
+
 For annealed \acrshort{xrd} the samples were heat treated in the \acrshort{dsc} by heating to the desired temperature at $20 K/min$ followed by Ar quenching to room temperature.
@@
 \subsubsection{Isothermal \acrshort{dsc}}
+Isothermal \acrshort{dsc} was performed on the bulk and film \MgZnCa~ to examine the thermal properties.
+The bulk alloy was relaxed at $120$\degree C for 10 minutes before \acrshort{dsc} measurements to ensure the \Tg~ was clearly visible.
+The film was not relaxed as unlike the bulk the lost in free volume from relaxation would be significant and make differences between the samples much more difficult to observe [source needed???].
+
+The bulk \MgZnCa~ was examined at \glspl{ht} of 5, 10, 15, 20, 30, 40, 60, 80, and 100 $K/min$ to observe changes in the \Tg~ and \Tx s with \gls{ht}.
+As expected greater \gls{ht} resulted in greater signal strength, exothermic peaks shifting to higher start temperatures, and an increase in thermal lag resulting in later exothermic finish temperatures and curve convolution.
+With this convolution the \Tg~ and \Tx $_{1}$  remained clearly visible for all \glspl{ht}, but \Tx $_{2,4,5}$ were only visible at low \glspl{ht}, and \Tx $_{3}$ was not clear at any \gls{ht}, see Figure \ref{fig:DSC_vHeatingRate_Bulk}.
+
+START HERE. Likely talking about Films!!!
+Both the bulk and film \MgZnCa~ were examined at various \acrshort{dsc} heating rates (\acrshort{ht}) to observe changed in the \Tg~ and \Tx~ temperatures.
+As expected higher heating rates resulted in great signal strength, exothermic peaks shifting to higher temperatures, and increases in thermal lag resulting in curve convolution.
 

### 2017-08-02 Paper01_EnthalpyAndCrystallization.tex
Results - DSC - wrote draft film DSC results

@@
 
-START HERE. Likely talking about Films!!!
-Both the bulk and film \MgZnCa~ were examined at various \acrshort{dsc} heating rates (\acrshort{ht}) to observe changed in the \Tg~ and \Tx~ temperatures.
-As expected higher heating rates resulted in great signal strength, exothermic peaks shifting to higher temperatures, and increases in thermal lag resulting in curve convolution.
+The film was examined at \glspl{ht} of 15, 20, 30, 40, 60, 80, and 100 $K/min$.
+The lower \glspl{ht} of 5 and 10 $k/min$ were not utilised owing to the lower film signal compared to the bulk.
+The reduced signal was likely from the low mass of the film, about $\frac{1}{10}$ that of the bulk.
+The film showed the expected variable relationships with increasing \gls{ht} as observed in the bulk.
+The signal intensity increased at a compatible rate to bulk up until \glspl{ht} of 80 and 100 $k/min$.
+These final two \glspl{ht} showed great increases in the signal intensity.
+The exothermic peaks all convoluted together making many of thermodynamic events difficult to observer.
+The \Tg~ and \Tx $_{1}$s were less defined than for the bulk, but could still be identified for all \glspl{ht}.
+For all \glspl{ht} the \Tx $_{2-5}$ onsets could not be easily identified, see Figure \ref{fig:DSC_vHeatingRate_Film}.
 

### 2017-08-03 Paper01_EnthalpyAndCrystallization.tex
Results - DSC - fixed mixups with isochronic and isothermal PLUS minor typos

@@
 Isochronic \acrshort{dsc} (204 F1 Phoenix, Netzsch, Selb, Germany) was carried out in Al crucibles under a protective Ar atmosphere (99.997 vol.\% purity).
-Scans were performed at heating rates of $5$ to $100 K/min$.
+Scans were performed at \glspl{ht} of $5$ to $100 K/min$.
 
@@
 \subsection{\acrshort{dsc}}
-\subsubsection{Isothermal \acrshort{dsc}}
-Isothermal \acrshort{dsc} was performed on the bulk and film \MgZnCa~ to examine the thermal properties.
+\subsubsection{Isochronic \acrshort{dsc}}
+Isochronic \acrshort{dsc} was performed on the bulk and film \MgZnCa~ to examine the thermal properties.
 The bulk alloy was relaxed at $120$\degree C for 10 minutes before \acrshort{dsc} measurements to ensure the \Tg~ was clearly visible.
@@
 
-The bulk \MgZnCa~ was examined at \glspl{ht} of 5, 10, 15, 20, 30, 40, 60, 80, and 100 $K/min$ to observe changes in the \Tg~ and \Tx s with \gls{ht}.
+The bulk \MgZnCa~ was examined at \acrfullpl{ht} of 5, 10, 15, 20, 30, 40, 60, 80, and 100 $K/min$ to observe changes in the \Tg~ and the \Tx s with \gls{ht}.
 As expected greater \gls{ht} resulted in greater signal strength, exothermic peaks shifting to higher start temperatures, and an increase in thermal lag resulting in later exothermic finish temperatures and curve convolution.
@@
 These final two \glspl{ht} showed great increases in the signal intensity.
-The exothermic peaks all convoluted together making many of thermodynamic events difficult to observer.
+The exothermic peaks all convoluted together making many of the thermodynamic events difficult to observer.
+It also appeared that all exothermic events shifted to lower temperatures as compared to the bulk.
 The \Tg~ and \Tx $_{1}$s were less defined than for the bulk, but could still be identified for all \glspl{ht}.

### 2017-08-03 Paper01_EnthalpyAndCrystallization.tex
Results - Fragility - Put equtions on own line and started rewrite of section

@@
 
-Variable heating rate \acrshort{dsc} for both the bulk and film \MgZnCa~ was used to establish the fragility of the system.
-Numerical solutions where used to fit the equation $\beta^{-1} = \tau_{0}~ e^{(\frac{D^{*}T_{0}}{T-T_{0}})}$ \cite{Busch1998} for both the bulk and film.
-The fragility $m$ could then be calculated from the relationship $D^{*}=590/(m-16)$ \cite{Angell2002, Wei2014}.
+Using the isochronic \acrshort{dsc} data the fragility of the \MgZnCa~ system could be established for both the bulk and film.
+Numerical solutions where used to fit the \gls{vft} relationship for \gls{ht} \cite{Busch1998}.
+
+\begin{equation}
+	\beta^{-1} = \tau_{0}~ e^{(\frac{D^{*}T_{0}}{T_{g}-T_{0}})}
+	\label{equ:VFT}
+\end{equation}
+
+Where $\tau_{0}$ is a pre-exponential factor, $D^{*}$ is the liquid Fragility parameter, and $T_{0}$ is the \gls{vft} temperature where the barrier to flow becomes infinite.
+
+The fragility $m$ could then be calculated from Equation \ref{equ:dStar} \cite{Angell2002, Wei2014}.
+
+\begin{equation}
+	D^{*}=590/(m-16)
+	\label{equ:dStar}
+\end{equation}
 

### 2017-08-03 Paper01_EnthalpyAndCrystallization.tex
Fragility - replaced word with glossy terms

@@
 
-\subsubsection{Fragility}
+\subsubsection{\Acrlong{m}}
 
-Using the isochronic \acrshort{dsc} data the fragility of the \MgZnCa~ system could be established for both the bulk and film.
+Using the isochronic \acrshort{dsc} data the \gls{m} of the \MgZnCa~ system could be established for both the bulk and film.
 Numerical solutions where used to fit the \gls{vft} relationship for \gls{ht} \cite{Busch1998}.
@@
 
-Where $\tau_{0}$ is a pre-exponential factor, $D^{*}$ is the liquid Fragility parameter, and $T_{0}$ is the \gls{vft} temperature where the barrier to flow becomes infinite.
+Where $\tau_{0}$ is a pre-exponential factor, $D^{*}$ is the liquid \acrlong{m} parameter, and $T_{0}$ is the \gls{vft} temperature where the barrier to flow becomes infinite.
 
-The fragility $m$ could then be calculated from Equation \ref{equ:dStar} \cite{Angell2002, Wei2014}.
+The \gls{m} could then be calculated from Equation \ref{equ:dStar} \cite{Angell2002, Wei2014}.
 
@@
 For the bulk it was found $\beta^{-1} = 1.338E - 16e^{5274 (\frac{1}{T-T_{0}})}$ with Adj.
-$R^{2}=0.972$, giving a $D^{*}=20.4$, and a fragility $m=44.9$.
+$R^{2}=0.972$, giving a $D^{*}=20.4$, and a \acrlong{m} $m=44.9$.
 For the film $\beta^{-1} = 5.921E - 11e^{2766 (\frac{1}{T-T_{0}})}$ with Adj.
-$R^{2}=0.861$, giving a $D^{*}=10.0$, and fragility $m=75.0$.
+$R^{2}=0.861$, giving a $D^{*}=10.0$, and \acrlong{m} $m=75.0$.
 See Figure \ref{fig:Fragility_BulkFilm_mValue}.
@@
 	\includegraphics[width=0.95\textwidth]{Bulk_Film_Fragility.png}
-	\caption[Table of contents Capition]{Fitted fragility for the \MgZnCa system obtained by \acrshort{dsc} at various heating rates}
+	\caption[Table of contents Capition]{Fitted \acrfull{m} for the \MgZnCa system obtained by \acrshort{dsc} at various heating rates}
 	\label{fig:Fragility_BulkFilm_mValue}

### 2017-08-07 Paper01_EnthalpyAndCrystallization.tex
Results - Fragility - Cleaned up final paragraph of section. Other minor edits.

@@
 
-\subsubsection{\Acrlong{m}}
+\subsubsection{Fragility}
 
 Using the isochronic \acrshort{dsc} data the \gls{m} of the \MgZnCa~ system could be established for both the bulk and film.
-Numerical solutions where used to fit the \gls{vft} relationship for \gls{ht} \cite{Busch1998}.
+Numerical solutions where used to fit the \acrshort{dsc} variant of the \gls{vft} relationship for \gls{ht} \cite{Busch1998}.
 
@@
 
-For the bulk it was found $\beta^{-1} = 1.338E - 16e^{5274 (\frac{1}{T-T_{0}})}$ with Adj.
-$R^{2}=0.972$, giving a $D^{*}=20.4$, and a \acrlong{m} $m=44.9$.
-For the film $\beta^{-1} = 5.921E - 11e^{2766 (\frac{1}{T-T_{0}})}$ with Adj.
-$R^{2}=0.861$, giving a $D^{*}=10.0$, and \acrlong{m} $m=75.0$.
-See Figure \ref{fig:Fragility_BulkFilm_mValue}.
+Using these two equations for the bulk it was found $\beta^{-1} = 1.338E - 16e^{5274 (\frac{1}{T-T_{0}})}$ with an Adj.
+$R^{2}=0.972$.
+This gave a $D^{*}=20.4$, and a \gls{m}$=44.9$.
+The film was fitted to $\beta^{-1} = 5.921E - 11e^{2766 (\frac{1}{T-T_{0}})}$ with a lower confidence of Adj.
+$R^{2}=0.861$, likely owing to the reduced number of data points.
+This gave a $D^{*}=10.0$, and \gls{m}$=75.0$, see Figure \ref{fig:Fragility_BulkFilm_mValue}.
 

### 2017-08-08 Paper01_EnthalpyAndCrystallization.tex
Results - Decon - Tx Onsets - Started draft section paragraphs

@@
 
-Both the bulk and film \MgZnCa~ were examined at various \acrshort{dsc} heating rates to observe changed in the \Tg and \Tx temperatures.
-As expected higher heating rates resulted endothermic peaks shifting to higher temperatures and curve convolution.
+Numerical solutions were used to deconvolute the isochronic \acrshort{dsc} data so the various \Tx~ onsets could be accurately determined.
+This numerical fitting utilised a summation of skewed Gaussian curves to fit a target curve corresponding to the original \acrshort{dsc} \glspl{ht} for both the bulk and film, see Figures \ref{fig:DSC_Bulk_Decon} and \ref{fig:DSC_Film_Decon}.
+Similar solutions to \acrshort{dsc} deconvolution \cite{
 
-Numerical solutions were used to deconvolution the \acrshort{dsc} data so the various \Tx onsets could be determined.
-The results of the deconvolution are presented in Table \ref{tab:BulkOnsets} for the bulk and Table \ref{tab:FilmOnsets} for the film.
+The results of the deconvolution are presented in Table \ref{tab:BulkOnsets} for the bulk and Table \ref{tab:FilmOnsets} for the film. Note \Tg~ and \Tx$_{1}$ are not obtained from the deconvolution.
 

### 2017-08-08 Paper01_EnthalpyAndCrystallization.tex
Bilb - Added 5 Deconvolution sources and check their compiling
Results - XRD - moved reference notes from intro into the XRD section.

@@
 Compared with equivalent experiments on the bulk alloy, results for the thin films show distinct differences in structural enthalpy and deviations from the expected crystalline phase evolution, displaying minor peak shifts, failure of some phases to evolve, and variations in the evolution rates.
-
-Key sources \cite{Zhang2013, Zhang2012} 
-\cite{Zhang2011}
 
@@
 Numerical solutions were used to deconvolute the isochronic \acrshort{dsc} data so the various \Tx~ onsets could be accurately determined.
-This numerical fitting utilised a summation of skewed Gaussian curves to fit a target curve corresponding to the original \acrshort{dsc} \glspl{ht} for both the bulk and film, see Figures \ref{fig:DSC_Bulk_Decon} and \ref{fig:DSC_Film_Decon}.
-Similar solutions to \acrshort{dsc} deconvolution \cite{
+This numerical fitting utilised a summation of skewed Gaussian curves to fit a target curve corresponding to the original data; as is a common method \cite{Ashour2010, Yamamoto2007, Spink2008, Spink2015, Schaffer2005}.
+The details of the fits for both the bulk and film are shown in Figures \ref{fig:DSC_Bulk_Decon} and \ref{fig:DSC_Film_Decon}.
 
-The results of the deconvolution are presented in Table \ref{tab:BulkOnsets} for the bulk and Table \ref{tab:FilmOnsets} for the film. Note \Tg~ and \Tx$_{1}$ are not obtained from the deconvolution.
+The results of the deconvolution are presented in Table \ref{tab:BulkOnsets} for the bulk and Table \ref{tab:FilmOnsets} for the film.
+Note \Tg~ and \Tx$_{1}$ are not obtained from the original raw data, not the deconvolution.
 
@@
 \subsubsection{Annealing \acrshort{xrd}}
+
+Note: Key XRD sources for \MgZnCa crystallisation phase identification \cite{Zhang2013, Zhang2012, Zhang2011}
 

### 2017-08-08 Paper01_EnthalpyAndCrystallization.tex
Results - Decon Onsets - Added a place holder gaussian fit equation

@@
 This numerical fitting utilised a summation of skewed Gaussian curves to fit a target curve corresponding to the original data; as is a common method \cite{Ashour2010, Yamamoto2007, Spink2008, Spink2015, Schaffer2005}.
-The details of the fits for both the bulk and film are shown in Figures \ref{fig:DSC_Bulk_Decon} and \ref{fig:DSC_Film_Decon}.
+This fitting summation takes the form of Equation \ref{equ:GaussianSummation} \todo{this is non-skewed form.
+It is a place holder}.
+
+\begin{equation}
+	f(x) = \sum_{n=i}^{n} h_{i}~ e^-{\bigg(\frac{(x-T_{i})^2}{(2c_{j})^2}\bigg)}
+	\label{equ:GaussianSummation}
+\end{equation}
+
+Where $h$ is the enthalpy peak intensity, $T$ is the temperature at the enthalpy peak centre, and $c$ is the Gaussian RMS width.
+
+The final solutions of this fitting for both the bulk and film are shown in Figures \ref{fig:DSC_Bulk_Decon} and \ref{fig:DSC_Film_Decon}.
 
 The results of the deconvolution are presented in Table \ref{tab:BulkOnsets} for the bulk and Table \ref{tab:FilmOnsets} for the film.
-Note \Tg~ and \Tx$_{1}$ are not obtained from the original raw data, not the deconvolution.
+Note \Tg~ and \Tx$_{1}$ are obtained from the original raw data, not the deconvolution.
 

### 2017-08-08 Paper01_EnthalpyAndCrystallization.tex
Results - decon - minor edits / writting

@@
 
-The final solutions of this fitting for both the bulk and film are shown in Figures \ref{fig:DSC_Bulk_Decon} and \ref{fig:DSC_Film_Decon}.
-
-The results of the deconvolution are presented in Table \ref{tab:BulkOnsets} for the bulk and Table \ref{tab:FilmOnsets} for the film.
+The final converged solutions of this fitting for both the bulk and film are shown in Figures \ref{fig:DSC_Bulk_Decon} and \ref{fig:DSC_Film_Decon} respectively.
+These results are tabulated in Table \ref{tab:BulkOnsets} for the bulk and Table \ref{tab:FilmOnsets} for the film.
 Note \Tg~ and \Tx$_{1}$ are obtained from the original raw data, not the deconvolution.
@@
 \subsubsection{Reaction enthalpy}
+
+Target error plot?
 

### 2017-08-08 Paper01_EnthalpyAndCrystallization.tex
Results - Decon - Enthalpy - added tables of the enthalpy values at each Tx

@@
 
+\begin{table}[h]
+	\centering
+	\begin{tabular}{ c c c c c c }
+		\toprule
+		Heating Rate \acrshort{ht} & $h_{T_{x1}}$ & $h_{T_{x2}}$ & $h_{T_{x3}}$ & $h_{T_{x4}}$ & $h_{T_{x5}}$ \\ 
+		$K/min$ & $J/g$ & $J/g$ & $J/g$ & $J/g$ & $J/g$ \\
+		\midrule
+		100  & 59.59 & 6.97 & 49.16 & 22.84 & 46.08 \\
+		80   & 42.61 & 6.08 & 32.33 & 18.27 & 31.25 \\
+		60   & 30.02 & 4.05 & 25.41 & 16.76 & 19.81 \\
+		40   & 16.93 & 4.36 & 12.44 & 11.13 & 11.68 \\
+		30   & 12.03 & 3.68 & 9.32  & 9.18  & 9.02  \\
+		20   & 7.18  & 2.21 & 4.99  & 5.67  & 5.78  \\
+		15   & 5.48  & 2.01 & 3.65  & 4.69  & 4.43  \\
+		10   & 3.45  & 1.43 & 2.28  & 3.14  & 2.92  \\
+		5    & 1.65  & 0.69 & 1.09  & 1.47  & 1.42  \\
+		\bottomrule
+	\end{tabular}
+	\caption{Bulk \MgZnCa~ alloy \gls{h} of crystallisation for $Tx_{1-5}$ for the various \acrshort{dsc} \acrlongpl{ht} \acrshort{ht}; \gls{h} is in $J/g$.}
+	\label{tab:Bulk_Enthalpy}
+\end{table}
+
+\begin{table}[h]
+	\centering
+	\begin{tabular}{ c c c c c c }
+		\toprule
+		Heating Rate \acrshort{ht} & $h_{T_{x1}}$ & $h_{T_{x2}}$ & $h_{T_{x3}}$ & $h_{T_{x4}}$ & $h_{T_{x5}}$ \\ 
+		$K/min$ & $J/g$ & $J/g$ & $J/g$ & $J/g$ & $J/g$ \\
+		\midrule
+		100  & 48.24 &    & 49.85 &    & 43.38 \\
+		80   & 43.27 &    & 53.56 &    & 36.18 \\
+		60   & 15.5  &    & 8.78  &    & 22.4  \\
+		40   & 16.22 &    & 9.13  &    & 16.27 \\
+		30   & 13.72 &    & 7.16  &    & 11.81 \\
+		20   & 6.16  &    & 2.3   &    & 7.45  \\
+		15   & 6.99  &    & 3.66  &    & 6.57  \\
+		\bottomrule
+	\end{tabular}
+	\caption{Film \MgZnCa~ alloy \gls{h} of crystallisation for $Tx_{1-5}$ for the various \acrshort{dsc} \acrlongpl{ht} \acrshort{ht}; \gls{h} is in $J/g$.}
+	\label{tab:Film_Enthalpy}
+\end{table}
+
 %MultiFigure

### 2017-08-08 Paper01_EnthalpyAndCrystallization.tex
Results - Decon _ Enthaply - put in draft paragraph

@@
 
+\subsubsection{Onset determination}
+
+Numerical 
+solutions were used to deconvolute the isochronic \acrshort{dsc} data so the various \Tx~ onsets could be accurately determined.
+This numerical fitting utilised a summation of skewed Gaussian curves to fit a target curve corresponding to the original data; as is a common method \cite{Ashour2010, Yamamoto2007, Spink2008, Spink2015, Schaffer2005}.
+This fitting summation takes the form of Equation \ref{equ:GaussianSummation} \todo{this is non-skewed form.
+It is a place holder}.
+
+\begin{equation}
+	f(x) = \sum_{n=i}^{n} h_{i}~ e^-{\bigg(\frac{(x-T_{i})^2}{(2c_{j})^2}\bigg)}
+	\label{equ:GaussianSummation}
+\end{equation}
+
+Where $h$ is the enthalpy peak intensity, $T$ is the temperature at the enthalpy peak centre, and $c$ is the Gaussian RMS width.
+
+The final converged solutions of this fitting for both the bulk and film are shown in Figures \ref{fig:DSC_Bulk_Decon} and \ref{fig:DSC_Film_Decon} respectively.
+These results are tabulated in Table \ref{tab:BulkOnsets} for the bulk and Table \ref{tab:FilmOnsets} for the film.
+Note \Tg~ and \Tx$_{1}$ are obtained from the original raw data, not the deconvolution.
+
 %MultiFigure
@@
 \end{figure}
-
-\subsubsection{Onset determination}
-
-Numerical solutions were used to deconvolute the isochronic \acrshort{dsc} data so the various \Tx~ onsets could be accurately determined.
-This numerical fitting utilised a summation of skewed Gaussian curves to fit a target curve corresponding to the original data; as is a common method \cite{Ashour2010, Yamamoto2007, Spink2008, Spink2015, Schaffer2005}.
-This fitting summation takes the form of Equation \ref{equ:GaussianSummation} \todo{this is non-skewed form.
-It is a place holder}.
-
-\begin{equation}
-	f(x) = \sum_{n=i}^{n} h_{i}~ e^-{\bigg(\frac{(x-T_{i})^2}{(2c_{j})^2}\bigg)}
-	\label{equ:GaussianSummation}
-\end{equation}
-
-Where $h$ is the enthalpy peak intensity, $T$ is the temperature at the enthalpy peak centre, and $c$ is the Gaussian RMS width.
-
-The final converged solutions of this fitting for both the bulk and film are shown in Figures \ref{fig:DSC_Bulk_Decon} and \ref{fig:DSC_Film_Decon} respectively.
-These results are tabulated in Table \ref{tab:BulkOnsets} for the bulk and Table \ref{tab:FilmOnsets} for the film.
-Note \Tg~ and \Tx$_{1}$ are obtained from the original raw data, not the deconvolution.
 
@@
 
-Target error plot?
+The deconvolution fits were integrated to find the area under each curves.
+This information provides the \gls{h} of the crystallization of each phase.
+This is presented in Tables \ref{tab:Bulk_Enthalpy} and \ref{tab:Film_Enthalpy} for the bulk and film respectively.
+Figure \ref{fig:DSC_Decon} shows the \Tx~ onsets and \acrfull{h} for both the bulk and film plotted together.
 

### 2017-08-08 Paper01_EnthalpyAndCrystallization.tex
Results - Decon - draft paragraph about 5 vs 3 Tx fits in bulk and film.

@@
 
+It is worth noting the deconvolution fitted 5 crystallisation events for the bulk \MgZnCa, but only 3 events for the film.
+This occured because the bulk had 5 well defined events, where as the film was largely convoluted together.
+Thus unique solutions could not be obtained by the lesser \Tx$_{2}$ and \Tx$_{4}$ events of the film.
+
 %MultiFigure
@@
 
+For next paper on relaxation / rejuvenation.
+
 \subsection{\acrshort{xrd}}

### 2017-08-08 Paper01_EnthalpyAndCrystallization.tex
Results - annealing xrd - added draft paragraphs

@@
 
+The crystallization events of the bulk and film were confirmed with annealing \acrshort{xrd}.
+The bulk and films were subjected to no treatment, 120, 140, 145, 170, 200, 250, 290, and 320\degree C heat treatments because \acrshort{xrd}.
+This was to confirm the location of the \Tg~ and \Tx s, as well as to identify which metallic compounds these phases were.
+
+These results showed the crystallization process of the glass is;
+
+Glass $\rightarrow$ Mg$_{51}$Zn$_{20}$ $\rightarrow$ Mg $\rightarrow$ Ca$_{2}$Mg$_{5}$Zn$_{5}$ $\rightarrow$ MgZn $\rightarrow$ Ca$_{2}$Mg$_{5}$Zn$_{13}$
+
+These phase appear to metastable.
+
 %single image

### 2017-08-09 Paper01_EnthalpyAndCrystallization.tex
Results - Annealing XRD - added Xtal path table and some draft sentences

@@
 The crystallization events of the bulk and film were confirmed with annealing \acrshort{xrd}.
-The bulk and films were subjected to no treatment, 120, 140, 145, 170, 200, 250, 290, and 320\degree C heat treatments because \acrshort{xrd}.
+The bulk and films were subjected to no treatment, 120, 140, 145, 170, 200, 250, 290, and 320\degree C heat treatments before \acrshort{xrd}.
 This was to confirm the location of the \Tg~ and \Tx s, as well as to identify which metallic compounds these phases were.
 
-These results showed the crystallization process of the glass is;
+From these experiments 5 crystallisation phases were identified in both the bulk and film. These results showed the crystallization process of the glass is;
 
@@
 
-These phase appear to metastable.
+These phase appear to metastable, and grow at different rates in the bulk and film.
+
+\begin{table}[h]
+	\centering
+	\begin{tabular}{ c c c c c }
+		\toprule
+		Phase & \multicolumn{2}{c}{Bulk} & \multicolumn{2}{c}{Film}                 \\
+		& First Temp (\degree C) & Last Temp (\degree C) & First Temp (\degree C) & Last Temp (\degree C) \\
+		\midrule
+		Glass 						& 35 & 200 & 35 & 200 \\
+		Mg$_{51}$Zn$_{20}$ 			& 170 & 200 & 140 & 200 \\
+		Mg 							& 170 & 320 & 140 & 320 \\
+		Ca$_{2}$Mg$_{5}$Zn$_{5}$	& 200 & 250 & 200 & 250 \\
+		MgZn 						& 250 & 250 & 250 & 250 \\
+		Ca$_{2}$Mg$_{5}$Zn$_{13}$ 	& 290 & 320 & 290 & 320 \\
+		\bottomrule
+	\end{tabular}
+	\caption{Temperatures at which each crystallisation phase is first observed and last observed in the annealing \acrshort{xrd} for both the bulk and film.}
+	\label{tab:Crystal_Sequence}
+\end{table}
 

### 2017-08-09 Paper01_EnthalpyAndCrystallization.tex
Results - Annealing XRD - added crystallization sources to table

@@
 		Glass 						& 35 & 200 & 35 & 200 \\
-		Mg$_{51}$Zn$_{20}$ 			& 170 & 200 & 140 & 200 \\
+		Mg$_{51}$Zn$_{20}$ \cite{Zhang2013, Khan1989} & 170 & 200 & 140 & 200 \\
 		Mg 							& 170 & 320 & 140 & 320 \\
-		Ca$_{2}$Mg$_{5}$Zn$_{5}$	& 200 & 250 & 200 & 250 \\
-		MgZn 						& 250 & 250 & 250 & 250 \\
-		Ca$_{2}$Mg$_{5}$Zn$_{13}$ 	& 290 & 320 & 290 & 320 \\
+		Ca$_{2}$Mg$_{5}$Zn$_{5}$ \cite{Zhang2013, Cao2016} & 200 & 250 & 200 & 250 \\
+		MgZn \cite{Khan1989} & 250 & 250 & 250 & 250 \\
+		Ca$_{2}$Mg$_{5}$Zn$_{13}$ \cite{Zhang2013} & 290 & 320 & 290 & 320 \\
 		\bottomrule

### 2017-08-09 Paper01_EnthalpyAndCrystallization.tex
results - dynamic xrd - added draft paragraph

@@
 
+The annealing \acrshort{xrd} was useful for identifying the crystal phases present, but not many difference between the evolution rates of the bulk or films could be observed.
+Thus samples were subjected to dynamic \acrshort{xrd} over their most active rang to observe changes \textit{in-situ}.
+This allowed the crystallisation to be watched live for seeing how phase evolved over time as the temperature was raised in 5 \degree C increments.
+
 %code to put 2 images side by side in a figure

### 2017-08-09 Paper01_EnthalpyAndCrystallization.tex
results - annealing xrd - finished drafting section

@@
 
-Note: Key XRD sources for \MgZnCa crystallisation phase identification \cite{Zhang2013, Zhang2012, Zhang2011}
+The crystallisation events observed and deconvoluted from the \acrshort{dsc} were further examined with annealing \acrshort{xrd}.
+Both the bulk and films were heat treated by annealing to 120, 140, 145, 170, 200, 250, 290, and 320\degree C before \acrshort{xrd}.
+This allowed for the location of the \Tg~ and \Tx s to be confirmed as well as for the crystallisation phases to be identify.
 
-The crystallization events of the bulk and film were confirmed with annealing \acrshort{xrd}.
-The bulk and films were subjected to no treatment, 120, 140, 145, 170, 200, 250, 290, and 320\degree C heat treatments before \acrshort{xrd}.
-This was to confirm the location of the \Tg~ and \Tx s, as well as to identify which metallic compounds these phases were.
+From these experiments 5 previously observed crystallisation phases of the MgZnCa system \cite{Zhang2013, Zhang2012, Zhang2011, Khan1989, Cao2016} were characterised in the bulk and film \MgZnCa.
+This allowed the crystallization process of \MgZnCa~ from the fully amorphous glass to fully crystalline metal to be identified as;
 
-From these experiments 5 crystallisation phases were identified in both the bulk and film. These results showed the crystallization process of the glass is;
+\centerline{Glass $\rightarrow$ Mg$_{51}$Zn$_{20}$ $\rightarrow$ Mg $\rightarrow$ Ca$_{2}$Mg$_{5}$Zn$_{5}$ $\rightarrow$ MgZn $\rightarrow$ Ca$_{2}$Mg$_{5}$Zn$_{13}$}
 
-Glass $\rightarrow$ Mg$_{51}$Zn$_{20}$ $\rightarrow$ Mg $\rightarrow$ Ca$_{2}$Mg$_{5}$Zn$_{5}$ $\rightarrow$ MgZn $\rightarrow$ Ca$_{2}$Mg$_{5}$Zn$_{13}$
+The annealing \acrshort{xrd} results are shown in Figures \ref{fig:XRD_Annealing_Bulk} and \ref{fig:XRD_Annealing_Film} for the bulk and film respectively.
+In these figures each phase is identified with a tracer at the temperature it was most strongly observed.
+Note the Al substrates peaks have been faceted in Figure \ref{fig:XRD_Annealing_Film} as to not dwarf the other peaks.
 
-These phase appear to metastable, and grow at different rates in the bulk and film.
+In Figures \ref{fig:XRD_Annealing_Bulk} and \ref{fig:XRD_Annealing_Film} it can be observed that Mg$_{51}$Zn$_{20}$ comes out at lower temperature in the film compared to the bulk, while the other phase nucleate and grow at similar rates for both the bulk and film.
+The temperature each phase is first and last observed are tabulated in Table \ref{tab:Crystal_Sequence}.
 
@@
 		Phase & \multicolumn{2}{c}{Bulk} & \multicolumn{2}{c}{Film}                 \\
-		& First Temp (\degree C) & Last Temp (\degree C) & First Temp (\degree C) & Last Temp (\degree C) \\
+		& First Temp & Last Temp & First Temp & Last Temp \\
 		\midrule
@@
 	\end{tabular}
-	\caption{Temperatures at which each crystallisation phase is first observed and last observed in the annealing \acrshort{xrd} for both the bulk and film.}
+	\caption{Temperatures at which each crystallisation phase is first observed and last observed in the annealing \acrshort{xrd} for both the bulk and film. All temperatures are in \degree C.}
 	\label{tab:Crystal_Sequence}
@@
 	\centering
-	\includegraphics[width=0.9\textwidth]{XRD_Annealing_Bulk.png}
-	\caption[Table of contents Capition]{\acrshort{xrd} pattern for Bulk \MgZnCa~ heated through several crystallization peaks identified from \acrshort{dsc}}
+	\includegraphics[width=0.85\textwidth]{XRD_Annealing_Bulk.png}
+	\caption[Table of contents Capition]{\acrshort{xrd} pattern for Bulk \MgZnCa~ heated treated to several temperatures for crystallization peaks identified from \acrshort{dsc}.}
 	\label{fig:XRD_Annealing_Bulk}
@@
 	\centering
-	\includegraphics[width=0.9\textwidth]{XRD_Annealing_Film.png}
-	\caption[Table of contents Capition]{\acrshort{xrd} pattern for Film \MgZnCa~ heated through several crystallization peaks identified from \acrshort{dsc}}
+	\includegraphics[width=0.85\textwidth]{XRD_Annealing_Film.png}
+	\caption[Table of contents Capition]{\acrshort{xrd} pattern for Film \MgZnCa~ heated treated to several temperatures for crystallization peaks identified from \acrshort{dsc}.
+Note the Al substrate peaks have been faceted as to not dwarf all other peaks.}
 	\label{fig:XRD_Annealing_Film}

### 2017-08-09 Paper01_EnthalpyAndCrystallization.tex
Results - annealing xrd - added references to the table, turned off cross refecning

@@
-%\documentclass[a4paper,12pt,oneside]{article}%FinalView
-\documentclass[draft,a4paper,12pt,oneside]{article}%draftView
+\documentclass[a4paper,12pt,oneside]{article}%FinalView
+%\documentclass[draft,a4paper,12pt,oneside]{article}%draftView
 
 \input{settings/preamble.tex}%Inputs Preamble for its .tex
-\usepackage[color]{showkeys}%Shows cross ref paths
+%\usepackage[color]{showkeys}%Shows cross ref paths
 
@@
 		MgZn \cite{Khan1989} & 250 & 250 & 250 & 250 \\
-		Ca$_{2}$Mg$_{5}$Zn$_{13}$ \cite{Zhang2013} & 290 & 320 & 290 & 320 \\
+		Ca$_{2}$Mg$_{5}$Zn$_{13}$ \cite{Zhang2013, Zhang2012, Zhang2011} & 290 & 320 & 290 & 320 \\
 		\bottomrule

### 2017-08-09 Paper01_EnthalpyAndCrystallization.tex
Figures - updating capitions. got to Decon Films.

@@
 	\includegraphics[width=0.65\textwidth]{DSC_Fragility_Bulk.png}
-	\caption[Table of contents Capition]{Bulk \MgZnCa~ relaxed at 120 \degree C for 10 minutes and heated at various heating rates.
-The insert stacks the \gls{dsc} curves and labels the \Tg~ and \Tx es of the $100 K/min$ sample.}%global caption
+	\caption{Bulk \MgZnCa~ relaxed at 120 \degree C for 10 minutes and heated at various \acrfullpl{ht}.
+The insert stacks the \gls{dsc} curves and labels the \Tg~ and \Tx s of the $100 K/min$ sample.}%global caption
 	\label{fig:DSC_vHeatingRate_Bulk}
@@
 	\includegraphics[width=0.65\textwidth]{DSC_Fragility_Film.png}
-	\caption[Table of contents Capition]{Unrelaxed film \MgZnCa~ heated at various heating rates.
-The insert stacks the \gls{dsc} curves and labels the \Tg~ and \Tx es of the $100 K/min$ sample.}%global caption
+	\caption{Unrelaxed film \MgZnCa~ heated at various \acrfullpl{ht}. The insert stacks the \gls{dsc} curves and labels the \Tg~ and \Tx s of the $100 K/min$ sample.}%global caption
 	\label{fig:DSC_vHeatingRate_Film}
@@
 	\includegraphics[width=0.95\textwidth]{Bulk_Film_Fragility.png}
-	\caption[Table of contents Capition]{Fitted \acrfull{m} for the \MgZnCa system obtained by \acrshort{dsc} at various heating rates}
+	\caption{Fitted \acrfull{m} for the \MgZnCa~ system obtained from the \Tg~ of \acrshort{dsc} at various \acrfullpl{ht} for the bulk and film.}
 	\label{fig:Fragility_BulkFilm_mValue}
@@
 	\includegraphics[width=.3\textwidth]{input_Raw_Bulk_NoLeveling_100Ks_result_A5lsc.png}
-	\caption{\acrshort{dsc} deconvolution for the bulk. From left to right, top to bottom, 5, 10, 15, 20, 30, 40, 60, 80, 100 K/min.}
+	\caption{\acrshort{dsc} deconvolution for the bulk at various \glspl{ht}. From left to right, top to bottom, \gls{ht} = 5, 10, 15, 20, 30, 40, 60, 80, 100 K/min.}
 	\label{fig:DSC_Bulk_Decon}
@@
 	\includegraphics[width=.3\textwidth]{input_Raw_Film_NoLeveling_100Ks_result_A5lsc.png}
-	\caption{\acrshort{dsc} deconvolution for the film. From left to right, top to bottom, 15, 20, 30, 40, 60, 80, 100 K/min.}
+	\caption{\acrshort{dsc} deconvolution for the film at various \glspl{ht}. From left to right, top to bottom, \gls{ht} = 15, 20, 30, 40, 60, 80, 100 K/min.}
 	\label{fig:DSC_Film_Decon}

### 2017-08-10 Paper01_EnthalpyAndCrystallization.tex
Figures - finished updating figure capitions.

@@
 	\includegraphics[width=0.65\textwidth]{DSC_Fragility_Bulk.png}
-	\caption{Bulk \MgZnCa~ relaxed at 120 \degree C for 10 minutes and heated at various \acrfullpl{ht}.
-The insert stacks the \gls{dsc} curves and labels the \Tg~ and \Tx s of the $100 K/min$ sample.}%global caption
+	\caption{Bulk \MgZnCa~ relaxed at 120 \degree C for 10 minutes and heated at various \acrfullpl{ht} from $5$ to $100 K/min$.
+The insert stacks the \gls{dsc} curves and labels the \Tg~ and \Tx s of the \gls{ht} $=100 K/min$ sample.}%global caption
 	\label{fig:DSC_vHeatingRate_Bulk}
@@
 	\includegraphics[width=0.65\textwidth]{DSC_Fragility_Film.png}
-	\caption{Unrelaxed film \MgZnCa~ heated at various \acrfullpl{ht}. The insert stacks the \gls{dsc} curves and labels the \Tg~ and \Tx s of the $100 K/min$ sample.}%global caption
+	\caption{Unrelaxed film \MgZnCa~ heated at various \acrfullpl{ht}  from $15$ to $100 K/min$.
+The insert stacks the \gls{dsc} curves and labels the \Tg~ and \Tx s of the \gls{ht} $=100 K/min$ sample.}%global caption
 	\label{fig:DSC_vHeatingRate_Film}
@@
 	\includegraphics[width=.3\textwidth]{input_Raw_Bulk_NoLeveling_100Ks_result_A5lsc.png}
-	\caption{\acrshort{dsc} deconvolution for the bulk at various \glspl{ht}. From left to right, top to bottom, \gls{ht} = 5, 10, 15, 20, 30, 40, 60, 80, 100 K/min.}
+	\caption{\acrshort{dsc} deconvolution for the bulk at various \acrfullpl{ht}. From left to right, top to bottom, \gls{ht} = 5, 10, 15, 20, 30, 40, 60, 80, 100 $K/min$.}
 	\label{fig:DSC_Bulk_Decon}
@@
 	\includegraphics[width=.3\textwidth]{input_Raw_Film_NoLeveling_100Ks_result_A5lsc.png}
-	\caption{\acrshort{dsc} deconvolution for the film at various \glspl{ht}. From left to right, top to bottom, \gls{ht} = 15, 20, 30, 40, 60, 80, 100 K/min.}
+	\caption{\acrshort{dsc} deconvolution for the film at various \acrfullpl{ht}. From left to right, top to bottom, \gls{ht} = 15, 20, 30, 40, 60, 80, 100 $K/min$.}
 	\label{fig:DSC_Film_Decon}
@@
 	\includegraphics[width=0.55\textwidth]{Bulk_Onset_Peaks_Relaxed_120C.png}
-	\caption[Table of contents Capition]{The \Tg s and \Tx es of the bulk \MgZnCa~ at all heating rates. }%global caption
+	\caption{The \Tg s and \Tx s plotted at each \acrshort{dsc} \acrfull{ht} for the bulk \MgZnCa.}%global caption
 	\label{fig:DSC_Onsets_Bulk}
@@
 	\includegraphics[width=0.55\textwidth]{Onsets_BulkandFilm.png}
-	\caption[Table of contents Capition]{The \Tg s and \Tx es of the bulk and film \MgZnCa~ at all heating rates. }%global caption
+	\caption[Table of contents Capition]{The \Tg s and \Tx s plotted at each \acrshort{dsc} \acrfull{ht} for both the bulk and film \MgZnCa. Bulk is shown in black, and film in red.}%global caption
 	\label{fig:DSC_Onsets_BulkFilm}
@@
 	\includegraphics[width=.6\textwidth]{Decon_peak_area_BR.png}
-	\caption{\acrshort{dsc} onset temperatures and enthalpy of formation for the bulk and film.}
+	\caption{\acrshort{dsc} \Tx~ onset temperatures and \acrfull{h} of crystallisation formation for the bulk and film at each \acrfull{ht}. Bulk is shown in black, and film in red.}
 	\label{fig:DSC_Decon}
@@
 	\includegraphics[width=0.85\textwidth]{XRD_Annealing_Bulk.png}
-	\caption[Table of contents Capition]{\acrshort{xrd} pattern for Bulk \MgZnCa~ heated treated to several temperatures for crystallization peaks identified from \acrshort{dsc}.}
+	\caption[Table of contents Capition]{\acrshort{xrd} pattern for bulk \MgZnCa~ heated treated to several temperatures for crystallization peak identified from \acrshort{dsc}.}
 	\label{fig:XRD_Annealing_Bulk}
@@
 	\includegraphics[width=0.85\textwidth]{XRD_Annealing_Film.png}
-	\caption[Table of contents Capition]{\acrshort{xrd} pattern for Film \MgZnCa~ heated treated to several temperatures for crystallization peaks identified from \acrshort{dsc}.
+	\caption[Table of contents Capition]{\acrshort{xrd} pattern for film \MgZnCa~ heated treated to several temperatures for crystallization peak identified from \acrshort{dsc}.
 Note the Al substrate peaks have been faceted as to not dwarf all other peaks.}
@@
 	\end{subfigure}
-	\caption{(a) Stacked \gls{xrd} patterns from the incremental heating of bulk \MgZnCa. (b) Cascading \gls{xrd} patterns from the incremental heating of bulk \MgZnCa. }%global caption
+	\caption{(a) Stacked \acrshort{xrd} patterns from the incremental dynamic \textit{in-situ} heating of bulk \MgZnCa.
+Note the peak around $51$\degree~ is attributed to the AlN heating element.
+(b) The same \acrshort{xrd} patterns as (a) presented in a cascading layout.}%global caption
 	\label{fig:XRD_Dynamic_Bulk}
@@
 	\end{subfigure}
-	\caption{(a) Stacked \gls{xrd} patterns from the incremental heating of film \MgZnCa. (b) Cascading \gls{xrd} patterns from the incremental heating of film \MgZnCa. }%global caption
+	\caption{(a) Stacked \acrshort{xrd} patterns from the incremental dynamic \textit{in-situ} heating of film \MgZnCa.
+Note the peak around $51$\degree~ is attributed to the AlN heating element, and the Al substrate peaks have been faceted as to not dwarf all other peaks.
+(b) The same \acrshort{xrd} patterns as (a) presented in a cascading layout.}%global caption
 	\label{fig:XRD_Dynamic_Film}

### 2017-08-10 Paper01_EnthalpyAndCrystallization.tex
Tables - updated table capitions

@@
-\documentclass[a4paper,12pt,oneside]{article}%FinalView
-%\documentclass[draft,a4paper,12pt,oneside]{article}%draftView
+%\documentclass[a4paper,12pt,oneside]{article}%FinalView
+\documentclass[draft,a4paper,12pt,oneside]{article}%draftView
 
 \input{settings/preamble.tex}%Inputs Preamble for its .tex
-%\usepackage[color]{showkeys}%Shows cross ref paths
+\usepackage[color]{showkeys}%Shows cross ref paths
 
@@
 	\end{tabular}
-	\caption{Bulk \MgZnCa~ alloy onset temperatures for the various \acrshort{dsc} \acrlongpl{ht} \acrshort{ht}. All temperatures are in \degree C.}
+	\caption{Bulk \MgZnCa~ alloy onset temperatures for the various \acrshort{dsc} \acrfullpl{ht}. All temperatures are in \degree C.}
 	\label{tab:BulkOnsets}
@@
 	\end{tabular}
-	\caption{Film \MgZnCa~ alloy onset temperatures for the various \acrshort{dsc} \acrlongpl{ht} \acrshort{ht}. All temperatures are in \degree C.}
+	\caption{Film \MgZnCa~ alloy onset temperatures for the various \acrshort{dsc} \acrfullpl{ht}. All temperatures are in \degree C.}
 	\label{tab:FilmOnsets}
@@
 	\end{tabular}
-	\caption{Bulk \MgZnCa~ alloy \gls{h} of crystallisation for $Tx_{1-5}$ for the various \acrshort{dsc} \acrlongpl{ht} \acrshort{ht}; \gls{h} is in $J/g$.}
+	\caption{Bulk \MgZnCa~ alloy \acrfull{h} of crystallisation formation for $Tx_{1-5}$ for the various \acrshort{dsc} \acrfullpl{ht}; \gls{h} is in $J/g$.}
 	\label{tab:Bulk_Enthalpy}
@@
 	\end{tabular}
-	\caption{Film \MgZnCa~ alloy \gls{h} of crystallisation for $Tx_{1-5}$ for the various \acrshort{dsc} \acrlongpl{ht} \acrshort{ht}; \gls{h} is in $J/g$.}
+	\caption{Film \MgZnCa~ alloy \acrfull{h} of crystallisation formation for $Tx_{1-5}$ for the various \acrshort{dsc} \acrfullpl{ht}; \gls{h} is in $J/g$.}
 	\label{tab:Film_Enthalpy}

### 2017-08-10 Paper01_EnthalpyAndCrystallization.tex
Results - dynamic xrd - minor edits, change crystallisation to Aus S spelling

@@
 %Title
-\textbf{\LARGE{An assessment of structural enthalpy and crystallization pathways of \MgZnCa~ bulk metallic glass and amorphous films}}
+\textbf{\LARGE{An assessment of structural enthalpy and crystallisation pathways of \MgZnCa~ bulk metallic glass and amorphous films}}
 
@@
 Both bulk samples and metallic glass films of \MgZnCa~ were produced by copper mold casting and \gls{dc} magnetron sputtering onto aluminium substrates, respectively.
-Comparisons between structural enthalpy, crystallization pathways, relaxation and crystallization kinetics of the bulk samples and films were examined by elevated temperature \acrshort{xrd} and \acrshort{dsc}.
+Comparisons between structural enthalpy, crystallisation pathways, relaxation and crystallisation kinetics of the bulk samples and films were examined by elevated temperature \acrshort{xrd} and \acrshort{dsc}.
 Compared with equivalent experiments on the bulk alloy, results for the thin films show distinct differences in structural enthalpy and deviations from the expected crystalline phase evolution, displaying minor peak shifts, failure of some phases to evolve, and variations in the evolution rates.
@@
 The master alloy of \MgZnCa~ was produced using high-purity elements of Mg (99.85 wt\%), Zn (99.995 wt\%), and Ca (99.8 wt\%).
-The alloy was prepared by induction melting in boron nitride coated graphite crucibles, purged with Ar (99.997 vol.\% purity) five times, and protected with a circulating Ar atmosphere.
+The alloy was prepared with an in-house induction melting furnace within boron nitride coated graphite crucibles, purged with Ar (99.997 vol.\% purity) five times, and protected with a circulating Ar atmosphere.
 Alloy homogeneity was ensured by heating and cooling through a cycle of 700\degree C, 385\degree C, 650\degree C, 385\degree C, 650\degree C to a casting temperature of 500 \degree C and 450\degree C for injection and gravity casting respectively.
@@
 All samples and targets were stored under Ar when not being examined or used.
+\todo{measure injection plate thickness with micrometer}
 
@@
 The deconvolution fits were integrated to find the area under each curves.
-This information provides the \gls{h} of the crystallization of each phase.
+This information provides the \gls{h} of the crystallisation of each phase.
 This is presented in Tables \ref{tab:Bulk_Enthalpy} and \ref{tab:Film_Enthalpy} for the bulk and film respectively.
@@
 From these experiments 5 previously observed crystallisation phases of the MgZnCa system \cite{Zhang2013, Zhang2012, Zhang2011, Khan1989, Cao2016} were characterised in the bulk and film \MgZnCa.
-This allowed the crystallization process of \MgZnCa~ from the fully amorphous glass to fully crystalline metal to be identified as;
+This allowed the crystallisation process of \MgZnCa~ from the fully amorphous glass to fully crystalline metal to be identified as;
 
@@
 
-In Figures \ref{fig:XRD_Annealing_Bulk} and \ref{fig:XRD_Annealing_Film} it can be observed that Mg$_{51}$Zn$_{20}$ comes out at lower temperature in the film compared to the bulk, while the other phase nucleate and grow at similar rates for both the bulk and film.
+In Figures \ref{fig:XRD_Annealing_Bulk} and \ref{fig:XRD_Annealing_Film} it can be observed that Mg$_{51}$Zn$_{20}$ comes out at lower temperature in the film compared to the bulk, while the other phases nucleate and grow at similar rates for both the bulk and film.
 The temperature each phase is first and last observed are tabulated in Table \ref{tab:Crystal_Sequence}.
@@
 	\includegraphics[width=0.85\textwidth]{XRD_Annealing_Bulk.png}
-	\caption[Table of contents Capition]{\acrshort{xrd} pattern for bulk \MgZnCa~ heated treated to several temperatures for crystallization peak identified from \acrshort{dsc}.}
+	\caption[Table of contents Capition]{\acrshort{xrd} pattern for bulk \MgZnCa~ heated treated to several temperatures for crystallisation peak identified from \acrshort{dsc}.}
 	\label{fig:XRD_Annealing_Bulk}
@@
 	\includegraphics[width=0.85\textwidth]{XRD_Annealing_Film.png}
-	\caption[Table of contents Capition]{\acrshort{xrd} pattern for film \MgZnCa~ heated treated to several temperatures for crystallization peak identified from \acrshort{dsc}.
+	\caption[Table of contents Capition]{\acrshort{xrd} pattern for film \MgZnCa~ heated treated to several temperatures for crystallisation peak identified from \acrshort{dsc}.
 Note the Al substrate peaks have been faceted as to not dwarf all other peaks.}
@@
 The annealing \acrshort{xrd} was useful for identifying the crystal phases present, but not many difference between the evolution rates of the bulk or films could be observed.
-Thus samples were subjected to dynamic \acrshort{xrd} over their most active rang to observe changes \textit{in-situ}.
-This allowed the crystallisation to be watched live for seeing how phase evolved over time as the temperature was raised in 5 \degree C increments.
+Thus samples were subjected to dynamic \acrshort{xrd} over their most active range of $31-60$\degree~ to observe changes \textit{in-situ}.
+This allowed the crystallisation to be actively observed over the range of $35-185$ \degree C, showing how phases evolved over time as the temperature was raised in 5\degree C increments.
 
@@
 The use of a 60K \gls{dsc} heating rate compared to the more commonly used 20K rate [sources] shifts peaks for the bulk \MgZnCa~ alloy about 8 - 15 degrees higher.
-This higher heating rates were used because crystallization events for the films were difficult to differentiation at the lower heating rate.
+This higher heating rates were used because crystallisation events for the films were difficult to differentiation at the lower heating rate.
 Films show little shift to high temperature peaks with increases heating rates, but large shifts with relaxation. 

### 2017-08-11 Paper01_EnthalpyAndCrystallization.tex
Results - dsc decon - minor edits
Sputter Temp and Voltage - updated approximate values to be based on standard deviation of recorded values of all depositions

@@
 Films were produced from an in-house \acrshort{dc} magnetron sputtering facility with Ar working gas (99.997 vol.\% purity).
-The power was $15W$, typical voltage of $290-350V$, nominal chamber pressure of 1 bar, substrate temperature of $25$\degree C, and Ar flow of 3.01 \acrshort{sccm}.
+The power was $15W$, typical voltage of $285-325V$, nominal chamber pressure of 1 bar, substrate temperature of $25$\degree C, and Ar flow of 3.01 \acrshort{sccm}.
 Films were deposited directly onto to Al \acrshort{dsc} lid substrates.
@@
 From the 35 minute depositions a nominal film thickness of $2.5 \mu m$ was obtained, giving a deposition rate of approximately $1.2 nm/s$.
-The temperature within the chamber was found to rise $3 - 4$\degree C, significantly less than the expected $20K$ suggested by similar setups \cite{Wang2014}.
+The temperature within the chamber was found to rise $2.9 - 3.5$\degree C, significantly less than the expected $20K$ suggested by similar setups \cite{Wang2014}.
 
@@
 The deconvolution fits were integrated to find the area under each curves.
-This information provides the \gls{h} of the crystallisation of each phase.
+This information provides the \gls{h} of the crystallisation formation of each phase.
 This is presented in Tables \ref{tab:Bulk_Enthalpy} and \ref{tab:Film_Enthalpy} for the bulk and film respectively.

### 2017-08-11 Paper01_EnthalpyAndCrystallization.tex
Results - intro - updated film thickness and dep rate. Added figures to show new calcs.

@@
 
-From the 35 minute depositions a nominal film thickness of $2.5 \mu m$ was obtained, giving a deposition rate of approximately $1.2 nm/s$.
+From the 35 minute depositions a nominal film thickness of $1.64 \pm 0.48 \mu m$ was obtained, giving a deposition rate of approximately $0.81 \pm 0.22 nm/s$, see Figure \ref{fig:Film_Thickness_DepRate}.
 The temperature within the chamber was found to rise $2.9 - 3.5$\degree C, significantly less than the expected $20K$ suggested by similar setups \cite{Wang2014}.
+
+%code to put 2 images side by side in a figure
+\begin{figure}[h]
+	\centering
+	%Image 1
+	\begin{subfigure}[htbp]{0.4\textwidth}
+		\includegraphics[width=\textwidth]{Film_Thickness.png}
+		\caption{}
+		\label{fig:Film_Thickness}
+	\end{subfigure}
+	%Image 2
+	\begin{subfigure}[htbp]{0.4\textwidth}
+		\includegraphics[width=\textwidth]{Deposition_Rate.png}
+		\caption{}
+		\label{fig:Deposition_Rate}
+	\end{subfigure}
+	\caption{(a) Box and whisker plot of the measured film thicknesses from depositions. (b) Box and whisker plot of the calculated deposition rates achieved.}%global caption
+	\label{fig:Film_Thickness_DepRate}
+\end{figure}
 

### 2017-08-14 Paper01_EnthalpyAndCrystallization.tex
Minor edits, added sub temp box and wisker plot

--- 2017-08-11 Paper01_EnthalpyAndCrystallization.tex
@@
 Bulk amorphous \MgZnCa~ rods of $2.5 mm$ diameter and plates of thickness of $XX \mu m$ were produced by copper mold injection casting.
-The $25.4 mm$ diameter targets were prepared from a cylindrical copper mold gravity castings sectioned to thicknesses of $3.25 mm$.
+The $25.4 mm$ diameter targets were prepared from cylindrical copper mold gravity castings sectioned to thicknesses of $3.25 mm$.
 All samples and targets were stored under Ar when not being examined or used.
@@
 Depositions were for a period of 35 minutes.
-Deposition rate was estimated at $1.2 nm/s$.
+Deposition rate was estimated at $0.8 nm/s$.
 
@@
 
-From the 35 minute depositions a nominal film thickness of $2.5 \mu m$ was obtained, giving a deposition rate of approximately $1.2 nm/s$.
-The temperature within the chamber was found to rise $2.9 - 3.5$\degree C, significantly less than the expected $20K$ suggested by similar setups \cite{Wang2014}.
+From the 35 minute depositions a nominal film thickness of $1.64 \pm 0.48 \mu m$ was obtained, giving a deposition rate of approximately $0.81 \pm 0.22 nm/s$.
+The temperature within the chamber was found to rise $2.9 - 3.5$\degree C, significantly less than the expected $20K$ suggested by similar setups \cite{Wang2014}, see Figure \ref{fig:Film_Thickness_DepRate}.
+
+%code to put 3 images side by side in a figure
+\begin{figure}[h]
+	\centering
+	%Image 1
+	\begin{subfigure}[htbp]{0.32\textwidth}
+		\includegraphics[width=\textwidth]{Film_Thickness.png}
+		\caption{}
+		\label{fig:Film_Thickness}
+	\end{subfigure}
+	%Image 2
+	\begin{subfigure}[htbp]{0.32\textwidth}
+		\includegraphics[width=\textwidth]{Deposition_Rate.png}
+		\caption{}
+		\label{fig:Deposition_Rate}
+	\end{subfigure}
+	%Image 3
+\begin{subfigure}[htbp]{0.32\textwidth}
+	\includegraphics[width=\textwidth]{Settling_Voltage.png}
+	\caption{}
+	\label{fig:Settling_Voltage}
+\end{subfigure}
+	\caption{(a) Box and whisker plot of the measured film thicknesses from depositions.
+(b) Box and whisker plot of the calculated deposition rates achieved.
+(c) Box and whisker plot of substrate temperature rise.}%global caption
+	\label{fig:Film_Thickness_DepRate}
+\end{figure}
 

### 2017-08-16 Paper01_EnthalpyAndCrystallization.tex
Results - Decon - Removed bulk Tx onset figures, minor edits to decon section.

@@
 
-The final converged solutions of this fitting for both the bulk and film are shown in Figures \ref{fig:DSC_Bulk_Decon} and \ref{fig:DSC_Film_Decon} respectively.
+The final deconverged solutions of this fitting for both the bulk and film are shown in Figures \ref{fig:DSC_Bulk_Decon} and \ref{fig:DSC_Film_Decon} respectively.
 These results are tabulated in Table \ref{tab:BulkOnsets} for the bulk and Table \ref{tab:FilmOnsets} for the film.
+Tables \ref{tab:BulkOnsets} and \ref{tab:FilmOnsets} are also plotted together in Figure \ref{fig:DSC_Onsets_BulkFilm} with the bulk shown in black and the film in red.
 Note \Tg~ and \Tx$_{1}$ are obtained from the original raw data, not the deconvolution.
@@
 This occured because the bulk had 5 well defined events, where as the film was largely convoluted together.
-Thus unique solutions could not be obtained by the lesser \Tx$_{2}$ and \Tx$_{4}$ events of the film.
+Thus unique solutions could not be obtained for the lesser \Tx$_{2}$ and \Tx$_{4}$ events of the film.
 
@@
 \end{table}
-
-%single image
-\begin{figure}[b]
-	\centering
-	\includegraphics[width=0.55\textwidth]{Bulk_Onset_Peaks_Relaxed_120C.png}
-	\caption{The \Tg s and \Tx s plotted at each \acrshort{dsc} \acrfull{ht} for the bulk \MgZnCa.}%global caption
-	\label{fig:DSC_Onsets_Bulk}
-\end{figure}
 

### 2017-08-16 Paper01_EnthalpyAndCrystallization.tex
Results - Xtal Enthalpy - added new paragraph. draft done

@@
 
-The deconvolution fits were integrated to find the area under each curves.
+The deconvolution fits were integrated to find the area under each curve.
 This information provides the \gls{h} of the crystallisation formation of each phase.
-This is presented in Tables \ref{tab:Bulk_Enthalpy} and \ref{tab:Film_Enthalpy} for the bulk and film respectively.
+These energies are presented in Tables \ref{tab:Bulk_Enthalpy} and \ref{tab:Film_Enthalpy} for the bulk and film respectively.
 Figure \ref{fig:DSC_Decon} shows the \Tx~ onsets and \acrfull{h} for both the bulk and film plotted together.
+
+From Tables \ref{tab:Bulk_Enthalpy} and \ref{tab:Film_Enthalpy}, and Figure \ref{fig:DSC_Decon} it can be seen most of the crystallisation formation energy is needed to form the $1^{st}$, $3^{rd}$, and $5^{th}$ phases (i.e.
+\Tx $_{1, 3, 5}$).
+With these three phases accounting for approximately $73 \pm 7\%$ of the bulk crystallisation.
+The combined crystallisation energy of these three bulk phases is also similar to the total energy for the films.
+Demonstrating that the bulk requires more energy to crystallize than the films.
+\todo{This is what ISMANAM scientist said would be expected from a not USG glass. i.e. this is the typical expectation [sources needs].}
 

### 2017-08-17 Paper01_EnthalpyAndCrystallization.tex
Sub - added sub image of annealing xrd normalised.

@@
 
+The bulk is shown in Figure \ref{fig:XRD_Dynamic_Bulk}, and film in Figure \ref{fig:XRD_Dynamic_Film}.
+
 %code to put 2 images side by side in a figure
@@
 
+%single image
+\begin{figure}[b]
+	\centering
+	\includegraphics[width=0.85\textwidth]{XRD_Normalised_Annealing_BulkFilm_Facet.png}
+	\caption{Supplementary: Annealing \acrshort{xrd} pattern for both bulk and film \MgZnCa~ heated treated to several temperatures for crystallisation peak identified from \acrshort{dsc}.
+Note the patterned have been normalised and the Al substrate peaks have been faceted as to not dwarf all other peaks.}
+	\label{fig:XRD_Annealing_BulkandFilm}
+\end{figure}
+
 \end{document}

### 2017-08-18 Paper01_EnthalpyAndCrystallization.tex
Proof read whole paper and fixed typos.

--- 2017-08-16 Paper01_EnthalpyAndCrystallization.tex
@@
 \input{settings/preamble.tex}%Inputs Preamble for its .tex
-\usepackage[color]{showkeys}%Shows cross ref paths
+%\usepackage[color]{showkeys}%Shows cross ref paths
 
@@
 Alloy homogeneity was ensured by heating and cooling through a cycle of 700\degree C, 385\degree C, 650\degree C, 385\degree C, 650\degree C to a casting temperature of 500 \degree C and 450\degree C for injection and gravity casting respectively.
-Bulk amorphous \MgZnCa~ rods of $2.5 mm$ diameter and plates of thickness of $XX \mu m$ were produced by copper mold injection casting.
+Bulk amorphous \MgZnCa~ rods of nominal $2.5 mm$ diameter and plates of nominal $1.2 mm$ thickness were produced by copper mold injection casting.
 The $25.4 mm$ diameter targets were prepared from cylindrical copper mold gravity castings sectioned to thicknesses of $3.25 mm$.
 All samples and targets were stored under Ar when not being examined or used.
-\todo{measure injection plate thickness with micrometer}
 
 \subsection{\acrshort{dc} magnetron sputtering}
-Films were produced from an in-house \acrshort{dc} magnetron sputtering facility with Ar working gas (99.997 vol.\% purity).
+Films were produced from an in-house \gls{dc} magnetron sputtering facility with Ar working gas (99.997 vol.\% purity).
 The power was $15W$, typical voltage of $285-325V$, nominal chamber pressure of 1 bar, substrate temperature of $25$\degree C, and Ar flow of 3.01 \acrshort{sccm}.
 Films were deposited directly onto to Al \acrshort{dsc} lid substrates.
-Depositions were for a period of 35 minutes.
-Deposition rate was estimated at $0.8 nm/s$.
+Depositions were for a period of 35 minutes at an estimated rate of $0.8 nm/s$.
 
@@
 Alloy composition and homogeneity were confirmed by \acrshort{sem}-\acrshort{eds} (S3400, Hitachi, ?Japan?).
-Hyper-maps were collected with a accelerating voltage of $15-20kV$, and a probe current of $50 \mu A$.
-(Conditions; counts were 5000 kps or better, dead time was less than 20 \%, and working distance was 10mm).
+Hyper-maps were collected with an accelerating voltage of $15-20kV$, a probe current of $50 \mu A$, counts of 5000 kps or better, dead time less than 20 \%, and working distance was 10mm.
 
@@
 Annealing \acrshort{xrd} (Empyrean, PANalytical, Cu $K_{\alpha}$ X-ray source, $\lambda = 1.541 \angstrom$) was performed at room temperature. 
-(Generator Voltage 45, Tube Current 40, Scan Step Size 0.0262606, Time per Step 397.29).
+With a generator voltage $45 kV$, tube current $40 mA$, scan step size 0.0262606, and time per step of 397.29.
 
 Dynamic \acrshort{xrd} (D8, Bruker, Cu $K_{\alpha}$ X-ray source, $\lambda = 1.541 \angstrom$) was performed by raising temperature at a rate of $20 K/min$ and performing scans \textit{in situ}.
-The first scan was performed at $35$\degree C, then $75$\degree C, after which temperature was raised in $5K$ increments until reaching the peak temperature at $185$\degree C.
+The first scan was performed at $35$\degree C, then $75$\degree C, after which temperature was raised in $5$\degree C increments until reaching a final temperature at $185$\degree C.
 The $2 \theta$ scans from $31 - 60$\degree~ were completed within $1092 sec$ ($18min,~ 12sec$) to minimise the effects of recrystallisation during the experiment.
-(Generator Voltage 45, Tube Current 100, Scan Step Size 0.02, Time per Step 134.4).
+With a generator voltage $45 kV$, tube current $100 mA$, scan step size 0.02, and time per step of 134.4.
 
@@
 From the 35 minute depositions a nominal film thickness of $1.64 \pm 0.48 \mu m$ was obtained, giving a deposition rate of approximately $0.81 \pm 0.22 nm/s$.
-The temperature within the chamber was found to rise $2.9 - 3.5$\degree C, significantly less than the expected $20K$ suggested by similar setups \cite{Wang2014}, see Figure \ref{fig:Film_Thickness_DepRate}.
+The substrate temperature within the chamber was found to rise $2.9 - 3.5$\degree C, significantly less than the expected $20K$ suggested by similar setups \cite{Wang2014}, see Figure \ref{fig:Film_Thickness_DepRate}.
 
@@
 \begin{subfigure}[htbp]{0.32\textwidth}
-	\includegraphics[width=\textwidth]{Settling_Voltage.png}
+	\includegraphics[width=\textwidth]{Temperature_Rise.png}
 	\caption{}
-	\label{fig:Settling_Voltage}
+	\label{fig:Temperature_Rise}
 \end{subfigure}
@@
 These final two \glspl{ht} showed great increases in the signal intensity.
-The exothermic peaks all convoluted together making many of the thermodynamic events difficult to observer.
+The exothermic peaks all convoluted together making many of the thermodynamic events difficult to observer at all \glspl{ht}.
 It also appeared that all exothermic events shifted to lower temperatures as compared to the bulk.
-The \Tg~ and \Tx $_{1}$s were less defined than for the bulk, but could still be identified for all \glspl{ht}.
+The film \Tg~ and \Tx $_{1}$s were less defined than for the bulk, but could still be identified for all \glspl{ht}.
 For all \glspl{ht} the \Tx $_{2-5}$ onsets could not be easily identified, see Figure \ref{fig:DSC_vHeatingRate_Film}.
@@
 	\caption{Bulk \MgZnCa~ relaxed at 120 \degree C for 10 minutes and heated at various \acrfullpl{ht} from $5$ to $100 K/min$.
-The insert stacks the \gls{dsc} curves and labels the \Tg~ and \Tx s of the \gls{ht} $=100 K/min$ sample.}%global caption
+The insert stacks the \gls{dsc} curves and labels the \Tg~ and \Tx s of the \gls{ht} $=100 K/min$ curve.}%global caption
 	\label{fig:DSC_vHeatingRate_Bulk}
@@
 	\caption{Unrelaxed film \MgZnCa~ heated at various \acrfullpl{ht}  from $15$ to $100 K/min$.
-The insert stacks the \gls{dsc} curves and labels the \Tg~ and \Tx s of the \gls{ht} $=100 K/min$ sample.}%global caption
+The insert stacks the \gls{dsc} curves and labels the \Tg~ and \Tx s of the \gls{ht} $=100 K/min$ curve.}%global caption
 	\label{fig:DSC_vHeatingRate_Film}
@@
 
-Where $h$ is the enthalpy peak intensity, $T$ is the temperature at the enthalpy peak centre, and $c$ is the Gaussian RMS width.
+Where $h$ is the magnitude of the enthalpy peak, $T$ is the temperature at the enthalpy peak centre, and $c$ is the Gaussian RMS width.
 
@@
 \Tx $_{1, 3, 5}$).
-With these three phases accounting for approximately $73 \pm 7\%$ of the bulk crystallisation.
-The combined crystallisation energy of these three bulk phases is also similar to the total energy for the films.
+With these three phases accounting for approximately $73 \pm 7\%$ of the bulk crystallisation energy.
+The total crystallisation energy of these three bulk phases is also similar to the total energy for the films.
 Demonstrating that the bulk requires more energy to crystallize than the films.
@@
 The crystallisation events observed and deconvoluted from the \acrshort{dsc} were further examined with annealing \acrshort{xrd}.
-Both the bulk and films were heat treated by annealing to 120, 140, 145, 170, 200, 250, 290, and 320\degree C before \acrshort{xrd}.
+Both the bulk and film were heat treated by annealing to 120, 140, 145, 170, 200, 250, 290, and 320\degree C before \acrshort{xrd}.
 This allowed for the location of the \Tg~ and \Tx s to be confirmed as well as for the crystallisation phases to be identify.
@@
 
-The annealing \acrshort{xrd} was useful for identifying the crystal phases present, but not many difference between the evolution rates of the bulk or films could be observed.
-Thus samples were subjected to dynamic \acrshort{xrd} over their most active range of $31-60$\degree~ to observe changes \textit{in-situ}.
-This allowed the crystallisation to be actively observed over the range of $35-185$ \degree C, showing how phases evolved over time as the temperature was raised in 5\degree C increments.
+The annealing \acrshort{xrd} was useful for identifying the crystal phases present, but not many difference between the evolution rates of the bulk or film could be observed.
+Thus samples were subjected to dynamic \acrshort{xrd} over their most active $2 \theta$ range of $31-60$\degree~ to observe changes \textit{in-situ}.
+This allowed the crystallisation to be actively observed over the range of $35-185$\degree C, showing how phases evolved over time as the temperature was raised in 5\degree C increments.
+
+The bulk is shown in Figure \ref{fig:XRD_Dynamic_Bulk}, and film in Figure \ref{fig:XRD_Dynamic_Film}.
 
@@
 
-The use of a 60K \gls{dsc} heating rate compared to the more commonly used 20K rate [sources] shifts peaks for the bulk \MgZnCa~ alloy about 8 - 15 degrees higher.
-This higher heating rates were used because crystallisation events for the films were difficult to differentiation at the lower heating rate.
-Films show little shift to high temperature peaks with increases heating rates, but large shifts with relaxation. 
-Bulk show the opposite behaviour, larger peaks shifts with higher heating rates and little shift with relaxation.
+The use of a 60K \gls{dsc} \acrfull{ht} compared to the more commonly used 20K rate [sources] shifts peaks for the bulk \MgZnCa~ alloy about 8 - 15 degrees higher.
+This higher \glspl{ht} were used because crystallisation events for the films were difficult to differentiation at the lower \glspl{ht}.
+Films show little shift to high temperature peaks with increases \glspl{ht}, but large shifts with relaxation. 
+Bulk show the opposite behaviour, larger peaks shifts with higher \glspl{ht} and little shift with relaxation.
 
@@
 
+%single image
+\begin{figure}[b]
+	\centering
+	\includegraphics[width=0.85\textwidth]{XRD_Normalised_Annealing_BulkFilm_Facet.png}
+	\caption{Supplementary: Normalised annealing \acrshort{xrd} pattern for both bulk and film \MgZnCa~ heated treated to several temperatures for crystallisation peak identified from \acrshort{dsc}.
+Bulk is shown in black, and film in red.
+Note the Al substrate and other high intensity peaks have been faceted as to not dwarf all other peaks.}
+	\label{fig:XRD_Annealing_BulkandFilm}
+\end{figure}
+
 \end{document}

### 2017-08-18 Paper01_EnthalpyAndCrystallization.tex
Results - Enthalpy Tables - Added decon totals to last column, and degree C to Tx tables
Sub - Image - added Normalised dynamic xrd to the suplimentary section

@@
 		Heating Rate \acrshort{ht} & \acrshort{Tg} & $T_{x1}$ & $T_{x2}$ & $T_{x3}$ & $T_{x4}$ & $T_{x5}$ \\ 
-		$K/min$ & & & & & & \\
+		$K/min$ & \degree C & \degree C & \degree C & \degree C & \degree C & \degree C \\
 		\midrule
@@
 		Heating Rate \acrshort{ht} & \acrshort{Tg} & $T_{x1}$ & $T_{x2}$ & $T_{x3}$ & $T_{x4}$ & $T_{x5}$ \\ 
-		$K/min$ & & & & & & \\
+		$K/min$  & \degree C & \degree C & \degree C & \degree C & \degree C & \degree C \\
 		\midrule
@@
 	\centering
-	\begin{tabular}{ c c c c c c }
+	\begin{tabular}{ c c c c c c c }
 		\toprule
-		Heating Rate \acrshort{ht} & $h_{T_{x1}}$ & $h_{T_{x2}}$ & $h_{T_{x3}}$ & $h_{T_{x4}}$ & $h_{T_{x5}}$ \\ 
-		$K/min$ & $J/g$ & $J/g$ & $J/g$ & $J/g$ & $J/g$ \\
+		Heating Rate \acrshort{ht} & $h_{T_{x1}}$ & $h_{T_{x2}}$ & $h_{T_{x3}}$ & $h_{T_{x4}}$ & $h_{T_{x5}}$ & $h_{Total}$ \\ 
+		$K/min$ & $J/g$ & $J/g$ & $J/g$ & $J/g$ & $J/g$ & $J/g$ \\
 		\midrule
-		100  & 59.59 & 6.97 & 49.16 & 22.84 & 46.08 \\
-		80   & 42.61 & 6.08 & 32.33 & 18.27 & 31.25 \\
-		60   & 30.02 & 4.05 & 25.41 & 16.76 & 19.81 \\
-		40   & 16.93 & 4.36 & 12.44 & 11.13 & 11.68 \\
-		30   & 12.03 & 3.68 & 9.32  & 9.18  & 9.02  \\
-		20   & 7.18  & 2.21 & 4.99  & 5.67  & 5.78  \\
-		15   & 5.48  & 2.01 & 3.65  & 4.69  & 4.43  \\
-		10   & 3.45  & 1.43 & 2.28  & 3.14  & 2.92  \\
-		5    & 1.65  & 0.69 & 1.09  & 1.47  & 1.42  \\
+		100 & 59.59 & 6.97 & 49.16 & 22.84 & 46.08 & 184.64 \\
+		80  & 42.61 & 6.08 & 32.33 & 18.27 & 31.25 & 130.54 \\
+		60  & 30.02 & 4.05 & 25.41 & 16.76 & 19.81 & 96.05  \\
+		40  & 16.93 & 4.36 & 12.44 & 11.13 & 11.68 & 56.54  \\
+		30  & 12.03 & 3.68 & 9.32  & 9.18  & 9.02  & 43.23  \\
+		20  & 7.18  & 2.21 & 4.99  & 5.67  & 5.78  & 25.83  \\
+		15  & 5.48  & 2.01 & 3.65  & 4.69  & 4.43  & 20.26  \\
+		10  & 3.45  & 1.43 & 2.28  & 3.14  & 2.92  & 13.22  \\
+		5   & 1.65  & 0.69 & 1.09  & 1.47  & 1.42  & 6.32   \\
 		\bottomrule
@@
 	\centering
-	\begin{tabular}{ c c c c c c }
+	\begin{tabular}{ c c c c c c c }
 		\toprule
-		Heating Rate \acrshort{ht} & $h_{T_{x1}}$ & $h_{T_{x2}}$ & $h_{T_{x3}}$ & $h_{T_{x4}}$ & $h_{T_{x5}}$ \\ 
-		$K/min$ & $J/g$ & $J/g$ & $J/g$ & $J/g$ & $J/g$ \\
+		Heating Rate \acrshort{ht} & $h_{T_{x1}}$ & $h_{T_{x2}}$ & $h_{T_{x3}}$ & $h_{T_{x4}}$ & $h_{T_{x5}}$ & $h_{Total}$ \\ 
+		$K/min$ & $J/g$ & $J/g$ & $J/g$ & $J/g$ & $J/g$ & $J/g$ \\
 		\midrule
-		100  & 48.24 &    & 49.85 &    & 43.38 \\
-		80   & 43.27 &    & 53.56 &    & 36.18 \\
-		60   & 15.5  &    & 8.78  &    & 22.4  \\
-		40   & 16.22 &    & 9.13  &    & 16.27 \\
-		30   & 13.72 &    & 7.16  &    & 11.81 \\
-		20   & 6.16  &    & 2.3   &    & 7.45  \\
-		15   & 6.99  &    & 3.66  &    & 6.57  \\
+		100 & 48.24 &  & 49.85 &  & 43.38 & 141.47 \\
+		80  & 43.27 &  & 53.56 &  & 36.18 & 133.01 \\
+		60  & 15.5  &  & 8.78  &  & 22.4  & 46.68  \\
+		40  & 16.22 &  & 9.13  &  & 16.27 & 41.62  \\
+		30  & 13.72 &  & 7.16  &  & 11.81 & 32.69  \\
+		20  & 6.16  &  & 2.3   &  & 7.45  & 15.91  \\
+		15  & 6.99  &  & 3.66  &  & 6.57  & 17.22  \\
 		\bottomrule
@@
 
+%single image
+\begin{figure}[b]
+	\centering
+	\includegraphics[width=0.85\textwidth]{XRD_Normalised_Dynamic_BulkFilm_Facet.png}
+	\caption{Supplementary: Normalised dynamic \acrshort{xrd} pattern for both bulk and film \MgZnCa~ heated incrementally \textit{in-situ} from $35-185$\degree C for crystallisation peak identified from \acrshort{dsc}.
+Bulk is shown in black, and film in red.
+Note the Al substrate and other high intensity peaks have been faceted as to not dwarf all other peaks.}
+	\label{fig:XRD_Dynamic_BulkandFilm}
+\end{figure}
+
 \end{document}

### 2017-08-21 Paper01_EnthalpyAndCrystallization.tex
Method - EDS - added SEM NanoSIM 230 and 450. Made suplimentary figures larger

@@
 \subsection{\acrshort{eds} analysis}
-Alloy composition and homogeneity were confirmed by \acrshort{sem}-\acrshort{eds} (S3400, Hitachi, ?Japan?).
+Alloy composition and homogeneity were confirmed by \acrshort{sem}-\acrshort{eds} (S3400, Hitachi, Japan; NanoSEM 230, FEI Nova; NanoSEM 450, FEI Nova).
 Hyper-maps were collected with an accelerating voltage of $15-20kV$, a probe current of $50 \mu A$, counts of 5000 kps or better, dead time less than 20 \%, and working distance was 10mm.
@@
 	\centering
-	\includegraphics[width=0.85\textwidth]{XRD_Normalised_Annealing_BulkFilm_Facet.png}
+	\includegraphics[width=0.99\textwidth]{XRD_Normalised_Annealing_BulkFilm_Facet.png}
 	\caption{Supplementary: Normalised annealing \acrshort{xrd} pattern for both bulk and film \MgZnCa~ heated treated to several temperatures for crystallisation peak identified from \acrshort{dsc}.
@@
 	\centering
-	\includegraphics[width=0.85\textwidth]{XRD_Normalised_Dynamic_BulkFilm_Facet.png}
+	\includegraphics[width=0.99\textwidth]{XRD_Normalised_Dynamic_BulkFilm_Facet.png}
 	\caption{Supplementary: Normalised dynamic \acrshort{xrd} pattern for both bulk and film \MgZnCa~ heated incrementally \textit{in-situ} from $35-185$\degree C for crystallisation peak identified from \acrshort{dsc}.

### 2017-08-22 Paper01_EnthalpyAndCrystallization.tex
Method - EDS - correct errors in SEM equipment types

@@
 \subsection{\acrshort{eds} analysis}
-Alloy composition and homogeneity were confirmed by \acrshort{sem}-\acrshort{eds} (S3400, Hitachi, Japan; NanoSEM 230, FEI Nova; NanoSEM 450, FEI Nova).
+Alloy composition and homogeneity were confirmed by \acrshort{sem}-\acrshort{eds} (S3400-N, Hitachi, Japan; Nova NanoSEM 230/450, FEI, The Netherlands).
 Hyper-maps were collected with an accelerating voltage of $15-20kV$, a probe current of $50 \mu A$, counts of 5000 kps or better, dead time less than 20 \%, and working distance was 10mm.

### 2017-08-24 Paper01_EnthalpyAndCrystallization.tex
Results - Dynamic XRD - started filling draft and data table.

@@
 
+When looking at the dynamic \gls{xrd} data it can been seen that many phases seen in the bulk fail to nucleate or are not observed as strongly in the film.
+A Mg and Mg$_{51}$Zn$_{20}$ peak at 32.1\degree~ is first clearly seen in the bulk at a temperature of 170\degree C.
+In the film there is first clear evidence of this peak at 90\degree C, although its resolution is poor from 150-170\degree C.
+
+In the bulk a double peak at 38\degree~ and 39\degree~ begins emerge at 125\degree C, phases which never evolve in the film.
+The bulk peaks at 42.3\degree~ and 43.7\degree~ start to emerge at 165\degree C but are never seen in the film.
+
+\begin{table}[h]
+	\centering
+	\begin{tabular}{ c c c c c c c c }
+		\toprule
+		Peak & Bulk & Film & Change & Bulk Start & Film Start & Change & Phases \\
+		& $2\theta$ & $2\theta$ & \% & \degree C & \degree C & \% & at\% \\
+		\midrule
+		1    & 32.1 & 32.1 & 0.0\%  & 170 & 90 & -47.1\% & Mg, \MgZn \\
+		2    & 34.3 & 34.3 & 0.0\%  & 75  & 115 & 53.3\% & Mg, \MgZn, \CaMgZnFive \\
+		3    & 36.6 & 36.5 & -0.3\% & 130 & 130 & 0.0\%  & Mg, \MgZn \\
+		4    & 38.0 & N/A  & N/A    & 125 & N/A & N/A    & \MgZn, \CaMgZnFive \\
+		5    & 39.0 & N/A  & N/A    & 125 & N/A & N/A    & \MgZn \\
+		6    & 42.3 & N/A  & N/A    & 165 & N/A & N/A    & \CaMgZnFive \\
+		7    & 43.7 & N/A  & N/A    & 170 & N/A & N/A    & \CaMgZnFive \\
+		8    & 47.7 & 47.6 & -0.2\% & 170 & 170 & 0.0\%  & Mg, \MgZn \\
+		9    & 53.3 & N/A  & N/A    & 175 & N/A & N/A    & \MgZn, \CaMgZnFive \\
+		10   & 57.2 & N/A  & N/A    & 170 & N/A  & N/A   & Mg, \MgZn \\
+		\bottomrule
+	\end{tabular}
+	\caption{Main dynamic \gls{xrd} peaks for both the bulk and the film.
+Data shows minor shifting for peaks 3 and 8, large state temperature differences for peaks 1 and 2, failure of peaks $4-7$, 9, and 10 to nucleation in the film.}
+	\label{tab:Dynamic_XRD}
+\end{table}
+
 %code to put 2 images side by side in a figure

### 2017-08-25 Paper01_EnthalpyAndCrystallization.tex
Tables - moved table captions to be above tables.
Results - Dynamic XRD - added to the draft section

@@
 	\centering
+	\caption{\acrshort{eds} composition of bulk and film \MgZnCa~ in atomic weight percent.}
 	\begin{tabular}{ c c c }
@@
 	\end{tabular}
-	\caption{\acrshort{eds} composition of bulk and film \MgZnCa~ in atomic weight percent.}
 	\label{tab:EDS_Composition}
@@
 	\centering
+	\caption{Bulk \MgZnCa~ alloy onset temperatures for the various \acrshort{dsc} \acrfullpl{ht}. All temperatures are in \degree C.}
 	\begin{tabular}{ c c c c c c c }
@@
 	\end{tabular}
-	\caption{Bulk \MgZnCa~ alloy onset temperatures for the various \acrshort{dsc} \acrfullpl{ht}. All temperatures are in \degree C.}
 	\label{tab:BulkOnsets}
@@
 	\centering
+	\caption{Film \MgZnCa~ alloy onset temperatures for the various \acrshort{dsc} \acrfullpl{ht}. All temperatures are in \degree C.}
 	\begin{tabular}{ c c c c c c c }
@@
 	\end{tabular}
-	\caption{Film \MgZnCa~ alloy onset temperatures for the various \acrshort{dsc} \acrfullpl{ht}. All temperatures are in \degree C.}
 	\label{tab:FilmOnsets}
@@
 	\centering
+	\caption{Bulk \MgZnCa~ alloy \acrfull{h} of crystallisation formation for $Tx_{1-5}$ for the various \acrshort{dsc} \acrfullpl{ht}; \gls{h} is in $J/g$.}
 	\begin{tabular}{ c c c c c c c }
@@
 	\end{tabular}
-	\caption{Bulk \MgZnCa~ alloy \acrfull{h} of crystallisation formation for $Tx_{1-5}$ for the various \acrshort{dsc} \acrfullpl{ht}; \gls{h} is in $J/g$.}
 	\label{tab:Bulk_Enthalpy}
@@
 	\centering
+	\caption{Film \MgZnCa~ alloy \acrfull{h} of crystallisation formation for $Tx_{1-5}$ for the various \acrshort{dsc} \acrfullpl{ht}; \gls{h} is in $J/g$.}
 	\begin{tabular}{ c c c c c c c }
@@
 	\end{tabular}
-	\caption{Film \MgZnCa~ alloy \acrfull{h} of crystallisation formation for $Tx_{1-5}$ for the various \acrshort{dsc} \acrfullpl{ht}; \gls{h} is in $J/g$.}
 	\label{tab:Film_Enthalpy}
@@
 	\centering
+	\caption{Temperatures at which each crystallisation phase is first observed and last observed in the annealing \acrshort{xrd} for both the bulk and film. All temperatures are in \degree C.}
 	\begin{tabular}{ c c c c c }
@@
 	\end{tabular}
-	\caption{Temperatures at which each crystallisation phase is first observed and last observed in the annealing \acrshort{xrd} for both the bulk and film. All temperatures are in \degree C.}
 	\label{tab:Crystal_Sequence}
@@
 
+\todo{peak shift can be seen in the annealing xrd. can make a table of that, but rates of nucleation is only seen in the dynamic.}
+
 \subsubsection{Dynamic \acrshort{xrd}}
@@
 
-When looking at the dynamic \gls{xrd} data it can been seen that many phases seen in the bulk fail to nucleate or are not observed as strongly in the film.
-A Mg and Mg$_{51}$Zn$_{20}$ peak at 32.1\degree~ is first clearly seen in the bulk at a temperature of 170\degree C.
-In the film there is first clear evidence of this peak at 90\degree C, although its resolution is poor from 150-170\degree C.
+The dynamic \acrshort{xrd} data shows that many phases seen in the bulk nucleate at different temperatures, are not observed as strongly, or fail to nucleate in the film.
+The first Mg and \MgZn~ peak at 32.1\degree~ is first clearly seen in the bulk at a temperature of 170\degree C.
+In the film the first clear evidence of this peak is at 90\degree C, although its resolution is poor from 150-170\degree C.
+The Mg, \MgZn, and \CaMgZnFive~ peak at 34.3\degree~ is seen at 75\degree C in the bulk, but not till 115\degree C in the film.
+The Mg and \MgZn~ peak at 47.7\degree~ is seen in both the bulk and film at 170\degree C.
 
-In the bulk a double peak at 38\degree~ and 39\degree~ begins emerge at 125\degree C, phases which never evolve in the film.
-The bulk peaks at 42.3\degree~ and 43.7\degree~ start to emerge at 165\degree C but are never seen in the film.
+In the bulk a double peak at 38\degree~ and 39\degree~ begins to emerge at 125\degree C, phases which never evolve in the film.
+The bulk \CaMgZnFive~ peaks at 42.3\degree~ and 43.7\degree~ start to emerge at 165\degree C and 170\degree C respectively, but are never seen in the film.
+The small 57.2\degree~ peak at 170\degree C is also never seen in the film.
+A final faint peak at 53.3\degree is seen in the bulk at 175\degree C but never in the film.
+These observations are tabulated in Table \ref{tab:Dynamic_XRD}.
 
@@
 	\centering
+	\caption{Main dynamic \gls{xrd} peaks for both the bulk and the film.
+Data shows minor shifting for peaks 3 and 8, large start temperature differences for peaks 1 and 2, and failure of peaks $4-7$, 9, and 10 to nucleation in the film.}
 	\begin{tabular}{ c c c c c c c c }
@@
 	\end{tabular}
-	\caption{Main dynamic \gls{xrd} peaks for both the bulk and the film.
-Data shows minor shifting for peaks 3 and 8, large state temperature differences for peaks 1 and 2, failure of peaks $4-7$, 9, and 10 to nucleation in the film.}
 	\label{tab:Dynamic_XRD}

### 2017-08-25 Paper01_EnthalpyAndCrystallization.tex
Results - Dynamic XRD - added normalised figures

@@
 
+%single image
+\begin{figure}[b]
+	\centering
+	\includegraphics[width=0.85\textwidth]{XRD_Normalised_Dynamic_185.png}
+	\caption[Table of contents Capition]{Normalised dynamic \acrshort{xrd} from $150-185$\degree C. Large bulk peaks have been faceted as to not dwarf smaller peaks and details.}%global caption
+	\label{fig:XRD_Dynamic_185}
+\end{figure}
+
+%single image
+\begin{figure}[b]
+	\centering
+	\includegraphics[width=0.85\textwidth]{XRD_Normalised_Dynamic_145.png}
+	\caption[Table of contents Capition]{Normalised dynamic \acrshort{xrd} from $110-145$\degree C.}%global caption
+	\label{fig:XRD_Dynamic_145}
+\end{figure}
+
+%single image
+\begin{figure}[b]
+	\centering
+	\includegraphics[width=0.85\textwidth]{XRD_Normalised_Dynamic_105.png}
+	\caption[Table of contents Capition]{Normalised dynamic \acrshort{xrd} from $35-105$\degree C.}%global caption
+	\label{fig:XRD_Dynamic_105}
+\end{figure}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2017-08-25 Paper01_EnthalpyAndCrystallization.tex
Results - Dynamic XRD - Added to the draft

@@
 
-The bulk is shown in Figure \ref{fig:XRD_Dynamic_Bulk}, and film in Figure \ref{fig:XRD_Dynamic_Film}.
-
 The dynamic \acrshort{xrd} data shows that many phases seen in the bulk nucleate at different temperatures, are not observed as strongly, or fail to nucleate in the film.
@@
 The small 57.2\degree~ peak at 170\degree C is also never seen in the film.
-A final faint peak at 53.3\degree is seen in the bulk at 175\degree C but never in the film.
+A final faint peak at 53.3\degree is seen in the bulk at 175\degree C, but never in the film.
 These observations are tabulated in Table \ref{tab:Dynamic_XRD}.
+The bulk \acrshort{xrd} is shown in Figure \ref{fig:XRD_Dynamic_Bulk}, and the film in Figure \ref{fig:XRD_Dynamic_Film}.
+Normalised plots allowing for easy identification of differences between the bulk and film are shown in Figures \ref{fig:XRD_Dynamic_185}, \ref{fig:XRD_Dynamic_145}, and \ref{fig:XRD_Dynamic_105}.
 

### 2017-08-25 Paper01_EnthalpyAndCrystallization.tex
Results - Dynamic XRD - Added peak shift table for dynamic XRD. Meant to make one for annealing XRD...
Suplimentary - Added annealing XRD peak list table. Cannot go in main body like I though.

@@
 
+\begin{table}[h]
+	\centering
+	\caption{Location of the bulk and film peaks for the dynamic \acrshort{xrd} Mg, \MgZn, and \CaMgZnFive~ compounds.}
+	\begin{tabular}{ c c c c c c c c c }
+		\toprule
+		\multicolumn{3}{c}{Mg} & \multicolumn{3}{c}{\MgZn} & \multicolumn{3}{c}{\CaMgZnFive} \\
+		Bulk & Film & Change \% & Bulk & Film & Change \% & Bulk & Film & Change \% \\
+		\midrule
+		32.1 & 32.1 & 0.0\%  & 32.1 & 32.1   & 0.0\%  & 34.1 & 34.1 & 0.0\% \\
+		34.3 & 34.3 & 0.0\%  & 34.3 & 34.3   & 0.0\%  & 34.6 & 35.1 & 1.4\% \\
+		36.6 & 36.5 & -0.3\% & 36.6 & 36.5   & -0.3\% & 36.0 & 35.7 & -0.8\% \\
+		47.7 & 47.6 & -0.2\% & 38.0 & 38.2   & 0.5\%  & 38.0 & 38.2 & 0.5\% \\
+		57.2 & 57.1 & -0.2\% & 39.1 & 39.5   & 1.0\%  & 42.3 & 42.2 & -0.2\% \\
+		&    &      & 45.1   & 45.2 & 0.2\%  & 43.7   & 43.3 & -0.9\% \\
+		&    &      & 47.7   & 47.6 & -0.2\% & 53.3   & 53.0 & -0.6\% \\
+		&    &      & 53.3   & 53.0 & -0.6\% &        &      &        \\
+		&    &      & 57.2   & 57.1 & -0.2\% &        &      &        \\
+		\bottomrule
+	\end{tabular}
+	\label{tab:Annealing_XRD_PeakShift}
+\end{table}
+
 %code to put 2 images side by side in a figure
@@
 
+%Supplementary
+
 %single image
@@
 \end{figure}
+
+\begin{table}[b]
+	\centering
+	\caption{Supplementary: Annealing \acrshort{xrd} peak pattern list.
+Peaks which appear in both the bulk and film are marked "Both," peaks only appearing on the bulk are marked "Bulk Only," and peaks only appearing on the film are marked "Film Only."}
+	\begin{tabular}{cccccccccc}
+		\toprule
+		\multicolumn{2}{c}{Mg} & \multicolumn{2}{c}{\MgZn} & \multicolumn{2}{c}{\CaMgZnFive} & \multicolumn{2}{c}{\CaMgZnThirteen} & \multicolumn{2}{c}{MgZn} \\
+		\midrule
+		32.264 & Both & 15.1461 & Bulk Only & 10.8738 & Both & 12.114 & Both & 12.636 & Both \\
+		34.5053 & Both & 17.5798 & Bulk Only & 14.0992 & Both & 13.935 & Both & 14.752 & Both \\
+		36.7065 & Both & 19.429 & Both & 17.9698 & Both & 20.165 & Both & 20.639 & Both \\
+		47.925 & Both & 21.6753 & Bulk Only & 21.7787 & Both & 21.035 & Both & 22.263 & Both \\
+		57.4721 & Both & 23.2049 & Bulk Only & 23.5826 & Both & 23.329 & Both & 23.58 & Both \\
+		63.2 & Both & 24.5533 & Film Only & 26.1221 & Both & 24.641 & Both & 28.871 & Both \\
+		67.4268 & Both & 27.668 & Bulk Only & 28.3477 & Both & 25.281 & Both & 32.054 & Both \\
+		68.7541 & Both & 30.4946 & Bulk Only & 30.3272 & Both & 27.947 & Both & 33.797 & Both \\
+		70.121 & Both & 32.0757 & Bulk Only & 32.8866 & Both & 29.258 & Both & 34.743 & Both \\
+		72.6686 & Both & 34.0114 & Both & 34.2311 & Both & 30.699 & Both & 35.892 & Both \\
+		77.9616 & Both & 36.3948 & Both & 34.9708 & Bulk Only & 31.589 & Both & 37.121 & Both \\
+		81.7143 & Both & 36.9487 & Bulk Only & 36.3289 & Both & 33.929 & Both & 38.101 & Both \\
+		&  & 37.8181 & Both & 37.6976 & Both & 35.308 & Both & 39.312 & Both \\
+		&  & 39.1701 & Both & 38.1445 & Both & 35.892 & Bulk Only & 40.416 & Both \\
+		&  & 42.4369 & Both & 39.7631 & Both & 36.806 & Both & 41.989 & Both \\
+		&  & 43.2937 & Both & 41.2057 & Both & 37.281 & Both & 42.824 & Both \\
+		&  & 44.8168 & Both & 42.441 & Both & 38.269 & Both & 43.917 & Both \\
+		&  & 47.9318 & Both & 43.9276 & Both & 40.041 & Both & 47.046 & Both \\
+		&  & 57.4692 & Both & 45.3071 & Both & 40.991 & Both & 48.376 & Both \\
+		&  & 63.2267 & Both & 48.1674 & Both & 42.195 & Both & 49.498 & Both \\
+		&  & 64.1349 & Film Only & 52.0808 & Both & 43.038 & Both & 51.285 & Both \\
+		&  & 65.0419 & Bulk Only & 53.6599 & Both & 43.917 & Both & 53.211 & Both \\
+		&  & 65.3533 & Film Only & 56.9387 & Both & 44.6 & Both & 55.66 & Both \\
+		&  & 68.5726 & Bulk Only & 58.561 & Both & 45.306 & Both & 57.955 & Both \\
+		&  & 70.0382 & Both & 60.5081 & Both & 46.535 & Both & 60.026 & Both \\
+		&  & 72.6234 & Both & 61.853 & Both & 47.306 & Film Only & 62.26 & Both \\
+		&  & 76.4763 & Bulk Only & 62.9999 & Both & 48.104 & Bulk Only & 63.687 & Both \\
+		&  & 77.2025 & Bulk Only & 64.3501 & Both & 50.079 & Both & 65.186 & Both \\
+		&  & 78.3347 & Both & 65.632 & Both & 51.285 & Both &  &  \\
+		&  & 82.0596 & Both & 66.831 & Both & 56.178 & Bulk Only &  &  \\
+		&  &  &  & 68.7827 & Both & 58.601 & Both &  &  \\
+		&  &  &  & 70.1095 & Both & 59.94 & Both &  &  \\
+		&  &  &  & 71.8163 & Both & 62.028 & Both &  &  \\
+		&  &  &  & 72.8322 & Bulk Only & 63.59 & Both &  &  \\
+		&  &  &  & 74.9981 & Both & 64.427 & Both &  &  \\
+		&  &  &  & 78.083 & Both & 66.229 & Both &  &  \\
+		&  &  &  & 81.5094 & Bulk Only & 67.362 & Both &  &  \\
+		&  &  &  & 82.6818 & Film Only & 68.198 & Both &  &  \\
+		&  &  &  & 83.1204 & Both & 69.524 & Both &  &  \\
+		&  &  &  &  &  & 70.48 & Both &  &  \\
+		&  &  &  &  &  & 72.032 & Bulk Only &  &  \\
+		&  &  &  &  &  & 73.329 & Both &  &  \\
+		&  &  &  &  &  & 73.997 & Bulk Only &  &  \\
+		&  &  &  &  &  & 76.736 & Both &  &  \\
+		&  &  &  &  &  & 78.69 & Both &  &  \\
+		&  &  &  &  &  & 79.631 & Both &  & \\
+		%\bottomrule
+	\end{tabular}
+	\label{tab:Sub_Annealing_XRD_Peaks}
+\end{table}
 

### 2017-08-28 Paper01_EnthalpyAndCrystallization.tex
Results - Annealing XRD - noted which phases match which Tx1-5, other minor edits throughout

@@
 		\midrule
-		Mg & $64.85 \pm 3.18$ & $62.92 \pm 3.24$ \\
-		Zn & $29.55 \pm 0.82$ & $31.17 \pm 0.95$ \\
-		Ca & $~~ 5.60 \pm 0.17$ & $~~ 5.91 \pm 0.19$ \\ 
+		Mg & $64.85 \pm 3.18$ & $63.20 \pm 3.28$ \\
+		Zn & $29.55 \pm 0.82$ & $30.95 \pm 0.96$ \\
+		Ca & $~~ 5.60 \pm 0.17$ & $~~ 5.85 \pm 0.19$ \\ 
 		\bottomrule
@@
 
+Note the phases identified in Table \ref{tab:Crystal_Sequence} have reasonable agreement with the onset temperatures presented in Tables \ref{tab:BulkOnsets} and \ref{tab:FilmOnsets}.
+With \MgZn~ and Mg corresponding to either \Tx $_{1}$ or \Tx $_{2}$, \CaMgZnFive~ to \Tx$_{3}$, MgZn to \Tx$_{4}$, and \CaMgZnThirteen~ to \Tx$_{5}$.
+
 \begin{table}[h]
@@
 \end{figure}
-
-\todo{peak shift can be seen in the annealing xrd. can make a table of that, but rates of nucleation is only seen in the dynamic.}
 
@@
 	\centering
-	\caption{Supplementary: Annealing \acrshort{xrd} peak pattern list.
+	\caption{Supplementary: Annealing \acrshort{xrd} $2 \theta$ peak pattern list.
 Peaks which appear in both the bulk and film are marked "Both," peaks only appearing on the bulk are marked "Bulk Only," and peaks only appearing on the film are marked "Film Only."}

### 2017-08-28 Paper01_EnthalpyAndCrystallization.tex
Results - Dyanmic XRD - worked on draft section

@@
 The bulk \CaMgZnFive~ peaks at 42.3\degree~ and 43.7\degree~ start to emerge at 165\degree C and 170\degree C respectively, but are never seen in the film.
-The small 57.2\degree~ peak at 170\degree C is also never seen in the film.
-A final faint peak at 53.3\degree is seen in the bulk at 175\degree C, but never in the film.
+A faint \MgZn~ and \CaMgZnFive~ peak at 53.3\degree is seen in the bulk at 175\degree C, but never in the film.
+The final small Mg and \MgZn~ 57.2\degree~ peak at 170\degree C is also never seen in the film.
 These observations are tabulated in Table \ref{tab:Dynamic_XRD}.
@@
 
+It was also observed that there was a some minor peak shifting between the Mg, \MgZn, and \CaMgZnFive~ phases in the dynamic bulk and film \acrshort{xrd}.
+The largest shifts were seen in the \CaMgZnFive~ 34.6\degree~ peak and \MgZn~ 39.1\degree~ peak of 1.4\% and 1.0\% respectively.
+These shifts are tabulated in Table \ref{tab:Dynamic_XRD_PeakShift}.
+
 \begin{table}[h]
@@
 	\end{tabular}
-	\label{tab:Annealing_XRD_PeakShift}
+	\label{tab:Dynamic_XRD_PeakShift}
 \end{table}

### 2017-08-28 Paper01_EnthalpyAndCrystallization.tex
Results - Dynamic XRD - Proof read and made minor edits

@@
 \newpage
+\addcontentsline{toc}{section}{TABLE OF CONTENTS}
 \tableofcontents\newpage
-\addcontentsline{toc}{section}{TABLE OF CONTENTS}
 \clearpage %% start of main matter
@@
 These observations are tabulated in Table \ref{tab:Dynamic_XRD}.
-The bulk \acrshort{xrd} is shown in Figure \ref{fig:XRD_Dynamic_Bulk}, and the film in Figure \ref{fig:XRD_Dynamic_Film}.
+The bulk dynamic \acrshort{xrd} is shown in Figure \ref{fig:XRD_Dynamic_Bulk}, and the film in Figure \ref{fig:XRD_Dynamic_Film}.
 Normalised plots allowing for easy identification of differences between the bulk and film are shown in Figures \ref{fig:XRD_Dynamic_185}, \ref{fig:XRD_Dynamic_145}, and \ref{fig:XRD_Dynamic_105}.
@@
 	\centering
-	\caption{Main dynamic \gls{xrd} peaks for both the bulk and the film.
+	\caption{Main dynamic \acrshort{xrd} peaks for both the bulk and the film.
 Data shows minor shifting for peaks 3 and 8, large start temperature differences for peaks 1 and 2, and failure of peaks $4-7$, 9, and 10 to nucleation in the film.}
@@
 It was also observed that there was a some minor peak shifting between the Mg, \MgZn, and \CaMgZnFive~ phases in the dynamic bulk and film \acrshort{xrd}.
-The largest shifts were seen in the \CaMgZnFive~ 34.6\degree~ peak and \MgZn~ 39.1\degree~ peak of 1.4\% and 1.0\% respectively.
+The largest shifts were seen in the \CaMgZnFive~ 34.6\degree~ peak and \MgZn~ 39.1\degree~ peak, with shifts of 1.4\% and 1.0\% respectively.
 These shifts are tabulated in Table \ref{tab:Dynamic_XRD_PeakShift}.
@@
 	\centering
-	\caption{Location of the bulk and film peaks for the dynamic \acrshort{xrd} Mg, \MgZn, and \CaMgZnFive~ compounds.}
+	\caption{Location of the dynamic bulk and film \acrshort{xrd} peaks for the Mg, \MgZn, and \CaMgZnFive~ compounds.}
 	\begin{tabular}{ c c c c c c c c c }

### 2017-08-29 Paper01_EnthalpyAndCrystallization.tex
Results - alloy comp - updated bulk alloy comp with new SEM results
Method - proof read method with minor edits

@@
 Bulk amorphous \MgZnCa~ rods of nominal $2.5 mm$ diameter and plates of nominal $1.2 mm$ thickness were produced by copper mold injection casting.
-The $25.4 mm$ diameter targets were prepared from cylindrical copper mold gravity castings sectioned to thicknesses of $3.25 mm$.
+The $25.4 mm$ diameter targets were prepared from cylindrical copper mold gravity castings sectioned to nominal thicknesses of $3.25 mm$, and polished.
 All samples and targets were stored under Ar when not being examined or used.
@@
 Films were deposited directly onto to Al \acrshort{dsc} lid substrates.
-Depositions were for a period of 35 minutes at an estimated rate of $0.8 nm/s$.
+Depositions were for a period of 35 minutes at an estimated deposition rate of $0.8 nm/s$.
 
@@
 Alloy composition and homogeneity were confirmed by \acrshort{sem}-\acrshort{eds} (S3400-N, Hitachi, Japan; Nova NanoSEM 230/450, FEI, The Netherlands).
-Hyper-maps were collected with an accelerating voltage of $15-20kV$, a probe current of $50 \mu A$, counts of 5000 kps or better, dead time less than 20 \%, and working distance was 10mm.
+Hyper-maps were collected with an accelerating voltage of $15-20keV$, a probe current of $50 \mu A$, spot size 4.2, counts of 5000 kps or better, dead time less than 20\%, and working distance was $5mm$.
 
@@
 
-Isothermal relaxation \acrshort{dsc} was preformed by heating samples at $20 K/min$ to the desired annealing temperature, holding for desired time, and Ar quenching to room temperature.
+\hl{Isothermal relaxation acrshort{dsc} was preformed by heating samples at $20 K/min$ to the desired annealing temperature, holding for desired time, and Ar quenching to room temperature.}
 
@@
 \subsection{\acrshort{xrd} characterization}
-Annealing \acrshort{xrd} (Empyrean, PANalytical, Cu $K_{\alpha}$ X-ray source, $\lambda = 1.541 \angstrom$) was performed at room temperature. 
+Annealing \acrshort{xrd} (Empyrean, PANalytical, Cu $K_{\alpha}$ X-ray source, $\lambda = 1.541 \angstrom$) was performed on heat treated bulk rods and films at room temperature. 
 With a generator voltage $45 kV$, tube current $40 mA$, scan step size 0.0262606, and time per step of 397.29.
 
-Dynamic \acrshort{xrd} (D8, Bruker, Cu $K_{\alpha}$ X-ray source, $\lambda = 1.541 \angstrom$) was performed by raising temperature at a rate of $20 K/min$ and performing scans \textit{in situ}.
+Dynamic \acrshort{xrd} (D8, Bruker, Cu $K_{\alpha}$ X-ray source, $\lambda = 1.541 \angstrom$) was performed on as manufactured bulk plates and films by raising temperature at a rate of $20 K/min$ and performing scans \textit{in situ}.
 The first scan was performed at $35$\degree C, then $75$\degree C, after which temperature was raised in $5$\degree C increments until reaching a final temperature at $185$\degree C.
@@
 		\midrule
-		Mg & $64.85 \pm 3.18$ & $63.20 \pm 3.28$ \\
-		Zn & $29.55 \pm 0.82$ & $30.95 \pm 0.96$ \\
-		Ca & $~~ 5.60 \pm 0.17$ & $~~ 5.85 \pm 0.19$ \\ 
+		Mg & $64.92 \pm 3.22$ & $63.20 \pm 3.28$ \\
+		Zn & $29.55 \pm 0.84$ & $30.95 \pm 0.96$ \\
+		Ca & $~~ 5.53 \pm 0.17$ & $~~ 5.85 \pm 0.19$ \\ 
 		\bottomrule
@@
 
-For next paper on relaxation / rejuvenation.
+\hl{For next paper on relaxation / rejuvenation.}
 

### 2017-08-30 Paper01_EnthalpyAndCrystallization.tex
Corrections - made proof reading corrections throughout

@@
 Alloy homogeneity was ensured by heating and cooling through a cycle of 700\degree C, 385\degree C, 650\degree C, 385\degree C, 650\degree C to a casting temperature of 500 \degree C and 450\degree C for injection and gravity casting respectively.
-Bulk amorphous \MgZnCa~ rods of nominal $2.5 mm$ diameter and plates of nominal $1.2 mm$ thickness were produced by copper mold injection casting.
-The $25.4 mm$ diameter targets were prepared from cylindrical copper mold gravity castings sectioned to nominal thicknesses of $3.25 mm$, and polished.
+Bulk amorphous \MgZnCa~ rods of nominal $2.5 mm$ diameter sectioned to \hl{2mm} thickness, and plates of nominal $1.2 mm$ thickness were produced by copper mold injection casting.
+The $25.4 mm$ diameter targets were prepared from cylindrical copper mold gravity castings sectioned to nominal thicknesses of \hl{3.25} $mm$, and polished.
 All samples and targets were stored under Ar when not being examined or used.
@@
 Alloy composition and homogeneity were confirmed by \acrshort{sem}-\acrshort{eds} (S3400-N, Hitachi, Japan; Nova NanoSEM 230/450, FEI, The Netherlands).
-Hyper-maps were collected with an accelerating voltage of $15-20keV$, a probe current of $50 \mu A$, spot size 4.2, counts of 5000 kps or better, dead time less than 20\%, and working distance was $5mm$.
+Hyper-maps were collected with an accelerating voltage of $15-20keV$, a probe current of $50 \mu A$, spot size 4.2, counts of $5000cps$ or better, dead time less than 20\%, and working distance was $5mm$.
 
@@
 
-\hl{Isothermal relaxation acrshort{dsc} was preformed by heating samples at $20 K/min$ to the desired annealing temperature, holding for desired time, and Ar quenching to room temperature.}
+\hl{Isothermal relaxation acrshort{dsc} was preformed by heating samples at $20 K/min$ to the desired annealing temperature, holding for the desired time, and Ar quenching to room temperature.}
 
@@
 
-The bulk \MgZnCa~ was examined at \acrfullpl{ht} of 5, 10, 15, 20, 30, 40, 60, 80, and 100 $K/min$ to observe changes in the \Tg~ and the \Tx s with \gls{ht}.
+The bulk \MgZnCa~ was examined at \acrfullpl{ht} of 5, 10, 15, 20, 30, 40, 60, 80, and 100 $K/min$ to observe changes in the \Tg~ and \Tx s with \gls{ht}.
 As expected greater \gls{ht} resulted in greater signal strength, exothermic peaks shifting to higher start temperatures, and an increase in thermal lag resulting in later exothermic finish temperatures and curve convolution.
@@
 
-Using the isochronic \acrshort{dsc} data the \gls{m} of the \MgZnCa~ system could be established for both the bulk and film.
+Using the isochronic \acrshort{dsc} \Tg s the \gls{m} of the \MgZnCa~ system could be established for both the bulk and film.
 Numerical solutions where used to fit the \acrshort{dsc} variant of the \gls{vft} relationship for \gls{ht} \cite{Busch1998}.
@@
 Numerical 
-solutions were used to deconvolute the isochronic \acrshort{dsc} data so the various \Tx~ onsets could be accurately determined.
+solutions were used to deconvolute the isochronic \acrshort{dsc} curves so the various \Tx~ onsets could be accurately determined.
 This numerical fitting utilised a summation of skewed Gaussian curves to fit a target curve corresponding to the original data; as is a common method \cite{Ashour2010, Yamamoto2007, Spink2008, Spink2015, Schaffer2005}.
-This fitting summation takes the form of Equation \ref{equ:GaussianSummation} \todo{this is non-skewed form.
-It is a place holder}.
+For simplified, un-skewed peaks this fitting summation takes the form of Equation \ref{equ:GaussianSummation}.
 
@@
 Tables \ref{tab:BulkOnsets} and \ref{tab:FilmOnsets} are also plotted together in Figure \ref{fig:DSC_Onsets_BulkFilm} with the bulk shown in black and the film in red.
-Note \Tg~ and \Tx$_{1}$ are obtained from the original raw data, not the deconvolution.
+Note the \Tg~ and \Tx$_{1}$ are obtained from the original raw data, not the deconvolution.
 
@@
 
-In Figures \ref{fig:XRD_Annealing_Bulk} and \ref{fig:XRD_Annealing_Film} it can be observed that Mg$_{51}$Zn$_{20}$ comes out at lower temperature in the film compared to the bulk, while the other phases nucleate and grow at similar rates for both the bulk and film.
+In Figures \ref{fig:XRD_Annealing_Bulk} and \ref{fig:XRD_Annealing_Film} it can be observed that Mg$_{51}$Zn$_{20}$ and Mg come out at a lower temperature in the film compared to the bulk, while the other phases nucleate and grow at similar rates for both the bulk and film.
 The temperature each phase is first and last observed are tabulated in Table \ref{tab:Crystal_Sequence}.
 
-Note the phases identified in Table \ref{tab:Crystal_Sequence} have reasonable agreement with the onset temperatures presented in Tables \ref{tab:BulkOnsets} and \ref{tab:FilmOnsets}.
+Note the phases identified in Table \ref{tab:Crystal_Sequence} have reasonable agreement with the \Tg~ and \Tx~ onset temperatures presented in Tables \ref{tab:BulkOnsets} and \ref{tab:FilmOnsets}.
 With \MgZn~ and Mg corresponding to either \Tx $_{1}$ or \Tx $_{2}$, \CaMgZnFive~ to \Tx$_{3}$, MgZn to \Tx$_{4}$, and \CaMgZnThirteen~ to \Tx$_{5}$.
@@
 	\centering
-	\caption{Temperatures at which each crystallisation phase is first observed and last observed in the annealing \acrshort{xrd} for both the bulk and film. All temperatures are in \degree C.}
+	\caption{Temperatures at which each crystallisation phase is first and last observed in the annealing \acrshort{xrd} for both the bulk and film. All temperatures are in \degree C.}
 	\begin{tabular}{ c c c c c }
@@
 	\includegraphics[width=0.85\textwidth]{XRD_Annealing_Bulk.png}
-	\caption[Table of contents Capition]{\acrshort{xrd} pattern for bulk \MgZnCa~ heated treated to several temperatures for crystallisation peak identified from \acrshort{dsc}.}
+	\caption[Table of contents Capition]{\acrshort{xrd} pattern for bulk \MgZnCa~ heated treated to several temperatures for crystallisation peak identified from \acrshort{dsc}.
+Each phase is identified by a tracer at the temperature it was most strongly observed.}
 	\label{fig:XRD_Annealing_Bulk}
@@
 	\caption[Table of contents Capition]{\acrshort{xrd} pattern for film \MgZnCa~ heated treated to several temperatures for crystallisation peak identified from \acrshort{dsc}.
+Each phase is identified by a tracer at the temperature it was most strongly observed.
 Note the Al substrate peaks have been faceted as to not dwarf all other peaks.}
@@
 
-The annealing \acrshort{xrd} was useful for identifying the crystal phases present, but not many difference between the evolution rates of the bulk or film could be observed.
+The annealing \acrshort{xrd} was useful for identifying the crystal phases present, but not many differences between the evolution rates of the bulk or film could be observed.
 Thus samples were subjected to dynamic \acrshort{xrd} over their most active $2 \theta$ range of $31-60$\degree~ to observe changes \textit{in-situ}.
@@
 The dynamic \acrshort{xrd} data shows that many phases seen in the bulk nucleate at different temperatures, are not observed as strongly, or fail to nucleate in the film.
-The first Mg and \MgZn~ peak at 32.1\degree~ is first clearly seen in the bulk at a temperature of 170\degree C.
+The initial Mg and \MgZn~ peak at 32.1\degree~ is first clearly seen in the bulk at a temperature of 170\degree C.
 In the film the first clear evidence of this peak is at 90\degree C, although its resolution is poor from 150-170\degree C.
@@
 		\midrule
-		32.264 & Both & 15.1461 & Bulk Only & 10.8738 & Both & 12.114 & Both & 12.636 & Both \\
-		34.5053 & Both & 17.5798 & Bulk Only & 14.0992 & Both & 13.935 & Both & 14.752 & Both \\
-		36.7065 & Both & 19.429 & Both & 17.9698 & Both & 20.165 & Both & 20.639 & Both \\
-		47.925 & Both & 21.6753 & Bulk Only & 21.7787 & Both & 21.035 & Both & 22.263 & Both \\
-		57.4721 & Both & 23.2049 & Bulk Only & 23.5826 & Both & 23.329 & Both & 23.58 & Both \\
-		63.2 & Both & 24.5533 & Film Only & 26.1221 & Both & 24.641 & Both & 28.871 & Both \\
-		67.4268 & Both & 27.668 & Bulk Only & 28.3477 & Both & 25.281 & Both & 32.054 & Both \\
+		32.2640 & Both & 15.1461 & Bulk Only & 10.8738 & Both & 12.114 & Both & 12.6360 & Both \\
+		34.5053 & Both & 17.5798 & Bulk Only & 14.0992 & Both & 13.935 & Both & 14.7520 & Both \\
+		36.7065 & Both & 19.4290 & Both & 17.9698 & Both & 20.165 & Both & 20.639 & Both \\
+		47.9250 & Both & 21.6753 & Bulk Only & 21.7787 & Both & 21.035 & Both & 22.263 & Both \\
+		57.4721 & Both & 23.2049 & Bulk Only & 23.5826 & Both & 23.329 & Both & 23.580 & Both \\
+		63.2000 & Both & 24.5533 & Film Only & 26.1221 & Both & 24.641 & Both & 28.871 & Both \\
+		67.4268 & Both & 27.6680 & Bulk Only & 28.3477 & Both & 25.281 & Both & 32.054 & Both \\
 		68.7541 & Both & 30.4946 & Bulk Only & 30.3272 & Both & 27.947 & Both & 33.797 & Both \\
-		70.121 & Both & 32.0757 & Bulk Only & 32.8866 & Both & 29.258 & Both & 34.743 & Both \\
+		70.1210 & Both & 32.0757 & Bulk Only & 32.8866 & Both & 29.258 & Both & 34.743 & Both \\
 		72.6686 & Both & 34.0114 & Both & 34.2311 & Both & 30.699 & Both & 35.892 & Both \\
@@
 		&  & 43.2937 & Both & 41.2057 & Both & 37.281 & Both & 42.824 & Both \\
-		&  & 44.8168 & Both & 42.441 & Both & 38.269 & Both & 43.917 & Both \\
+		&  & 44.8168 & Both & 42.4410 & Both & 38.269 & Both & 43.917 & Both \\
 		&  & 47.9318 & Both & 43.9276 & Both & 40.041 & Both & 47.046 & Both \\
@@
 		&  & 65.0419 & Bulk Only & 53.6599 & Both & 43.917 & Both & 53.211 & Both \\
-		&  & 65.3533 & Film Only & 56.9387 & Both & 44.6 & Both & 55.66 & Both \\
-		&  & 68.5726 & Bulk Only & 58.561 & Both & 45.306 & Both & 57.955 & Both \\
+		&  & 65.3533 & Film Only & 56.9387 & Both & 44.600 & Both & 55.660 & Both \\
+		&  & 68.5726 & Bulk Only & 58.5610 & Both & 45.306 & Both & 57.955 & Both \\
 		&  & 70.0382 & Both & 60.5081 & Both & 46.535 & Both & 60.026 & Both \\
-		&  & 72.6234 & Both & 61.853 & Both & 47.306 & Film Only & 62.26 & Both \\
+		&  & 72.6234 & Both & 61.8530 & Both & 47.306 & Film Only & 62.260 & Both \\
 		&  & 76.4763 & Bulk Only & 62.9999 & Both & 48.104 & Bulk Only & 63.687 & Both \\
 		&  & 77.2025 & Bulk Only & 64.3501 & Both & 50.079 & Both & 65.186 & Both \\
-		&  & 78.3347 & Both & 65.632 & Both & 51.285 & Both &  &  \\
-		&  & 82.0596 & Both & 66.831 & Both & 56.178 & Bulk Only &  &  \\
+		&  & 78.3347 & Both & 65.6320 & Both & 51.285 & Both &  &  \\
+		&  & 82.0596 & Both & 66.8310 & Both & 56.178 & Bulk Only &  &  \\
 		&  &  &  & 68.7827 & Both & 58.601 & Both &  &  \\
-		&  &  &  & 70.1095 & Both & 59.94 & Both &  &  \\
+		&  &  &  & 70.1095 & Both & 59.940 & Both &  &  \\
 		&  &  &  & 71.8163 & Both & 62.028 & Both &  &  \\
-		&  &  &  & 72.8322 & Bulk Only & 63.59 & Both &  &  \\
+		&  &  &  & 72.8322 & Bulk Only & 63.590 & Both &  &  \\
 		&  &  &  & 74.9981 & Both & 64.427 & Both &  &  \\
-		&  &  &  & 78.083 & Both & 66.229 & Both &  &  \\
+		&  &  &  & 78.0830 & Both & 66.229 & Both &  &  \\
 		&  &  &  & 81.5094 & Bulk Only & 67.362 & Both &  &  \\
@@
 		&  &  &  & 83.1204 & Both & 69.524 & Both &  &  \\
-		&  &  &  &  &  & 70.48 & Both &  &  \\
+		&  &  &  &  &  & 70.480 & Both &  &  \\
 		&  &  &  &  &  & 72.032 & Bulk Only &  &  \\
@@
 		&  &  &  &  &  & 76.736 & Both &  &  \\
-		&  &  &  &  &  & 78.69 & Both &  &  \\
+		&  &  &  &  &  & 78.690 & Both &  &  \\
 		&  &  &  &  &  & 79.631 & Both &  & \\

### 2017-08-30 Paper01_EnthalpyAndCrystallization.tex
Replaced \Tg with \gls{Tg} and same for Tx

@@
 Isochronic \acrshort{dsc} was performed on the bulk and film \MgZnCa~ to examine the thermal properties.
-The bulk alloy was relaxed at $120$\degree C for 10 minutes before \acrshort{dsc} measurements to ensure the \Tg~ was clearly visible.
+The bulk alloy was relaxed at $120$\degree C for 10 minutes before \acrshort{dsc} measurements to ensure the \gls{Tg} was clearly visible.
 The film was not relaxed as unlike the bulk the lost in free volume from relaxation would be significant and make differences between the samples much more difficult to observe [source needed???].
 
-The bulk \MgZnCa~ was examined at \acrfullpl{ht} of 5, 10, 15, 20, 30, 40, 60, 80, and 100 $K/min$ to observe changes in the \Tg~ and \Tx s with \gls{ht}.
+The bulk \MgZnCa~ was examined at \acrfullpl{ht} of 5, 10, 15, 20, 30, 40, 60, 80, and 100 $K/min$ to observe changes in the \gls{Tg} and \glspl{Tx} with \gls{ht}.
 As expected greater \gls{ht} resulted in greater signal strength, exothermic peaks shifting to higher start temperatures, and an increase in thermal lag resulting in later exothermic finish temperatures and curve convolution.
-With this convolution the \Tg~ and \Tx $_{1}$  remained clearly visible for all \glspl{ht}, but \Tx $_{2,4,5}$ were only visible at low \glspl{ht}, and \Tx $_{3}$ was not clear at any \gls{ht}, see Figure \ref{fig:DSC_vHeatingRate_Bulk}.
+With this convolution the \gls{Tg} and \gls{Tx}$_{1}$  remained clearly visible for all \glspl{ht}, but \gls{Tx}$_{2,4,5}$ were only visible at low \glspl{ht}, and \gls{Tx}$_{3}$ was not clear at any \gls{ht}, see Figure \ref{fig:DSC_vHeatingRate_Bulk}.
 
@@
 It also appeared that all exothermic events shifted to lower temperatures as compared to the bulk.
-The film \Tg~ and \Tx $_{1}$s were less defined than for the bulk, but could still be identified for all \glspl{ht}.
-For all \glspl{ht} the \Tx $_{2-5}$ onsets could not be easily identified, see Figure \ref{fig:DSC_vHeatingRate_Film}.
+The film \gls{Tg} and \gls{Tx}$_{1}$s were less defined than for the bulk, but could still be identified for all \glspl{ht}.
+For all \glspl{ht} the \gls{Tx}$_{2-5}$ onsets could not be easily identified, see Figure \ref{fig:DSC_vHeatingRate_Film}.
 
@@
 	\caption{Bulk \MgZnCa~ relaxed at 120 \degree C for 10 minutes and heated at various \acrfullpl{ht} from $5$ to $100 K/min$.
-The insert stacks the \gls{dsc} curves and labels the \Tg~ and \Tx s of the \gls{ht} $=100 K/min$ curve.}%global caption
+The insert stacks the \gls{dsc} curves and labels the \gls{Tg} and \glspl{Tx} of the \gls{ht} $=100 K/min$ curve.}%global caption
 	\label{fig:DSC_vHeatingRate_Bulk}
@@
 	\caption{Unrelaxed film \MgZnCa~ heated at various \acrfullpl{ht}  from $15$ to $100 K/min$.
-The insert stacks the \gls{dsc} curves and labels the \Tg~ and \Tx s of the \gls{ht} $=100 K/min$ curve.}%global caption
+The insert stacks the \gls{dsc} curves and labels the \gls{Tg} and \glspl{Tx} of the \gls{ht} $=100 K/min$ curve.}%global caption
 	\label{fig:DSC_vHeatingRate_Film}
@@
 
-Using the isochronic \acrshort{dsc} \Tg s the \gls{m} of the \MgZnCa~ system could be established for both the bulk and film.
+Using the isochronic \acrshort{dsc} \glspl{Tg} the \gls{m} of the \MgZnCa~ system could be established for both the bulk and film.
 Numerical solutions where used to fit the \acrshort{dsc} variant of the \gls{vft} relationship for \gls{ht} \cite{Busch1998}.
@@
 	\includegraphics[width=0.95\textwidth]{Bulk_Film_Fragility.png}
-	\caption{Fitted \acrfull{m} for the \MgZnCa~ system obtained from the \Tg~ of \acrshort{dsc} at various \acrfullpl{ht} for the bulk and film.}
+	\caption{Fitted \acrfull{m} for the \MgZnCa~ system obtained from the \gls{Tg} of \acrshort{dsc} at various \acrfullpl{ht} for the bulk and film.}
 	\label{fig:Fragility_BulkFilm_mValue}
@@
 Numerical 
-solutions were used to deconvolute the isochronic \acrshort{dsc} curves so the various \Tx~ onsets could be accurately determined.
+solutions were used to deconvolute the isochronic \acrshort{dsc} curves so the various \gls{Tx} onsets could be accurately determined.
 This numerical fitting utilised a summation of skewed Gaussian curves to fit a target curve corresponding to the original data; as is a common method \cite{Ashour2010, Yamamoto2007, Spink2008, Spink2015, Schaffer2005}.
@@
 Tables \ref{tab:BulkOnsets} and \ref{tab:FilmOnsets} are also plotted together in Figure \ref{fig:DSC_Onsets_BulkFilm} with the bulk shown in black and the film in red.
-Note the \Tg~ and \Tx$_{1}$ are obtained from the original raw data, not the deconvolution.
+Note the \gls{Tg} and \gls{Tx}$_{1}$ are obtained from the original raw data, not the deconvolution.
 
@@
 This occured because the bulk had 5 well defined events, where as the film was largely convoluted together.
-Thus unique solutions could not be obtained for the lesser \Tx$_{2}$ and \Tx$_{4}$ events of the film.
+Thus unique solutions could not be obtained for the lesser \gls{Tx}$_{2}$ and \gls{Tx}$_{4}$ events of the film.
 
@@
 	\includegraphics[width=0.55\textwidth]{Onsets_BulkandFilm.png}
-	\caption[Table of contents Capition]{The \Tg s and \Tx s plotted at each \acrshort{dsc} \acrfull{ht} for both the bulk and film \MgZnCa. Bulk is shown in black, and film in red.}%global caption
+	\caption[Table of contents Capition]{The \glspl{Tg} and \glspl{Tx} plotted at each \acrshort{dsc} \acrfull{ht} for both the bulk and film \MgZnCa.
+Bulk is shown in black, and film in red.}%global caption
 	\label{fig:DSC_Onsets_BulkFilm}
@@
 These energies are presented in Tables \ref{tab:Bulk_Enthalpy} and \ref{tab:Film_Enthalpy} for the bulk and film respectively.
-Figure \ref{fig:DSC_Decon} shows the \Tx~ onsets and \acrfull{h} for both the bulk and film plotted together.
+Figure \ref{fig:DSC_Decon} shows the \gls{Tx} onsets and \acrfull{h} for both the bulk and film plotted together.
 
 From Tables \ref{tab:Bulk_Enthalpy} and \ref{tab:Film_Enthalpy}, and Figure \ref{fig:DSC_Decon} it can be seen most of the crystallisation formation energy is needed to form the $1^{st}$, $3^{rd}$, and $5^{th}$ phases (i.e.
-\Tx $_{1, 3, 5}$).
+\gls{Tx}$_{1, 3, 5}$).
 With these three phases accounting for approximately $73 \pm 7\%$ of the bulk crystallisation energy.
@@
 	\includegraphics[width=.6\textwidth]{Decon_peak_area_BR.png}
-	\caption{\acrshort{dsc} \Tx~ onset temperatures and \acrfull{h} of crystallisation formation for the bulk and film at each \acrfull{ht}. Bulk is shown in black, and film in red.}
+	\caption{\acrshort{dsc} \gls{Tx} onset temperatures and \acrfull{h} of crystallisation formation for the bulk and film at each \acrfull{ht}. Bulk is shown in black, and film in red.}
 	\label{fig:DSC_Decon}
@@
 Both the bulk and film were heat treated by annealing to 120, 140, 145, 170, 200, 250, 290, and 320\degree C before \acrshort{xrd}.
-This allowed for the location of the \Tg~ and \Tx s to be confirmed as well as for the crystallisation phases to be identify.
+This allowed for the location of the \gls{Tg} and \glspl{Tx} to be confirmed as well as for the crystallisation phases to be identify.
 
@@
 
-Note the phases identified in Table \ref{tab:Crystal_Sequence} have reasonable agreement with the \Tg~ and \Tx~ onset temperatures presented in Tables \ref{tab:BulkOnsets} and \ref{tab:FilmOnsets}.
-With \MgZn~ and Mg corresponding to either \Tx $_{1}$ or \Tx $_{2}$, \CaMgZnFive~ to \Tx$_{3}$, MgZn to \Tx$_{4}$, and \CaMgZnThirteen~ to \Tx$_{5}$.
+Note the phases identified in Table \ref{tab:Crystal_Sequence} have reasonable agreement with the \gls{Tg} and \gls{Tx} onset temperatures presented in Tables \ref{tab:BulkOnsets} and \ref{tab:FilmOnsets}.
+With \MgZn~ and Mg corresponding to either \gls{Tx}$_{1}$ or \gls{Tx}$_{2}$, \CaMgZnFive~ to \gls{Tx}$_{3}$, MgZn to \gls{Tx}$_{4}$, and \CaMgZnThirteen~ to \gls{Tx}$_{5}$.
 

### 2017-08-30 Paper01_EnthalpyAndCrystallization.tex
Results - Dynamic - Figures - updated legend on 145 and 105C figures

@@
 
-The use of a 60K \gls{dsc} \acrfull{ht} compared to the more commonly used 20K rate [sources] shifts peaks for the bulk \MgZnCa~ alloy about 8 - 15 degrees higher.
+\hl{The use of a 60K} \gls{dsc} \acrfull{ht} compared to the more commonly used 20K rate [sources] shifts peaks for the bulk \MgZnCa~ alloy about 8 - 15 degrees higher.
 This higher \glspl{ht} were used because crystallisation events for the films were difficult to differentiation at the lower \glspl{ht}.

### 2017-08-30 Paper01_EnthalpyAndCrystallization.tex
Method - Master Alloy - correct rod and target thickness values

@@
 Alloy homogeneity was ensured by heating and cooling through a cycle of 700\degree C, 385\degree C, 650\degree C, 385\degree C, 650\degree C to a casting temperature of 500 \degree C and 450\degree C for injection and gravity casting respectively.
-Bulk amorphous \MgZnCa~ rods of nominal $2.5 mm$ diameter sectioned to \hl{2mm} thickness, and plates of nominal $1.2 mm$ thickness were produced by copper mold injection casting.
-The $25.4 mm$ diameter targets were prepared from cylindrical copper mold gravity castings sectioned to nominal thicknesses of \hl{3.25} $mm$, and polished.
+Bulk amorphous \MgZnCa~ rods of nominal $2.5 mm$ diameter sectioned to $1mm$ thickness, and plates of nominal $1.2 mm$ thickness were produced by copper mold injection casting.
+The $25.4 mm$ diameter targets were prepared from cylindrical copper mold gravity castings sectioned to nominal thicknesses of $3.25mm$, and polished.
 All samples and targets were stored under Ar when not being examined or used.
